### 2023-04-18 Draft.Rmd
asdfghj

---
title: "Draft"
author: "Aileen Li"
date: "2023-04-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-04-18 Draft.Rmd
saved raw data

@@
 
-## R Markdown
+```{r}
+library(tidyverse)
+dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
 ```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-04-18 Draft.Rmd
added reqs

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
+Title and Introduction
+Write a narrative introduction containing:
+A description of the modeling approaches you have chosen for your comparison;
+An explanation of how the predictor variables were chosen for your model;
+Any exploratory analysis that was done with the data (e.g. correlations, scatterplots, boxplots, histograms, etc.) in order to learn about relationships in the data;
+Your expectation for what the RMSE performance of your model should be.
+
 ```{r}
 library(tidyverse)
-dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
+origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
 
 ```
+
+Wrangling
+This section should include any wrangling or transformations of the data that were done prior to modeling. Code should be included throughout and 
+a textual explanation should be included to explain any wrangling operations.
+
+Results
+Describe the development of your 3 prediction models (or 4 models, if working in a group) and
+how you compared their performance. 
+Be sure to describe the splitting of training and testing datasets 
+and the use of cross-validation to evaluate prediction metrics. 
+Remember that the primary metric for your prediction model will be root-mean-squared error (RMSE). 
+Your results should include 
+at least one visualization demonstrating the prediction performance of your models. 
+You should also include 
+a table summarizing the prediction metrics (including RMSE) across all of the models that you tried.
+
+Discussion
+Putting it all together, what did you learn from your data and your model performance?
+• Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
+• Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
+• Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
+• Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).
+
+Formatting
+Create the report using R Markdown, with 
+headers for each section; 
+include comments to the R code; 
+include references (datasets, context). 
+The final report should be no more than 20 pages (the number of pages can vary greatly depending on the cleaning process).
+It is extremely important that you select pages when submitting on Gradescope.

### 2023-04-18 Draft.Rmd
Update Draft.Rmd
del

--- 2023-04-18 Draft.Rmd
@@
 library(tidyverse)
-dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
+origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
 

### 2023-04-18 Draft.Rmd
load libraries

--- 2023-04-18 Draft.Rmd
@@
 title: "Draft"
-author: "Aileen Li"
+author: "Aileen Li, Nyah Strickland"
 date: "2023-04-18"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 library(tidyverse)
-dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
+library(tidymodels)
+library(broom)
+library(carat)
+library(randomForest)
+library(plotROC)
+
+origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
 

### 2023-04-18 Draft.Rmd
smth

@@
 ---
-title: "Draft"
+title: "Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S."
 author: "Aileen Li, Nyah Strickland"

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

@@
 origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
+```
+## Wrangling
+```{r Predictors}
+## Use 80% of data for training
+train <- origin %>% 
+    slice(1:40)
+
+## Use 20% for testing
+test <- origin %>% 
+    slice(41:50)
+
+# Visualize linear relationship between predictors (lat, lon, state) and predicted value
 
 ```
+
+## Models 
+```{r Linear Regression}
+## Create the recipe
+rec <- origin %>% 
+    recipe(value ~ lat + lon + state) 
+rec
+
+model1 <- linear_reg() %>% 
+    set_engine("lm") %>% 
+    set_mode("regression")
+
+wf1 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model)
+wf1
+
+res <- fit(wf1, data = train)
+
+## Check performance on the complete training data
+res %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+## Check performance using cross-validation
+folds <- vfold_cv(train, v = 10)
+folds
+res <- fit_resamples(wf1, resamples = folds)
+res %>% 
+    collect_metrics()
+```

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

@@
 ```{r Predictors}
+## Split origin dataset into 80/20
+dat_split <- initial_split(origin, prop =.8)
+dat_split
+
 ## Use 80% of data for training 
-train <- origin %>% 
-    slice(1:40)
-
-## Use 20% for testing
-test <- origin %>% 
-    slice(41:50)
+train <- training(dat_split)
 

### 2023-04-19 AileensCode.Rmd
sdfghj

---
title: "Aileens Code"
author: "Aileen Li"
date: "2023-04-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-04-19 Draft.Rmd
yuiop

@@
 ```
+## Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.
+
+Air pollution has consequences for everyone, most especially for those with pre-existing conditions.
+To measure air pollution, we measure tiny particles or droplets in the air that are two and one-half microns or less in width called PM2.5.
+So being able to predict the average PM2.5 concentrations will allow us to keep people most susceptible safe as we look for and implement changes to improve the air quality in the region.
+We chose the predictors by ---- 
+For our four models, we chose linear regression, k-nearest neighbors, bootstrapping, and random forest.
+Linear regression will model a linear relationship between the PM2.5 value in the atmosphere and the predictors.
+K-nearest neighbors will return predicted PM2.5 values based on their neighboring data points.
+Bootstrapping resamples the given data multiple times and returns predictions based on their average.
+Random forest makes an averaged prediction from a collection of independent decision trees.
+We predict that the RMSE performance of the bootstrapping model will be the best.
 
@@
 ```
+
 ## Wrangling

### 2023-04-19 Draft.Rmd
bnnb

@@
 So being able to predict the average PM2.5 concentrations will allow us to keep people most susceptible safe as we look for and implement changes to improve the air quality in the region.
-We chose the predictors by ---- 
+We chose the predictors by ----.
 For our four models, we chose linear regression, k-nearest neighbors, bootstrapping, and random forest.
@@
 ```{r Predictors}
-## Split origin dataset into 80/20
+# Split origin dataset into 80/20
 dat_split <- initial_split(origin, prop =.8)
@@
 
-## Use 80% of data for training 
+# Use 80% of data for training 
 train <- training(dat_split)
+
+# Create standardize train data for kNN
 

### 2023-04-19 Draft.Rmd
edited lm

@@
 ```{r Linear Regression}
-## Create the recipe
+# Create the recipe for all models
 rec <- origin %>% 
     recipe(value ~ lat + lon + state) 
-rec
+# rec
 
+# Linear regr. model
 model1 <- linear_reg() %>% 
@@
     add_recipe(rec) %>% 
-    add_model(model)
-wf1
+    add_model(model1)
+# wf1
 
-res <- fit(wf1, data = train)
+res1 <- fit(wf1, data = train)
 
-## Check performance on the complete training data
-res %>% 
+# Check performance of lin. regr. model on the complete training data
+res1 %>% 
     extract_fit_engine() %>% 
@@
 
-## Check performance using cross-validation
-folds <- vfold_cv(train, v = 10)
-folds
-res <- fit_resamples(wf1, resamples = folds)
-res %>% 
+# Check  lin. regr. model performance using cross-validation
+folds1 <- vfold_cv(train, v = 10)
+folds1
+res1 <- fit_resamples(wf1, resamples = folds1)
+res1 %>% 
     collect_metrics()

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

@@
 ```
+```{r kNN}
+## Scale the data for k-NN model
+origin_scaled <- origin %>% 
+    mutate(across(-value, scale))
+
+## Create the model
+model2 <- nearest_neighbor(neighbors = 5) %>% 
+    set_engine("kknn") %>% 
+    set_mode("classification")
+
+## Create workflow
+  wf2 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model2)
+
+## Fit the model on the full training dataset using the `fit()` function
+pokemon_kNN <- fit(wf2, data = train)
+
+## Check performance on the complete training data
+res2 %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+## Check performance using cross-validation
+folds <- vfold_cv(train, v = 10)
+folds
+res2 <- fit_resamples(wf2, resamples = folds)
+res2 %>% 
+    collect_metrics()
+```
+
+```{r Bootstrap}
+## Create Bootstrap Model
+model3 <- nearest_neighbor(neighbors = 5) %>% 
+    set_engine("kknn") %>% 
+    set_mode("classification")
+
+## Create workflow
+  wf3 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model3)
+
+```
+
+```{r Random Forests}
+## Create Random Forest Model
+model4 <- rand_forest(mtry = 5) %>% 
+    set_engine("ranger") %>% 
+    set_mode("regression")
+
+## Create workflow
+  wf4 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model4)
+
+```

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

@@
     recipe(value ~ lat + lon + state)
-# rec
 
@@
 
-# Check performance of lin. regr. model on the complete training data
+# Check performance of linear regression model on the complete training data
 res1 %>% 
@@
 
-# Check  lin. regr. model performance using cross-validation
+# Check  linear regression model performance using cross-validation
 folds1 <- vfold_cv(train, v = 10)
@@
 
-## Create the model
+## Create kNN model
 model2 <- nearest_neighbor(neighbors = 5) %>% 

### 2023-04-19 Draft.Rmd
k

--- 2023-04-19 Draft.Rmd
@@
   Air pollution has consequences for everyone, most especially for those with pre-existing conditions.
-To measure air pollution, we measure tiny particles or droplets in the air that are two and one-half microns or less in width called PM2.5.
-So being able to predict the average PM2.5 concentrations will allow us to keep people most susceptible safe as we look for and implement changes to improve the air quality in the region.
-We chose the predictors by ----.
+Air pollution is measured in tiny particles or droplets in the air that are two and one-half microns or less in width called PM2.5.
+So being able to predict the average PM2.5 concentrations will allow us to keep people most vulnerable safe as we look for and implement changes to improve the air quality in the region.
+We chose the predictors by …
 For our four models, we chose linear regression, k-nearest neighbors, bootstrapping, and random forest.
-Linear regression will model a linear relationship between the PM2.5 value in the atmosphere and the predictors.
-K-nearest neighbors will return predicted PM2.5 values based on their neighboring data points.
+Linear regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
+K-nearest neighbors (kNN) returns predicted PM2.5 values based on their neighboring data points.
 Bootstrapping resamples the given data multiple times and returns predictions based on their average.
 Random forest makes an averaged prediction from a collection of independent decision trees.
-We predict that the RMSE performance of the bootstrapping model will be the best.
+We predict that the RMSE performance of the bootstrapping model will be the best, with a value of around 0.5.
 
@@
 
-# Visualize linear relationship between predictors (lat, lon, state) and predicted value
+# Visualize linear relationship between predictors (lat, lon, state) and value
+# Visual of relationship between PM
+origin |> ggplot(aes(x=lon, y=value)) + 
+  geom_point() + geom_smooth() + 
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude ()", y="PM2.5")
 

### 2023-04-19 Draft.Rmd
edited knn

--- 2023-04-19 Draft.Rmd
@@
 # Visualize linear relationship between predictors (lat, lon, state) and value
-# Visual of relationship between PM
 origin |> ggplot(aes(x=lon, y=value)) + 
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude ()", y="PM2.5")
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude (degrees)", y="PM2.5")
 
@@
 
-# Check  lin. regr. model performance using cross-validation
+# Check linear regression model performance using cross-validation
 folds1 <- vfold_cv(train, v = 10)
@@
 ```
+
+```{r kNN}
+# Find ideal k clusters
+
+# Scale the training data for k-NN model
+train_scales
+origin_scaled <- origin %>% 
+    mutate(across(-value, scale))
+
+# Create kNN model
+model2 <- nearest_neighbor(neighbors = 5) %>% 
+    set_engine("kknn") %>% 
+    set_mode("regression")
+
+# Create workflow
+  wf2 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model2)
+
+# Fit the model on the full training dataset using the `fit()` function
+res2 <- fit(wf2, data = train)
+
+# Check performance on the complete training data
+res2 %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+# Check performance using cross-validation
+folds <- vfold_cv(train, v = 10)
+folds
+res2 <- fit_resamples(wf2, resamples = folds) #error Assigned data `orig_rows` must be compatible with existing data.
+res2 %>% 
+    collect_metrics()
+```
+
+```{r Bootstrap}
+# Create Bootstrap Model
+model3 <- nearest_neighbor(neighbors = 5) %>% 
+    set_engine("kknn") %>% 
+    set_mode("classification")
+
+# Create workflow
+  wf3 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model3)
+
+```
+
+```{r Random Forests}
+# Create Random Forest Model
+model4 <- rand_forest(mtry = 5) %>% 
+    set_engine("ranger") %>% 
+    set_mode("regression")
+
+# Create workflow
+  wf4 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model4)
+
+```

### 2023-04-19 Draft.Rmd
scaled train for knn

@@
 
-# Check performance of linear regression model on the complete training data
+# Check performance of linear regression model on the training data
 res1 %>% 
@@
 ```{r kNN}
-# Find ideal k clusters
+# Find ideal k neighbors
+sqrt(nrow(train))
 
 # Scale the training data for k-NN model
-train_scales
-origin_scaled <- origin %>% 
-    mutate(across(-value, scale))
+train_scaled = train |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)
 
 # Create kNN model
-model2 <- nearest_neighbor(neighbors = 5) %>% 
+model2 <- nearest_neighbor(neighbors = 26) %>% 
     set_engine("kknn") %>% 
@@
 # Fit the model on the full training dataset using the `fit()` function
-res2 <- fit(wf2, data = train)
+res2 <- fit(wf2, data = train_scaled)
 
@@
 folds
-res2 <- fit_resamples(wf2, resamples = folds) #error Assigned data `orig_rows` must be compatible with existing data.
+res2 <- fit_resamples(wf2, resamples = folds) # error Assigned data `orig_rows` must be compatible with existing data.
 res2 %>% 

### 2023-04-20 Draft.Rmd
jop

@@
 folds
-res2 <- fit_resamples(wf2, resamples = folds) # error Assigned data `orig_rows` must be compatible with existing data.
+res2 <- fit_resamples(wf2, resamples = folds) # ERROR Assigned data `orig_rows` must be compatible with existing data.
 res2 %>% 

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

@@
 library(broom)
-library(carat)
-library(randomForest)
+library(caret)
 library(plotROC)
@@
 ```{r Bootstrap}
-# Create Bootstrap Model
+# Create Bootstrap Model (resampling data)
+set.seed(123)
 model3 <- nearest_neighbor(neighbors = 5) %>% 

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

@@
 # Create the recipe for all models
-rec <- origin %>% 
+rec <- train %>% 
     recipe(value ~ lat + lon + state)
@@
 ```
+
+## Results
+Describe the development of your 3 prediction models (or 4 models, if working in a group) and
+how you compared their performance. 
+Be sure to describe the splitting of training and testing datasets 
+and the use of cross-validation to evaluate prediction metrics. 
+Remember that the primary metric for your prediction model will be root-mean-squared error (RMSE). 
+Your results should include 
+at least one visualization demonstrating the prediction performance of your models. 
+You should also include 
+a table summarizing the prediction metrics (including RMSE) across all of the models that you tried.
+
+1. Based on test set performance, at what locations does your model give predictions that
+are closest and furthest from the observed values? What do you hypothesize are the
+reasons for the good or bad performance at these locations?
+2. What variables might predict where your model performs well or not? For example, are
+their regions of the country where the model does better or worse? Are there variables
+that are not included in this dataset that you think might improve the model performance
+if they were included in your model?
+3. There is interest in developing more cost-effect approaches to monitoring air pollution
+on the ground. Two candidates for replacing the use of ground-based monitors are
+numerical models like CMAQ and satellite-based observations such as AOD. How well do
+CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction
+performance of your model change when CMAQ or aod are included (or not included) in
+the model?
+4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
+will perform well or not in those two states? Explain your reasoning
+
+## Discussion
+Putting it all together, what did you learn from your data and your model performance?
+• Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
+• Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
+• Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
+• Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).

### 2023-04-20 Draft.Rmd
pop

--- 2023-04-20 Draft.Rmd
@@
 # Check performance using cross-validation
-folds <- vfold_cv(train, v = 10)
-folds
-res2 <- fit_resamples(wf2, resamples = folds) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+folds2 <- vfold_cv(train, v = 10)
+# folds
+res2 <- fit_resamples(wf2, resamples = folds2) # ERROR Assigned data `orig_rows` must be compatible with existing data.
 res2 %>% 

### 2023-04-20 Draft.Rmd
boosting

--- 2023-04-20 Draft.Rmd
@@
 # Check linear regression model performance using cross-validation
+
 folds1 <- vfold_cv(train, v = 10)
@@
 # Check performance using cross-validation
-folds <- vfold_cv(train, v = 10)
-folds
-res2 <- fit_resamples(wf2, resamples = folds) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+
+folds2 <- vfold_cv(train, v = 10)
+# folds
+res2 <- fit_resamples(wf2, resamples = folds2) # ERROR Assigned data `orig_rows` must be compatible with existing data.
 res2 %>% 
     collect_metrics()
+```
+
+```{r Bootstrap test}
+model3 = boost_tree( mtry = integer(), trees = integer(), min_n = integer(),
+  tree_depth = integer(), learn_rate = numeric(), loss_reduction = numeric(),
+  sample_size = numeric(), stop_iter = integer()) %>%
+  set_engine("xgboost") %>%
+  set_mode("regression") %>%
+  translate()
+
+# preprocessing "recipe"
+preprocessing_recipe <- 
+  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
+  # convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds3 <- 
+  recipes::bake(
+    preprocessing_recipe, 
+    new_data = training(dat_split)
+  ) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# grid specification
+xgboost_params <- 
+  dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+knitr::kable(head(xgboost_grid))
+
+xgboost_wf <- 
+  workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value~lon+lat)
+
+# hyperparameter tuning
+xgboost_tuned <- tune::tune_grid(
+  object = xgboost_wf,
+  resamples = folds3,
+  grid = xgboost_grid,
+  metrics = yardstick::metric_set(rmse, rsq, mae),
+  control = tune::control_grid(verbose = TRUE)
+)
+
+xgboost_tuned %>%
+  tune::show_best(metric = "rmse") %>%
+  knitr::kable()
+
 ```
@@
 set.seed(123)
-model3 <- nearest_neighbor(neighbors = 5) %>% 
-    set_engine("kknn") %>% 
-    set_mode("classification")
+model3 <- boost_tree() %>% 
+    set_engine("xgboost") %>%
+    set_mode("regression")
 
@@
 
+# Fit the model on the training dataset using the `fit()` function
+res3 <- fit(wf3, data = train) # Error in if (is.numeric(args$trees) && args$trees < 0) { : missing value where TRUE/FALSE needed
+
+# Check performance on the complete training data
+res3 %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+# Check performance using cross-validation
+
+folds3 <- vfold_cv(train, v = 10)
+# folds
+res3 <- fit_resamples(wf3, resamples = folds3) 
+res3 %>% 
+    collect_metrics()
 ```
+
+Preprocessing requirements
+xgboost does not have a means to translate factor predictors to grouped splits.
+Factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) for this engine.
+When using the formula method via fit.model_spec(), parsnip will convert factor columns to indicators using a one-hot encoding.
 

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

@@
 
-```{r Random Forests}
 # Create Random Forest Model
-model4 <- rand_forest(mtry = 5) %>% 
+set.seed(123)
+# Use grid of tuning parameters
+model4 <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
     set_engine("ranger") %>% 
     set_mode("regression")
-
 # Create workflow
@@
 
-```
+# Fit the model on the full training dataset using the `fit()` function
+res4 <- fit(wf4, data = train_scaled)
+# Check performance on the complete training data
+res4 %>% 
+    extract_fit_engine() %>% 
+    summary()
+# Check performance using cross-validation
+folds <- vfold_cv(train, v = 10)
+folds
+# Determine performance of model by resampling
+res3 <- fit_resamples(wf4, folds) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+res3 %>% 
+    collect_metrics()
+
+## Try a grid of tuning parameters
+model <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
+    set_engine("ranger") %>% 
+    set_mode("regression")
+
+wf <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model)
+
+## Fit model over grid of tuning parameters
+res <- tune_grid(wf, resamples = folds)
+res %>% 
+    collect_metrics()
 

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

@@
 
+origin %>% ggplot(aes(x=lat, y=value)) + 
+  geom_point() + geom_smooth() + 
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="Latitude (degrees)", y="PM2.5")
+
+origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="State", y="PM2.5") 
 ```

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

--- 2023-04-20 Draft.Rmd
@@
 ```{r Predictors}
+set.seed(123)
 # Split origin dataset into 80/20
@@
 
-```{r Random Forests}
 # Create Random Forest Model
-model4 <- rand_forest(mtry = 5) %>% 
+set.seed(123)
+# Create Random Forest Model
+# Use grid of tuning parameters
+model4 <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
     set_engine("ranger") %>% 
     set_mode("regression")
-
 # Create workflow
@@
 
-```
+# Fit the model on the full training dataset using the `fit()` function
+res4 <- fit(wf4, data = train_scaled)
+# Check performance on the complete training data
+res4 %>% 
+    extract_fit_engine() %>% 
+    summary()
+# Check performance using cross-validation
+folds4 <- vfold_cv(train, v = 10)
+folds4
+# Determine performance of model by resampling
+res4 <- fit_resamples(wf4, folds4) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+res4 %>% 
+    collect_metrics()
+
+## Try a grid of tuning parameters
+model <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
+    set_engine("ranger") %>% 
+    set_mode("regression")
+
+wf4 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model)
+
+## Fit model over grid of tuning parameters
+res <- tune_grid(wf4, resamples = folds4, grid = 20)
+
+res %>% 
+    collect_metrics()
 

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

@@
 
+```{r Random Forest}
 # Create Random Forest Model
 set.seed(123)
-# Create Random Forest Model
 # Use grid of tuning parameters
@@
     collect_metrics()
+```
 

### 2023-04-20 Draft.Rmd
edited format of boosting code

--- 2023-04-20 Draft.Rmd
@@
 
-origin %>% ggplot(aes(x=lat, y=value)) + 
-  geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Latitude (degrees)", y="PM2.5")
-
-origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="State", y="PM2.5") 
 ```
@@
 
-```{r Bootstrap test}
-model3 = boost_tree( mtry = integer(), trees = integer(), min_n = integer(),
-  tree_depth = integer(), learn_rate = numeric(), loss_reduction = numeric(),
-  sample_size = numeric(), stop_iter = integer()) %>%
-  set_engine("xgboost") %>%
-  set_mode("regression") %>%
-  translate()
-
-# preprocessing "recipe"
+```{r Boost}
+# Preprocessing "recipe"
 preprocessing_recipe <- 
@@
 
-folds3 <- 
-  recipes::bake(
-    preprocessing_recipe, 
-    new_data = training(dat_split)
-  ) %>%  
+folds3 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
   rsample::vfold_cv(v = 5)
@@
 
-# grid specification
-xgboost_params <- 
-  dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
 
 xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
 knitr::kable(head(xgboost_grid))
 
-xgboost_wf <- 
-  workflows::workflow() %>%
+xgboost_wf <- workflows::workflow() %>%
   add_model(xgboost_model) %>% 
@@
 
-# hyperparameter tuning
-xgboost_tuned <- tune::tune_grid(
-  object = xgboost_wf,
-  resamples = folds3,
-  grid = xgboost_grid,
-  metrics = yardstick::metric_set(rmse, rsq, mae),
-  control = tune::control_grid(verbose = TRUE)
-)
+# Hyperparameter tuning
+# Takes a long time to run
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds3,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq, mae),
+  control = tune::control_grid(verbose = TRUE))
 
+# Find hyper parameter values which performed best at minimizing RMSE
 xgboost_tuned %>%
@@
   knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>%
+  tune::select_best("rmse")
+knitr::kable(xgboost_best_params)
 
+# Final boost model
+xgboost_model_final <- xgboost_model %>% 
+  finalize_model(xgboost_best_params)
+
+# Eval. model performance on test data
+train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
+
+train_prediction <- xgboost_model_final %>%
+# fit the model on all the training data
+  fit(formula = value ~ lon+lat, data = train_processed) %>%
+  # predict the sale prices for the training data
+  predict(new_data = train_processed) %>%
+  bind_cols(training(ames_split))
+
+xgboost_score_train <- train_prediction %>%
+  yardstick::metrics(sale_price, .pred) %>%
+  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
+
+knitr::kable(xgboost_score_train)
 ```
@@
 
+```{r Random Forests}
 # Create Random Forest Model
-set.seed(123)
-# Use grid of tuning parameters
-model4 <- rand_forest(mtry = tune("mtry"),
-                     min_n = tune("min_n")) %>% 
+model4 <- rand_forest(mtry = 5) %>% 
     set_engine("ranger") %>% 
     set_mode("regression")
+
 # Create workflow
@@
 
-# Fit the model on the full training dataset using the `fit()` function
-res4 <- fit(wf4, data = train_scaled)
-# Check performance on the complete training data
-res4 %>% 
-    extract_fit_engine() %>% 
-    summary()
-# Check performance using cross-validation
-folds <- vfold_cv(train, v = 10)
-folds
-# Determine performance of model by resampling
-res3 <- fit_resamples(wf4, folds) # ERROR Assigned data `orig_rows` must be compatible with existing data.
-res3 %>% 
-    collect_metrics()
-
-## Try a grid of tuning parameters
-model <- rand_forest(mtry = tune("mtry"),
-                     min_n = tune("min_n")) %>% 
-    set_engine("ranger") %>% 
-    set_mode("regression")
-
-wf <- workflow() %>% 
-    add_recipe(rec) %>% 
-    add_model(model)
-
-## Fit model over grid of tuning parameters
-res <- tune_grid(wf, resamples = folds)
-res %>% 
-    collect_metrics()
+```
 

### 2023-04-20 Draft.Rmd

@@
 
-```{r Random Forests}
+```{r Random Forest}
 # Create Random Forest Model
-model4 <- rand_forest(mtry = 5) %>% 
+set.seed(123)
+# Use grid of tuning parameters
+model4 <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
     set_engine("ranger") %>% 
     set_mode("regression")
-
 # Create workflow
@@
 
+# Fit the model on the full training dataset using the `fit()` function
+res4 <- fit(wf4, data = train_scaled)
+# Check performance on the complete training data
+res4 %>% 
+    extract_fit_engine() %>% 
+    summary()
+# Check performance using cross-validation
+folds4 <- vfold_cv(train, v = 10)
+folds4
+# Determine performance of model by resampling
+res4 <- fit_resamples(wf4, folds4) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+res4 %>% 
+    collect_metrics()
+
+## Try a grid of tuning parameters
+model <- rand_forest(mtry = tune("mtry"),
+                     min_n = tune("min_n")) %>% 
+    set_engine("ranger") %>% 
+    set_mode("regression")
+
+wf4 <- workflow() %>% 
+    add_recipe(rec) %>% 
+    add_model(model)
+
+## Fit model over grid of tuning parameters
+res <- tune_grid(wf4, resamples = folds4, grid = 20)
+
+res %>% 
+    collect_metrics()
 ```

### 2023-04-20 Draft.Rmd
edited code 2

@@
   recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
-  # convert categorical variables to factors
+  # Convert categorical variables to factors
   recipes::step_string2factor(all_nominal()) %>%
-  # combine low frequency factor levels
+  # Combine low frequency factor levels
   recipes::step_other(all_nominal(), threshold = 0.01) %>%
-  # remove no variance predictors which provide no predictive information 
+  # Remove no variance predictors which provide no predictive information 
   recipes::step_nzv(all_nominal()) %>%
@@
 # Find hyper parameter values which performed best at minimizing RMSE
-xgboost_tuned %>%
-  tune::show_best(metric = "rmse") %>%
-  knitr::kable()
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
 # Isolate the best performing hyperparameter values.
-xgboost_best_params <- xgboost_tuned %>%
-  tune::select_best("rmse")
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
 knitr::kable(xgboost_best_params)
@@
 # Final boost model
-xgboost_model_final <- xgboost_model %>% 
-  finalize_model(xgboost_best_params)
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
 
@@
 train_prediction <- xgboost_model_final %>%
-# fit the model on all the training data
+  # Fit the model on all the training data
   fit(formula = value ~ lon+lat, data = train_processed) %>%
-  # predict the sale prices for the training data
+  # Predict the sale prices for the training data
   predict(new_data = train_processed) %>%
@@
   mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
-
 knitr::kable(xgboost_score_train)

### 2023-04-20 Draft.Rmd
set seed

@@
 ```{r Linear Regression}
+set.seed(123)
 # Create the recipe for all models
@@
 ```{r kNN}
+set.seed(123)
 # Find ideal k neighbors
@@
 
-# Fit the model on the full training dataset using the `fit()` function
+# Fit the model on the training dataset using the `fit()` function
 res2 <- fit(wf2, data = train_scaled)
@@
 ```{r Boost}
+set.seed(123)
 # Preprocessing "recipe"
@@
 
+res3 = xgboost_model_final %>% fit(formula = value ~ lon+lat, data = train)
+  extract_fit_engine() %>% 
+  summary()
+
+# Check performance using cross-validation
+
+folds3 <- vfold_cv(train, v = 10)
+# folds
+res3 <- fit_resamples(wf3, resamples = folds3) 
+res3 %>% 
+    collect_metrics()
+
 # Eval. model performance on test data
@@
   predict(new_data = train_processed) %>%
-  bind_cols(training(ames_split))
+  bind_cols(training(dat_split))
 
 xgboost_score_train <- train_prediction %>%
-  yardstick::metrics(sale_price, .pred) %>%
+  yardstick::metrics(value, .pred) %>%
   mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
@@
 ```{r Bootstrap}
+set.seed(123)
 # Create Bootstrap Model (resampling data)
@@
 ```{r Random Forest}
+set.seed(123)
 # Create Random Forest Model

### 2023-04-20 Draft.Rmd
added code block

@@
 Air pollution is measured in tiny particles or droplets in the air that are two and one-half microns or less in width called PM2.5.
-So being able to predict the average PM2.5 concentrations will allow us to keep people most vulnerable safe as we look for and implement changes to improve the air quality in the region.
+So being able to predict the average PM2.5 concentrations ($\mu$g/m$^3$) will allow us to keep people most vulnerable safe as we look for and implement changes to improve the air quality in the region.
 We chose the predictors by …
-For our four models, we chose linear regression, k-nearest neighbors, bootstrapping, and random forest.
+For our four models, we chose linear regression, k-nearest neighbors, xgboosting, and random forest.
 Linear regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
 K-nearest neighbors (kNN) returns predicted PM2.5 values based on their neighboring data points.
-Bootstrapping resamples the given data multiple times and returns predictions based on their average.
+INSERT BOOSTING MODEL SENTENCE.
 Random forest makes an averaged prediction from a collection of independent decision trees.
@@
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude (degrees)", y="PM2.5")
+  labs(title="PM2.5 Concentration vs Longitude", x="Longitude (degrees)", y="PM2.5 (mu g/m^3)")
 
@@
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Latitude (degrees)", y="PM2.5")
+  labs(title="PM2.5 Concentration vs Latitude", x="Latitude (degrees)", y="PM2.5 (mu g/m^3)")
 
 origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="State", y="PM2.5") 
+  labs(title="PM2.5 Concentration by State", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") +
+  theme(legend.position="none",strip.text.x = element_text(margin = margin()))
+```
+
+## Predictor Reduction
+```{r}
+# Scale dataset
+
+# Covar. matrix
+
+# Eigenval.s and eigenvec.s
+
+# PCA
+
+# Data transformation in new dimensional space
+
 ```

### 2023-04-20 Draft.Rmd
remove bootstrap code block

@@
 
-res3 = xgboost_model_final %>% fit(formula = value ~ lon+lat, data = train)
-  extract_fit_engine() %>% 
-  summary()
-
-# Check performance using cross-validation
-
-folds3 <- vfold_cv(train, v = 10)
-# folds
-res3 <- fit_resamples(wf3, resamples = folds3) 
-res3 %>% 
-    collect_metrics()
-
 # Eval. model performance on test data
@@
 knitr::kable(xgboost_score_train)
-```
-
-```{r Bootstrap}
-set.seed(123)
-# Create Bootstrap Model (resampling data)
-set.seed(123)
-model3 <- boost_tree() %>% 
-    set_engine("xgboost") %>%
-    set_mode("regression")
-
-# Create workflow
-  wf3 <- workflow() %>% 
-    add_recipe(rec) %>% 
-    add_model(model3)
-
-# Fit the model on the training dataset using the `fit()` function
-res3 <- fit(wf3, data = train) # Error in if (is.numeric(args$trees) && args$trees < 0) { : missing value where TRUE/FALSE needed
-
-# Check performance on the complete training data
-res3 %>% 
-    extract_fit_engine() %>% 
-    summary()
-
-# Check performance using cross-validation
-
-folds3 <- vfold_cv(train, v = 10)
-# folds
-res3 <- fit_resamples(wf3, resamples = folds3) 
-res3 %>% 
-    collect_metrics()
 ```

### 2023-04-20 Draft.Rmd
aic

@@
 library(plotROC)
+library(vip)
 
@@
 
-# Create standardize train data for kNN
+# Create standardize train data for kNN and PCA
 
@@
 ## Models 
+```{r Lin Regr.}
+rec1 <- recipe(value ~ ., data = train) %>% 
+                      step_YeoJohnson(all_numeric(), -all_outcomes()) %>% 
+                      step_normalize(all_numeric(), -all_outcomes())
+
+model1 <- linear_reg() %>% 
+    set_engine("lm") %>% 
+    set_mode("regression")
+
+fit1 = model1 |> fit(value ~ ., data=train)
+summary(fit1$fit)
+
+tidy(fit1)
+glance(fit1)
+vip(fit1)
+
+wf1 <- workflow() %>% 
+    add_recipe(rec1) %>% 
+    add_model(model1)
+
+res1 = wf1 |> last_fit(split=dat_split)
+res1 |> collect_metrics()
+
+library(MASS)
+fit <- lm(value ~ .,data=train)
+step <- stepAIC(fit, direction="both")
+step$anova
+
+```
+
 ```{r Linear Regression}
@@
 
-```{r Boost}
+Preprocessing requirements
+xgboost does not have a means to translate factor predictors to grouped splits.
+Factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) for this engine.
+When using the formula method via fit.model_spec(), parsnip will convert factor columns to indicators using a one-hot encoding.
+
+```{r Xgboost}
 set.seed(123)
@@
 ```
-
-Preprocessing requirements
-xgboost does not have a means to translate factor predictors to grouped splits.
-Factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) for this engine.
-When using the formula method via fit.model_spec(), parsnip will convert factor columns to indicators using a one-hot encoding.
 

### 2023-04-21 Draft.Rmd
pop

@@
 library(plotROC)
-library(vip)
 
@@
 ```{r Lin Regr.}
-rec1 <- recipe(value ~ ., data = train) %>% 
-                      step_YeoJohnson(all_numeric(), -all_outcomes()) %>% 
-                      step_normalize(all_numeric(), -all_outcomes())
-
 model1 <- linear_reg() %>% 
@@
 
-fit1 = model1 |> fit(value ~ ., data=train)
-summary(fit1$fit)
+fit1 = model1 |> fit(value ~ ., data=train_scaled)
+x=summary(fit1$fit)$coefficients
 
@@
 glance(fit1)
-vip(fit1)
 
@@
 library(MASS)
-fit <- lm(value ~ .,data=train)
-step <- stepAIC(fit, direction="both")
+fit <- lm(value ~ .,data=train_scaled)
+step <- stepAIC(fit, direction="forward")
 step$anova

### 2023-04-22 Draft.Rmd
pred elim

@@
 library(plotROC)
+library(randomForest)
 
@@
 # Create standardize train data for kNN and PCA
+# excl. id and value
+train_scaled = train[,3:50] |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)
 
@@
 
-## Predictor Reduction
+## Predictor/Feature Selection
 ```{r}
+# Use Random Forest for variable selection
+rfmodel = randomForest(value~., data=train[,2:50])
+import=as.data.frame(importance(rfmodel)) |> arrange(desc(IncNodePurity))
+import=tibble::rownames_to_column(import, 'variables')
+# Now from this list, you can select the variables. Mostly, the top 20 variables are what we select. However, this is just an indicative value and may vary based upon the problem.
+
+# take top 20 important variables
+import20 = import[1:20,]
+
+# Use Information Gain for variable selection
+library(MASS)
+
+fit_lm = lm(value~, data=train)
+
+stepAIC(fit_lm, direction="backward", trace=FALSE)
+stepAIC(fit_lm, direction="forward", trace=FALSE)
+stepAIC(fit_lm, direction="both", trace=FALSE)
+
+# Use Recursive Feature Elimination method
+set.seed(123)
+cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
+
+profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)
+
+# Use Lasso for variable selection X
+y=train[,2]
+
+library(glmnet)
+feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
+
+as.matrix(coef(features,features$lambda.min))
+
 # Scale dataset
@@
 ## Models 
+```{r}
+set.seed(123)
+library(party)
+# fit randfom forest and get var. importance based on mean decr. in accuracy
+train_num = train[,2:50] |> dplyr::select(where(is.numeric))
+cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
+# adj for corr. btw predictors
+varimp(cf1, conditional=TRUE)
+# more robust towards class imbalance
+varimpAUC(cf1)
+
+```
+
 ```{r Lin Regr.}
@@
     set_mode("regression")
+
+imp = varImp(model1, scale=FALSE)
 
@@
 
-# Scale the training data for k-NN model
-train_scaled = train |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)
+# Scale the training data for k-NN model in wrangling
 

### 2023-04-22 Draft.Rmd
moved code

@@
 import20 = import[1:20,]
+```
 
+```{r delete}
 # Use Information Gain for variable selection
 library(MASS)
-
 fit_lm = lm(value~, data=train)
-
 stepAIC(fit_lm, direction="backward", trace=FALSE)
@@
 cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
-
 profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)
@@
 y=train[,2]
-
 library(glmnet)
 feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
-
 as.matrix(coef(features,features$lambda.min))
 
-# Scale dataset
-
-# Covar. matrix
-
-# Eigenval.s and eigenvec.s
-
-# PCA
-
-# Data transformation in new dimensional space
-
-```
-
-## Models 
-```{r}
+# fit randfom forest and get var. importance based on mean decr. in accuracy
 set.seed(123)
 library(party)
-# fit randfom forest and get var. importance based on mean decr. in accuracy
 train_num = train[,2:50] |> dplyr::select(where(is.numeric))
@@
 
+# Scale dataset
+# Covar. matrix
+# Eigenval.s and eigenvec.s
+# PCA
+# Data transformation in new dimensional space
 ```
 
+## Models 
 ```{r Lin Regr.}

### 2023-04-22 Draft.Rmd
del margin

@@
   labs(title="PM2.5 Concentration by State", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") +
-  theme(legend.position="none",strip.text.x = element_text(margin = margin()))
+  theme(legend.position="none")
 ```
@@
 
-# take top 20 important variables
-import20 = import[1:20,]
+# take top 10 important variables
+import10 = import[1:10,]
 ```
@@
 rec <- train %>% 
-    recipe(value ~ lat + lon + state)
+    recipe(value ~ )
 

### 2023-04-22 Draft.Rmd
Update Draft.Rmd

@@
 dat_split
-
 # Use 80% of data for training 
@@
 # Create standardize train data for kNN and PCA
-# excl. id and value
-train_scaled = train[,3:50] |> dplyr::select(where(is.numeric)) |> mutate(across(fips:aod, scale)) |> cbind(state=train$state,county=train$county,city=train$city)
+# Omit value and id variables since these should not be scaled
+train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) #%>% cbind(state=train$state,county=train$county,city=train$city)
+
+# Calculate principal components on scaled training data
+pca_result <- train_scaled %>% dplyr::select(where(is.numeric)) %>%
+  prcomp()
+
+# Plot scree plot
+pca_result %>% fviz_eig()
+
+# Plot table to show explained variance % by PCs
+summary(pca_result)
+
+# Threshold of Explained Variance = 80%
+# Calculated the sum of PCs with highest explained variance until threshold was meant
+0.3253 + 0.09749 + 0.07984 + 0.06501 + 0.05196 + 0.04147 + 0.03445 +
+0.02926 + 0.02563 + 0.0220 + 0.02127 + 0.0188
+
+PC1 <- pca_result$rotation[,1]
+PC1_scores <- abs(PC1)
+PC1_scores_ordered <- sort(PC1_scores, decreasing = TRUE)
+names(PC1_scores_ordered)
+
+# Reduce dimension of dataset
+trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
+# Add the center (and re-scale) back to data 
+if(all(pca_result$scale != FALSE)){
+  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
+  } 
+if(all(pca_result$center != FALSE)){ 
+  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
+  } 
+dim(trunc); dim(train_scaled)
+
+# unhelpful plot -- delete
+# plot(pca_result$x[,1], pca_result$x[,2])
+
+# Show which features have the most influence
+as_tibble(pca_result$rotation, 
+          rownames = "variable") %>% 
+    ggplot(aes(variable, PC1)) +
+    geom_point() +
+    coord_flip()
+
+as_tibble(pca_result$rotation, 
+          rownames = "variable") %>% 
+    ggplot(aes(variable, PC2)) +
+    geom_point() +
+    coord_flip()
+
+# Plot clusters between PC1 and PC2 using a biplot
+fviz_pca_var(pca_result)
+
+# Reduce dimension of dataset
+trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
+# Add the center (and re-scale) back to data 
+if(all(pca_result$scale != FALSE)){
+  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
+  } 
+if(all(pca_result$center != FALSE)){ 
+  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
+  } 
+dim(trunc); dim(train_scaled)
 
 # Visualize linear relationship between predictors (lat, lon, state) and value
-origin |> ggplot(aes(x=lon, y=value)) + 
+origin %>% ggplot(aes(x=lon, y=value)) + 
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration vs Longitude", x="Longitude (degrees)", y="PM2.5 (mu g/m^3)")
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude (degrees)", y="PM2.5")
 
@@
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration vs Latitude", x="Latitude (degrees)", y="PM2.5 (mu g/m^3)")
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="Latitude (degrees)", y="PM2.5")
 
 origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
-  labs(title="PM2.5 Concentration by State", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") +
-  theme(legend.position="none")
+  labs(title="PM2.5 Concentration (mu g/m^3)", x="State", y="PM2.5") 
 ```

### 2023-04-22 Draft.Rmd
Update Draft.Rmd

@@
 ## Models 
-```{r Lin Regr.}
+```{r Lin Regr. DELETE}
 model1 <- linear_reg() %>% 
@@
 
-```{r Linear Regression}
+```{r Linear Regression KEEP}
 set.seed(123)

### 2023-04-22 Draft.Rmd
Update Draft.Rmd
lin regr done

--- 2023-04-22 Draft.Rmd
@@
 K-nearest neighbors (kNN) returns predicted PM2.5 values based on their neighboring data points.
-INSERT BOOSTING MODEL SENTENCE.
-Random forest makes an averaged prediction from a collection of independent decision trees.
+**INSERT BOOSTING MODEL SENTENCE.** Random forest makes an averaged prediction from a collection of independent decision trees.
 We predict that the RMSE performance of the bootstrapping model will be the best, with a value of around 0.5.
@@
 library(broom)
+library(xgboost)
 library(caret)
@@
 library(randomForest)
+library(factoextra)
+library(MASS)
 
@@
 # Omit value and id variables since these should not be scaled
-train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) #%>% cbind(state=train$state,county=train$county,city=train$city)
+train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
+#%>% cbind(state=train$state,county=train$county,city=train$city)
 
@@
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Longitude (degrees)", y="PM2.5")
+  labs(title="PM2.5 Concentration vs Longitude", x="Longitude (Degrees)", y="PM2.5 (mu g/m^3)")
 
@@
   geom_point() + geom_smooth() + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="Latitude (degrees)", y="PM2.5")
+  labs(title="PM2.5 Concentration vs Latitude", x="Latitude (Degrees)", y="PM2.5 (mu g/m^3)")
 
 origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
-  labs(title="PM2.5 Concentration (mu g/m^3)", x="State", y="PM2.5") 
+  labs(title="PM2.5 Concentration", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") + theme(legend.position='none')
 ```
@@
 import=tibble::rownames_to_column(import, 'variables')
-# Now from this list, you can select the variables. Mostly, the top 20 variables are what we select. However, this is just an indicative value and may vary based upon the problem.
 
@@
 varimpAUC(cf1)
-
-# Scale dataset
-# Covar. matrix
-# Eigenval.s and eigenvec.s
-# PCA
-# Data transformation in new dimensional space
 ```
@@
 ## Models 
-```{r Lin Regr.}
-model1 <- linear_reg() %>% 
-    set_engine("lm") %>% 
-    set_mode("regression")
+```{r Linear}
+set.seed(123)
+# Fit model and get summary
+fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train)
+step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
+# Drops county_area, popdens_county, and log_nei_2008_pm25_sum_10000
 
-imp = varImp(model1, scale=FALSE)
-
-fit1 = model1 |> fit(value ~ ., data=train_scaled)
-x=summary(fit1$fit)$coefficients
-
-tidy(fit1)
-glance(fit1)
-
-wf1 <- workflow() %>% 
-    add_recipe(rec1) %>% 
-    add_model(model1)
-
-res1 = wf1 |> last_fit(split=dat_split)
-res1 |> collect_metrics()
-
-library(MASS)
-fit <- lm(value ~ .,data=train_scaled)
-step <- stepAIC(fit, direction="forward")
-step$anova
-
-```
-
-```{r Linear Regression}
-set.seed(123)
 # Create the recipe for all models
-rec <- train %>% 
-    recipe(value ~ )
+rec1 <- train %>% 
+    recipe(value ~ CMAQ+lat+lon+aod+zcta+log_nei_2008_pm25_sum_10000)
 
@@
 wf1 <- workflow() %>% 
-    add_recipe(rec) %>% 
+    add_recipe(rec1) %>% 
     add_model(model1)
@@
 
-res1 <- fit(wf1, data = train)
+res1 <- wf1 |> parsnip::fit(data = train)
 
@@
 # Check linear regression model performance using cross-validation
-
 folds1 <- vfold_cv(train, v = 10)
-folds1
+# folds1
 res1 <- fit_resamples(wf1, resamples = folds1)
@@
 # Scale the training data for k-NN model in wrangling
+train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
+#%>% cbind(state=train$state,county=train$county,city=train$city)
 

### 2023-04-22 Draft.Rmd
Update Draft.Rmd

@@
 ## Models
+
 ```{r Linear}
@@
 
-```{r kNN}
+```{r kNN ALL MODELS FAILED}
 set.seed(123)

### 2023-04-22 AileensCode.Rmd
a

@@
 ```{r cars}
-summary(cars)
+
+```{r delete}
+# Use Information Gain for variable selection
+library(MASS)
+fit_lm = lm(value~, data=train)
+stepAIC(fit_lm, direction="backward", trace=FALSE)
+stepAIC(fit_lm, direction="forward", trace=FALSE)
+stepAIC(fit_lm, direction="both", trace=FALSE)
+
+# Use Recursive Feature Elimination method
+set.seed(123)
+cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
+profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)
+
+# Use Lasso for variable selection X
+y=train[,2]
+library(glmnet)
+feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
+as.matrix(coef(features,features$lambda.min))
+
+# fit randfom forest and get var. importance based on mean decr. in accuracy
+set.seed(123)
+library(party)
+train_num = train[,2:50] |> dplyr::select(where(is.numeric))
+cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
+# adj for corr. btw predictors
+varimp(cf1, conditional=TRUE)
+# more robust towards class imbalance
+varimpAUC(cf1)
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-04-22 Draft.Rmd
updtae

--- 2023-04-22 Draft.Rmd
@@
 import10 = import[1:10,]
-```
-
-```{r delete}
-# Use Information Gain for variable selection
-library(MASS)
-fit_lm = lm(value~, data=train)
-stepAIC(fit_lm, direction="backward", trace=FALSE)
-stepAIC(fit_lm, direction="forward", trace=FALSE)
-stepAIC(fit_lm, direction="both", trace=FALSE)
-
-# Use Recursive Feature Elimination method
-set.seed(123)
-cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
-profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)
-
-# Use Lasso for variable selection X
-y=train[,2]
-library(glmnet)
-feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
-as.matrix(coef(features,features$lambda.min))
-
-# fit randfom forest and get var. importance based on mean decr. in accuracy
-set.seed(123)
-library(party)
-train_num = train[,2:50] |> dplyr::select(where(is.numeric))
-cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
-# adj for corr. btw predictors
-varimp(cf1, conditional=TRUE)
-# more robust towards class imbalance
-varimpAUC(cf1)
 ```

### 2023-04-22 Draft.Rmd
yu
Update Draft.Rmd

@@
 # Omit value and id variables since these should not be scaled
-train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
-#%>% cbind(state=train$state,county=train$county,city=train$city)
+train_scaled = train %>% select(-id) %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)
 
@@
 
-```{r kNN}
+```{r kNN uses scaled training data - ALL MODELS FAILED}
 set.seed(123)

### 2023-04-22 Draft.Rmd
updated knn

--- 2023-04-22 Draft.Rmd
@@
 # Omit value and id variables since these should not be scaled
+# train_scaled for PCA
 train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
 #%>% cbind(state=train$state,county=train$county,city=train$city)
+
+# train_knn for kNN model
+train_knn = train[,2:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)
 
@@
 
-# Scale the training data for k-NN model in wrangling
-train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
-#%>% cbind(state=train$state,county=train$county,city=train$city)
+# Create recipe
+rec2 = train_knn |> recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000)
 
@@
   wf2 <- workflow() %>% 
-    add_recipe(rec) %>% 
+    add_recipe(rec2) %>% 
     add_model(model2)
@@
 # Fit the model on the training dataset using the `fit()` function
-res2 <- fit(wf2, data = train_scaled)
+res2 <- parsnip::fit(wf2, data = train_knn)
 
@@
 # Check performance using cross-validation
-
 folds2 <- vfold_cv(train, v = 10)
@@
 preprocessing_recipe <- 
-  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
+  recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data = training(dat_split)) %>%
   # Convert categorical variables to factors
@@
 
-knitr::kable(head(xgboost_grid))
+head(xgboost_grid)
 
@@
 # Hyperparameter tuning
-# Takes a long time to run
+# Takes a long time to run, 5 min
 xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds3,
-  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq, mae),
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
   control = tune::control_grid(verbose = TRUE))
@@
 xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
-knitr::kable(xgboost_best_params)
+xgboost_best_params
 
@@
   # Fit the model on all the training data
-  fit(formula = value ~ lon+lat, data = train_processed) %>%
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
   # Predict the sale prices for the training data
@@
   mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
-knitr::kable(xgboost_score_train)
+xgboost_score_train
 ```
@@
 # Create Random Forest Model
-set.seed(123)
 # Use grid of tuning parameters

### 2023-04-23 Draft.Rmd
edited
added rf code

@@
 library(MASS)
+library(ranger)
 
@@
 rfmodel = randomForest(value~., data=train[,2:50])
-import=as.data.frame(importance(rfmodel)) |> arrange(desc(IncNodePurity))
+import=as.data.frame(randomForest::importance(rfmodel)) |> arrange(desc(IncNodePurity))
 import=tibble::rownames_to_column(import, 'variables')
@@
 ## Models 
-```{r Linear}
+```{r LinearRegression}
 set.seed(123)
@@
 
-```{r kNN ALL MODELS FAILED}
+```{r kNearestNeighbors}
+# kNN uses scaled data called train_knn
 set.seed(123)
@@
 set.seed(123)
-# Preprocessing "recipe"
+# Preprocessing recipe
 preprocessing_recipe <- 
@@
   add_model(xgboost_model) %>% 
-  add_formula(value~lon+lat)
+  add_formula(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000)
 
 # Hyperparameter tuning
-# Takes a long time to run, 5 min
+# Takes a long time to run, 5-8 min
 xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds3,
@@
 
-# Eval. model performance on test data
+# Eval. model performance on train data
 train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
@@
              log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
-  # Predict the sale prices for the training data
+  # Predict value for the training data
   predict(new_data = train_processed) %>%
@@
 
-```{r Random Forest}
+```{r RandomForest}
 set.seed(123)
-# Create Random Forest Model
-# Use grid of tuning parameters
-model4 <- rand_forest(mtry = tune("mtry"),
-                     min_n = tune("min_n")) %>% 
-    set_engine("ranger") %>% 
-    set_mode("regression")
-# Create workflow
-  wf4 <- workflow() %>% 
-    add_recipe(rec) %>% 
-    add_model(model4)
+# Preprocessing recipe
+rec4 <- recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train) %>%
+  step_log(all_outcomes()) |> 
+  step_normalize(all_numeric_predictors()) |> 
+  step_dummy(all_nominal_predictors())
 
-# Fit the model on the full training dataset using the `fit()` function
-res4 <- fit(wf4, data = train_scaled)
-# Check performance on the complete training data
-res4 %>% 
-    extract_fit_engine() %>% 
-    summary()
-# Check performance using cross-validation
-folds4 <- vfold_cv(train, v = 10)
-folds4
-# Determine performance of model by resampling
-res4 <- fit_resamples(wf4, folds4) # ERROR Assigned data `orig_rows` must be compatible with existing data.
-res4 %>% 
-    collect_metrics()
-
-## Try a grid of tuning parameters
-model <- rand_forest(mtry = tune("mtry"),
-                     min_n = tune("min_n")) %>% 
-    set_engine("ranger") %>% 
+#  Create model specification and wf
+rf_spec <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>%
+  set_engine("ranger", num.threads=7, importance="impurity") |> 
   set_mode("regression")
@@
 wf4 <- workflow() %>%
-    add_recipe(rec) %>% 
-    add_model(model)
+  add_recipe(rec4) %>%
+  add_model(rf_spec)
 
-## Fit model over grid of tuning parameters
-res <- tune_grid(wf4, resamples = folds4, grid = 20)
+folds4 = recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
 
-res %>% 
-    collect_metrics()
+# Space-filling designs grid
+rf_grid <- grid_latin_hypercube(min_n(), mtry(range = c(4, 9)), trees(), size = 60)
+
+# Tuning hyperparameters
+library(doParallel)
+all_cores = parallel::detectCores(logical=FALSE)
+cl = makePSOCKcluster(all_cores)
+doParallel::registerDoParallel(cl)
+
+# Takes long time to load 2 min
+tune_res <- wf4 |> tune_grid(resamples = folds4, grid = rf_grid, metrics=metric_set(rmse,rsq), control = tune::control_grid(verbose = TRUE))
+tune_res
+
+# Find hyper parameter values which performed best at minimizing RMSE
+tune_res %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+rf_best_params <- tune_res %>% tune::select_best("rmse")
+rf_best_params
+
+# Final Random Forest model
+rf_model_final <- rf_spec %>% finalize_model(rf_best_params)
+
+# Check Random Forest model performance
+train_processed2 <- bake(preprocessing_recipe,  new_data = training(dat_split))
+
+train_prediction2 = rf_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train_processed2) |> 
+  predict(new_data=train_processed2) |> 
+  bind_cols(training(dat_split))
+
+rf_score_train = train_prediction2 |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+rf_score_train
 ```

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 ## Wrangling
+We split 80% of the origin dataset into training and 20% into testing.
+Then, we scaled the training datasets for PCA and kNN since both of these require little variance among the variables in the dataset.
+We omitted the 'id' and 'value' variables from the 'trained_scaled' dataset for PCA because the 'id' values for the monitors would not provide any useful insight on PM2.5 concentration and the 'value' itself is not a predictor.
+Next, we chose 12 principal components with the highest explained variance since the sum of these components met our threshold of 80% explained variance.
+Then, we tried to see which variables contributed the most to 'value' and reduced the dimension of the 'trained_scale' dataset based on these variables.
+For kNN, we created a scaled training set 'train_knn' since extreme values would bias the distance calculation used in kNN modeling.
+For the other models, the regular 'train' set since the variables' values do not affect their prediction performance.
+Lastly, we did some exploratory analysis to see the linear relationship between longitude and latitude with PM2.5 concentration.
 ```{r Predictors}
@@
 ## Predictor/Feature Selection
+We used random forest (RF) to determine which variables would be the best predictors for our model since RF is good at using variance to determine which features would be most influential for a model's predictive performance.
+In other words, the more variability there is in a dataset, the better RF performs at predicting which variables contribute to the outcome by averaging the results of all trees at the end and this averaging reduces the model's variance.
+Since our dataset has a wide variety of predictors ranging from education attainment levels to poverty levels in a given monitor region to emission data, RF would be good at reducing the variance in our dataset.
+For a given feature, the lower its impurity levels are, the more important that feature is.
+As a result, we took the top 10 important variables as input for the training set for our models.
 ```{r}

### 2023-04-23 Draft.Rmd
edited wrangling txt

@@
 Then, we scaled the training datasets for PCA and kNN since both of these require little variance among the variables in the dataset.
-We omitted the 'id' and 'value' variables from the 'trained_scaled' dataset for PCA because the 'id' values for the monitors would not provide any useful insight on PM2.5 concentration and the 'value' itself is not a predictor.
+We omitted the 'id' and 'value' variables from the 'trained_scaled' dataset for PCA because the 'id' values for the monitors would not provide any useful insight on PM2.5 concentration and 'value' is not a predictor.
 Next, we chose 12 principal components with the highest explained variance since the sum of these components met our threshold of 80% explained variance.
@@
 For kNN, we created a scaled training set 'train_knn' since extreme values would bias the distance calculation used in kNN modeling.
-For the other models, the regular 'train' set since the variables' values do not affect their prediction performance.
+The other models either used 'train' dataset since the variables' values do not affect their prediction performance or used a specially altered version of it.
 Lastly, we did some exploratory analysis to see the linear relationship between longitude and latitude with PM2.5 concentration.
@@
   labs(title="PM2.5 Concentration vs Latitude", x="Latitude (Degrees)", y="PM2.5 (mu g/m^3)")
-
-origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
-  labs(title="PM2.5 Concentration", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") + theme(legend.position='none')
 ```
@@
 ## Predictor/Feature Selection
-We used random forest (RF) to determine which variables would be the best predictors for our model since RF is good at using variance to determine which features would be most influential for a model's predictive performance.
+We used the random forest algorithm (RF) to determine which variables would be the best predictors for our model since RF is good at using variance to determine which features would be most influential for a model's predictive performance.
 In other words, the more variability there is in a dataset, the better RF performs at predicting which variables contribute to the outcome by averaging the results of all trees at the end and this averaging reduces the model's variance.
@@
 For a given feature, the lower its impurity levels are, the more important that feature is.
-As a result, we took the top 10 important variables as input for the training set for our models.
+As a result, we got an ordered list of important variables and took the top 10 as input for the training set for our models.
+The top 10 important predictors were CMAQ, lat, county_area, lon, aod, popdens_county, zcta, log_nei_2008_pm25_sum_10000, and log_nei_2008_pm10_sum_10000.
+
 ```{r}

### 2023-04-23 Draft.Rmd
added knn txt

@@
 ## Models 
+### 1. Linear Regression
 ```{r LinearRegression}
@@
 ```
+
+We first found the ideal number of k neighbors.
+This was determined by finding the square root of the number of observations, which was rounded to be 26.
+We fit the model on the training set data and checked its performance using two methods: one is fitting the model to extracting the MAE and MSE and the other is k-fold cross validation.
+RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
 

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 ## Models 
+For linear regression (LR), the unscaled training set was used since variance does not affect the prediction performance of this model.
+Step Akaike Information Criteria (AIC) was used to simplify feature amount without impacting the model's performance.
+Features are dropped as the AIC score decreases and feature dropping stops once the AIC score increaes.
+'CMAQ,' 'lat,' 'lon,' 'aod,' 'zcta,' and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe 'rec1.' Then, model was fitted and the summary of the model had a RMSE of 2.22 performance of the linear regression model.
+After sampling on 10 subsets of the training set, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
 ### 1. Linear Regression

### 2023-04-23 Draft.Rmd
xgboost title

--- 2023-04-23 Draft.Rmd
@@
 Lastly, we did some exploratory analysis to see the linear relationship between longitude and latitude with PM2.5 concentration.
+
 ```{r Predictors}
@@
 As a result, we got an ordered list of important variables and took the top 10 as input for the training set for our models.
-The top 10 important predictors were CMAQ, lat, county_area, lon, aod, popdens_county, zcta, log_nei_2008_pm25_sum_10000, and log_nei_2008_pm10_sum_10000.
+The top 10 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', 'aod', 'popdens_county', 'zcta', 'log_nei_2008_pm25_sum_10000', and 'log_nei_2008_pm10_sum_10000'.
 
@@
 ### 1. Linear Regression
+For linear regression (LR), the unscaled training set was used since variance does not affect the prediction performance of this model.
+Step Akaike Information Criteria (AIC) was used to simplify feature amount without impacting the model's performance.
+Features are dropped as the AIC score decreases and feature dropping stops once the AIC score increases.
+'CMAQ,' 'lat,' 'lon,' 'aod,' 'zcta,' and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe.
+Then, model was fitted.
+Using the summary function, we found the LR model had a RMSE of 2.22 performance.
+After sampling on 10 subsets of the training set, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
+
 ```{r LinearRegression}
@@
 
+### 2. K-Nearest Neighbors
+
 We first found the ideal number of k neighbors.
 This was determined by finding the square root of the number of observations, which was rounded to be 26.
-We fit the model on the training set data and checked its performance using two methods: one is fitting the model to extracting the MAE and MSE and the other is k-fold cross validation.
+We fit the model on the training set data and checked its performance using two methods: the first was fitting the model to extracting the MAE and MSE and the second was k-fold cross validation.
 RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
@@
 
+### 3. Extreme Gradient Boost
 Preprocessing requirements
@@
 ```
+
+### 4. Random FOrest Regression
 

### 2023-04-23 Draft.Rmd
added rmse table

@@
 
+### Best Model
+The following code creates a table containing the RMSE and RSQ estimates for each of our four models.
+```{r}
+# Create table of prediction metrics
+linreg = res1 |> collect_metrics() |> as.data.frame()
+linreg = cbind(linreg[,1], round(linreg[,3],2))
+knn = res2 %>% collect_metrics() |> as.data.frame()
+knn = cbind(knn[,1], round(knn[,3],2))
+xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
+xgboost = cbind(xgboost[,1], xgboost[,3])
+ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
+ranfor = cbind(ranfor[,1], ranfor[,3])
+
+compare = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg,knn,xgboost,ranfor))
+colnames(compare) = c('model','estimator','estimate')
+tibble(compare)
+```
+
+As seen on the table, the Random Forest model has the lowest RMSE and is thus the best and final model based on our procedure.
+
 ## Results

### 2023-04-23 Draft.Rmd
edited intro

@@
 So being able to predict the average PM2.5 concentrations ($\mu$g/m$^3$) will allow us to keep people most vulnerable safe as we look for and implement changes to improve the air quality in the region.
-We chose the predictors by …
-For our four models, we chose linear regression, k-nearest neighbors, xgboosting, and random forest.
-Linear regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
-K-nearest neighbors (kNN) returns predicted PM2.5 values based on their neighboring data points.
-**INSERT BOOSTING MODEL SENTENCE.** Random forest makes an averaged prediction from a collection of independent decision trees.
-We predict that the RMSE performance of the bootstrapping model will be the best, with a value of around 0.5.
+We created four models to predict the annual average of ambient air pollution in a location based on the variables in the dataset.
+For our four models, we chose Linear Regression, K-Nearest Neighbors, Xgboosting, and Random Forest.
+Linear Regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
+K-Nearest Neighbors returns predicted PM2.5 values based on their neighboring data points.
+Xgboosting predicts PM2.5 values by combining the estimates of a set of simpler, weaker models.
+Random forest makes an averaged prediction from a collection of independent decision trees.
+We hypothesize that the RMSE performance of the Xgboosting model will be the best, with a value of around 0.5.
 
@@
 library(ranger)
+library(doParallel)
 
@@
 ## Wrangling
+
 We split 80% of the origin dataset into training and 20% into testing.
@@
 
-```{r Predictors}
+```{r ExploratoryAnalysis}
 set.seed(123)
@@
 
-## Predictor/Feature Selection
+## Predictor/Feature Extraction
+
 We used the random forest algorithm (RF) to determine which variables would be the best predictors for our model since RF is good at using variance to determine which features would be most influential for a model's predictive performance.
@@
 ### 3. Extreme Gradient Boost
+
 Preprocessing requirements
@@
 # Tuning hyperparameters
-library(doParallel)
 all_cores = parallel::detectCores(logical=FALSE)
@@
 
-As seen on the table, the Random Forest model has the lowest RMSE and is thus the best and final model based on our procedure.
+As seen on the table, the Random Forest model has the lowest RMSE of 0.62.
+Since we are choosing the best model by RMSE, the Random Forest model is thus the best and final model based on our procedure.
 

### 2023-04-23 Draft.Rmd
fghjk
Update Draft.Rmd

@@
 The top 10 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', 'aod', 'popdens_county', 'zcta', 'log_nei_2008_pm25_sum_10000', and 'log_nei_2008_pm10_sum_10000'.
+This website was used [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
 
@@
 
-### 3. Extreme Gradient Boost
+### 3. Extreme Gradient Boost Regression
+The Extreme Gradient (XG) Boosting model performs by training weak learners, models that have low prediction accuracy, sequentially to become a single strong learner, a model that has strong prediction accuracy.
+We preprocess the training set to make the predictive modeling process more accurate and smoother by prepping (estimates the quantities for 'train_scaled') and baking (assigns prepped data to an object) the data.
+The aforementioned top 10 predictors were used in this preprocessing recipe.
+Moreover, the categorical variables were factored and features with no variance were removed before this data was baked.
+Then, this processed data is assigned to 'folds3' and resampled on 5 subsets of the training set.
+We tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+low prediction error).
+Next, we isolated the best hyperparameter values, so they can be used for the final boosting model.
+Lastly, we fitted the model and evaluated its prediction performance.
+Its RMSE score was .71, indicating the XG Boosting is a good model.
 

### 2023-04-23 Draft.Rmd
best model

@@
 We created four models to predict the annual average of ambient air pollution in a location based on the variables in the dataset.
-For our four models, we chose Linear Regression, K-Nearest Neighbors, Xgboosting, and Random Forest.
+We chose our predictors using the Random Forest algorithm.
+And for our four models, we chose Linear Regression, K-Nearest Neighbors, Xgboosting, and Random Forest.
 Linear Regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
@@
 
-## Predictor/Feature Extraction
+## Results
+### Predictor/Feature Extraction
 
@@
 The top 10 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', 'aod', 'popdens_county', 'zcta', 'log_nei_2008_pm25_sum_10000', and 'log_nei_2008_pm10_sum_10000'.
+We will use these features to predict 'value' proceeding onwards.
 This website was used [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
@@
 
-## Models 
+### Models 
 ### 1. Linear Regression
@@
 
+The K-Nearest Neighbors (KNN) model finds the predicted 'value' by taking the average 'value' of its k neighbors.
 We first found the ideal number of k neighbors.
 This was determined by finding the square root of the number of observations, which was rounded to be 26.
-We fit the model on the training set data and checked its performance using two methods: the first was fitting the model to extracting the MAE and MSE and the second was k-fold cross validation.
+We fit the model on the training set data and checked its performance using two methods: the first was fitting the model to extracting the MAE and MSE and the second was 10-fold cross validation.
 RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
+We found that after 10-fold cross validation, the RMSE was 1.79.
+This indicates that the model does not predict well.
 
@@
 ### 3. Extreme Gradient Boost Regression
-The Extreme Gradient (XG) Boosting model performs by training weak learners, models that have low prediction accuracy, sequentially to become a single strong learner, a model that has strong prediction accuracy.
+
+The Extreme Gradient Boosting (XGB) model performs by training weak learners, models that have low prediction accuracy, sequentially to become a single strong learner, a model that has strong prediction accuracy.
 We preprocess the training set to make the predictive modeling process more accurate and smoother by prepping (estimates the quantities for 'train_scaled') and baking (assigns prepped data to an object) the data.
@@
 Its RMSE score was .71, indicating the XG Boosting is a good model.
-
-Preprocessing requirements
-xgboost does not have a means to translate factor predictors to grouped splits.
-Factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) for this engine.
-When using the formula method via fit.model_spec(), parsnip will convert factor columns to indicators using a one-hot encoding.
 
@@
 ### Best Model
+
 The following code creates a table containing the RMSE and RSQ estimates for each of our four models.
+
 ```{r}
@@
 colnames(compare) = c('model','estimator','estimate') 
+compare = as.data.frame(compare) |> pivot_wider(names_from=estimator, values_from=estimate)
 tibble(compare)
@@
 
-As seen on the table, the Random Forest model has the lowest RMSE of 0.62.
+As seen on the table, LR has the lowest r-squared estimate and highest RMSE while RF is the opposite.
+KNN has the second highest RMSE with a moderate r-squared estimate.
+And XGB has both a high RMSE and r-squared estimate.
+Random Forest model has the lowest RMSE of 0.62 and highest r-squared estimate.
 Since we are choosing the best model by RMSE, the Random Forest model is thus the best and final model based on our procedure.
@@
 ## Results
-Describe the development of your 3 prediction models (or 4 models, if working in a group) and
-how you compared their performance. 
-Be sure to describe the splitting of training and testing datasets 
-and the use of cross-validation to evaluate prediction metrics. 
-Remember that the primary metric for your prediction model will be root-mean-squared error (RMSE). 
 Your results should include 
 at least one visualization demonstrating the prediction performance of your models.
-You should also include 
-a table summarizing the prediction metrics (including RMSE) across all of the models that you tried.
 

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 ### 4. Random FOrest Regression
+The Random Forest (RF) Regression model performs by training multiple different samples simultaneously and averages the outcome at the end for the final prediction.
+The randomness of these samples contribute to the prediction accuracy of this model.
+Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve make the predictive modeling process and then create model specifications.
+This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set.
+We tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+low prediction error).
+Next, we isolated the best hyperparameter values, so they can be used for the final boosting model.
+Lastly, we fitted the model and evaluated its prediction performance.
+Its RMSE score was .62, indicating the RF is a good predictive model.
 

### 2023-04-23 Draft.Rmd
hhh

--- 2023-04-23 Draft.Rmd
@@
 
-```{r}
+```{r Library}
 library(tidyverse)
@@
 train <- training(dat_split)
+test <- data[dat_split==1, ]
 
@@
 1. Based on test set performance, at what locations does your model give predictions that
-are closest and furthest from the observed values? What do you hypothesize are the
-reasons for the good or bad performance at these locations?
-2. What variables might predict where your model performs well or not? For example, are
-their regions of the country where the model does better or worse? Are there variables
-that are not included in this dataset that you think might improve the model performance
-if they were included in your model?
+are closest and furthest from the observed values? What do you hypothesize are the reasons for the good or bad performance at these locations?
+
+2. What variables might predict where your model performs well or not? For example, are their regions of the country where the model does better or worse? Are there variables
+that are not included in this dataset that you think might improve the model performance if they were included in your model?
+
 3. There is interest in developing more cost-effect approaches to monitoring air pollution
-on the ground. Two candidates for replacing the use of ground-based monitors are
-numerical models like CMAQ and satellite-based observations such as AOD. How well do
-CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction
-performance of your model change when CMAQ or aod are included (or not included) in
+on the ground. Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD. How well do
+CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction performance of your model change when CMAQ or aod are included (or not included) in
 the model?
+
 4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
@@
 Putting it all together, what did you learn from your data and your model performance?
+
 • Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
+
 • Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
+
 • Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
+
 • Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).

### 2023-04-23 Draft.Rmd
ppp

@@
 train <- training(dat_split)
-test <- data[dat_split==1, ]
+test <- testing(dat_split)
 
@@
 ```{r}
-# Create table of prediction metrics
-linreg = res1 |> collect_metrics() |> as.data.frame()
-linreg = cbind(linreg[,1], round(linreg[,3],2))
-knn = res2 %>% collect_metrics() |> as.data.frame()
-knn = cbind(knn[,1], round(knn[,3],2))
-xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
-xgboost = cbind(xgboost[,1], xgboost[,3])
-ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
-ranfor = cbind(ranfor[,1], ranfor[,3])
+# Create table of prediction metrics from training data
+linreg1 = res1 |> collect_metrics() |> as.data.frame()
+linreg1 = cbind(linreg1[,1], round(linreg1[,3],2))
+knn1 = res2 %>% collect_metrics() |> as.data.frame()
+knn1 = cbind(knn1[,1], round(knn1[,3],2))
+xgboost1 = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
+xgboost1 = cbind(xgboost1[,1], xgboost1[,3])
+ranfor1 = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
+ranfor1 = cbind(ranfor1[,1], ranfor1[,3])
 
-compare = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg,knn,xgboost,ranfor))
-colnames(compare) = c('model','estimator','estimate') 
-compare = as.data.frame(compare) |> pivot_wider(names_from=estimator, values_from=estimate)
-tibble(compare)
+compare1 = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg1,knn1,xgboost1,ranfor1))
+colnames(compare1) = c('model','estimator','estimate') 
+compare1 = as.data.frame(compare1) |> pivot_wider(names_from=estimator, values_from=estimate)
+tibble(compare1)
+
+# Get pred. metrics from models based on testing data
+# LR
+
+# KNN
+
+# XGB
+
+# RF
+
 ```

### 2023-04-23 Draft.Rmd
Update Draft.Rmd
added fips

@@
 fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train)
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train)
 step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
@@
 RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
-We found that after 10-fold cross validation, the RMSE was 1.79.
+We found that after 10-fold cross validation, the RMSE was 1.78.
 This indicates that the model does not predict well.
@@
 rec2 = train_knn |> recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000)
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
 
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was .71, indicating the XG Boosting is a good model.
+Its RMSE score was .42, indicating the XG Boosting is a good model.
 
@@
   recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data = training(dat_split)) %>%
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = training(dat_split)) %>%
   # Convert categorical variables to factors
@@
   add_formula(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000)
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
 
@@
 rec4 <- recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train) %>%
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train) %>%
   step_log(all_outcomes()) |> 
@@
 tune_res <- wf4 |> tune_grid(resamples = folds4, grid = rf_grid, metrics=metric_set(rmse,rsq), control = tune::control_grid(verbose = TRUE))
-tune_res
+# tune_res
 
@@
   parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train_processed2) |> 
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed2) |> 
   predict(new_data=train_processed2) |> 
@@
 # Create table of prediction metrics from training data
-linreg1 = res1 |> collect_metrics() |> as.data.frame()
-linreg1 = cbind(linreg1[,1], round(linreg1[,3],2))
-knn1 = res2 %>% collect_metrics() |> as.data.frame()
-knn1 = cbind(knn1[,1], round(knn1[,3],2))
-xgboost1 = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
-xgboost1 = cbind(xgboost1[,1], xgboost1[,3])
-ranfor1 = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
-ranfor1 = cbind(ranfor1[,1], ranfor1[,3])
+linreg = res1 |> collect_metrics() |> as.data.frame()
+linreg = cbind(linreg[,1], round(linreg[,3],2))
+knn = res2 %>% collect_metrics() |> as.data.frame()
+knn = cbind(knn[,1], round(knn[,3],2))
+xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
+xgboost = cbind(xgboost[,1], xgboost[,3])
+ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
+ranfor = cbind(ranfor[,1], ranfor[,3])
 
-compare1 = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg1,knn1,xgboost1,ranfor1))
-colnames(compare1) = c('model','estimator','estimate') 
-compare1 = as.data.frame(compare1) |> pivot_wider(names_from=estimator, values_from=estimate)
-tibble(compare1)
+compare = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg,knn,xgboost,ranfor))
+colnames(compare) = c('model','estimator','estimate') 
+compare = as.data.frame(compare) |> pivot_wider(names_from=estimator, values_from=estimate)
+compare
 
-# Get pred. metrics from models based on testing data
-# LR
+# Fit RF model to testing data
+test_processed <- bake(preprocessing_recipe,  new_data = testing(dat_split))
 
-# KNN
+# Get pred. metrics based on testing data
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=test_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
 
-# XGB
-
-# RF
-
+xgb_score_test = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+xgb_score_test
 ```
 
-As seen on the table, LR has the lowest r-squared estimate and highest RMSE while RF is the opposite.
-KNN has the second highest RMSE with a moderate r-squared estimate.
-And XGB has both a high RMSE and r-squared estimate.
-Random Forest model has the lowest RMSE of 0.62 and highest r-squared estimate.
-Since we are choosing the best model by RMSE, the Random Forest model is thus the best and final model based on our procedure.
+As seen on the table, LR has the highest RMSE and lowest r-squared estimate.
+KNN has the second highest RMSE with a moderate R-squared estimate.
+And XGB has the lowest RMSE of 0.42 and the highest R-squared estimate of 0.98.
+Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
+Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 0.39 and 0.98 respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 98% of the variance in the data, which means this model fits the data well.
 

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 the model?
+- create visualization showing how close features CMAQ and AOD predict values of PM2.5 to actual/observed values
 
@@
 will perform well or not in those two states? Explain your reasoning
+Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the origin dataset included states of varying sizes and pollution levels.
+Moreover, its RMSE score is .42 and R^2 is .98, indicating that the prediction performance of this model is excellent.
+Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also interrelatedness in this dataset aids the model in learning the different environments in which pollution occurs.
 

### 2023-04-23 Draft.Rmd
edited rf txt

--- 2023-04-23 Draft.Rmd
@@
 We will use these features to predict 'value' proceeding onwards.
-This website was used [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
+This website was used:[TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
 
@@
 step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
-# Drops county_area, popdens_county, and log_nei_2008_pm25_sum_10000
+# Drops county_area, popdens_county, fips, and log_nei_2008_pm25_sum_10000
 
@@
 Its RMSE score was .42, indicating the XG Boosting is a good model.
+This website was used:[RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
 

### 2023-04-23 Draft.Rmd
edited rf txt

--- 2023-04-23 Draft.Rmd
@@
 We will use these features to predict 'value' proceeding onwards.
-This website was used:[TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
+This website was used: [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
 
@@
 Features are dropped as the AIC score decreases and feature dropping stops once the AIC score increases.
-'CMAQ,' 'lat,' 'lon,' 'aod,' 'zcta,' and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe.
+'CMAQ', 'lat', 'lon', 'aod', 'zcta', and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe.
 Then, model was fitted.
 Using the summary function, we found the LR model had a RMSE of 2.22 performance.
-After sampling on 10 subsets of the training set, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
+After 10-fold cross validation, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
 
@@
 We found that after 10-fold cross validation, the RMSE was 1.78.
-This indicates that the model does not predict well.
+This indicates that the model does not predict well since there is such a large amount of error.
 
@@
 Then, this processed data is assigned to 'folds3' and resampled on 5 subsets of the training set.
-We tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+Using 'fold3', we tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
 low prediction error).
@@
 Its RMSE score was .42, indicating the XG Boosting is a good model.
-This website was used:[RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
+This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
 
@@
 ### 4. Random FOrest Regression
+
 The Random Forest (RF) Regression model performs by training multiple different samples simultaneously and averages the outcome at the end for the final prediction.
@@
 Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve make the predictive modeling process and then create model specifications.
-This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set.
-We tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set to tune the hyperparameters.
+We then perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
 low prediction error).
@@
 After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 0.39 and 0.98 respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 98% of the variance in the data, which means this model fits the data well.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 98% of the variance in the data, which means this model fits/predicts the data well.
 
 ## Results
+```{r Results}
+
+```
+
 Your results should include 
@@
 
-1. Based on test set performance, at what locations does your model give predictions that
-are closest and furthest from the observed values? What do you hypothesize are the reasons for the good or bad performance at these locations?
+**1.
+Based on test set performance, at what locations does your model give predictions that are closest and furthest from the observed values?
+What do you hypothesize are the reasons for the good or bad performance at these locations?**
 
-2. What variables might predict where your model performs well or not? For example, are their regions of the country where the model does better or worse? Are there variables
-that are not included in this dataset that you think might improve the model performance if they were included in your model?
+**2.
+What variables might predict where your model performs well or not?
+For example, are their regions of the country where the model does better or worse?
+Are there variables that are not included in this dataset that you think might improve the model performance if they were included in your model?**
 
-3. There is interest in developing more cost-effect approaches to monitoring air pollution
-on the ground. Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD. How well do
-CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction performance of your model change when CMAQ or aod are included (or not included) in
-the model?
+**3.
+There is interest in developing more cost-effect approaches to monitoring air pollution on the ground.
+Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD.
+How well do CMAQ and AOD predict ground-level concentrations of PM2.5?
+How does the prediction performance of your model change when CMAQ or AOD are included (or not included) in the model?**
+
 - create visualization showing how close features CMAQ and AOD predict values of PM2.5 to actual/observed values
+- no cmaq and no aod models
 
-4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
-will perform well or not in those two states? Explain your reasoning
+```{r Q3}
+
+```
+
+**4. The dataset here did not include data from Alaska or Hawaii. Do you think your model will perform well or not in those two states? Explain your reasoning.**
+
+Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the original dataset included states of varying sizes with different climates and pollution levels.
+Moreover, its RMSE score is 0.42 and R-squared is 0.98, indicating that the prediction performance of this model is excellent.
+Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also inter-relatedness of the features in this dataset aids the model in predicting ambient air pollution in differing environments.
 

### 2023-04-23 Draft.Rmd
changed rmse

@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was .42, indicating the XG Boosting is a good model.
+Its RMSE score was 0.56, indicating the XG Boosting is a good model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.42 and the highest R-squared estimate of 0.98.
+And XGB has the lowest RMSE of 0.56 and the highest R-squared estimate of 0.96.
 Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
 Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 0.39 and 0.98 respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 98% of the variance in the data, which means this model fits/predicts the data well.
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 0.61 and 0.94, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.61 $\mu$g/m$^3$, and that the features we used in our model are able to explain 94% of the variance in the data, which means this model fits/predicts the data well.
 
@@
 ```{r Results}
+compare |> ggplot(aes(y=rmse)) + geom_bar()
 

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
   parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
   # Predict value for the training data
@@
 Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the original dataset included states of varying sizes with different climates and pollution levels.
-Moreover, its RMSE score is 0.42 and R-squared is 0.98, indicating that the prediction performance of this model is excellent.
+Moreover, its RMSE score is 0.62 and R-squared is 0.94, indicating that the prediction performance of this model is good in relation to the other models.
 Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also inter-relatedness of the features in this dataset aids the model in predicting ambient air pollution in differing environments.

### 2023-04-23 Draft.Rmd
pred test train

@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was 0.56, indicating the XG Boosting is a good model.
+Its RMSE score was 0.55, indicating the XG Boosting is a good model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 
-### 4. Random FOrest Regression
+### 4. Random Forest Regression
 
@@
 
-```{r}
+```{r Best&Final}
 # Create table of prediction metrics from training data
@@
 
+# Visual of rmse for our 4 models
+compare |> ggplot(aes(x=model, y=rmse)) + 
+  geom_bar(stat="identity") + 
+  labs(title='RMSE of the Four Models') +
+  theme_minimal()
+
 # Fit RF model to testing data
@@
   parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=test_processed) |> 
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed) |> 
   predict(new_data=test_processed) |> 
@@
 
-As seen on the table, LR has the highest RMSE and lowest r-squared estimate.
+As seen on the table and visual, LR has the highest RMSE and lowest r-squared estimate.
 KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.56 and the highest R-squared estimate of 0.96.
+And XGB has the lowest RMSE of 0.55 and the highest R-squared estimate of 0.96.
 Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
 Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 0.61 and 0.94, respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 0.61 $\mu$g/m$^3$, and that the features we used in our model are able to explain 94% of the variance in the data, which means this model fits/predicts the data well.
-
-## Results
-```{r Results}
-compare |> ggplot(aes(y=rmse)) + geom_bar()
-
-```
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.23 and 0.73, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.23 $\mu$g/m$^3$, and that the features we used in our model are able to explain 73% of the variance in the data, which means this model fits/predicts the data well.
 
@@
 ```{r Q3}
+# Fit RF model to testing data
+
+# Get pred. metrics based on testing data
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=test_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
+
+xgb_score_test = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+xgb_score_test
 
@@
 Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the original dataset included states of varying sizes with different climates and pollution levels.
-Moreover, its RMSE score is 0.62 and R-squared is 0.94, indicating that the prediction performance of this model is good in relation to the other models.
+Moreover, its RMSE score is 0.42 and R-squared is 0.98, indicating that the prediction performance of this model is excellent.
 Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also inter-relatedness of the features in this dataset aids the model in predicting ambient air pollution in differing environments.

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 
-# Fit RF model to testing data
+# Fit XG Boost model to testing data
 test_processed <- bake(preprocessing_recipe, new_data = testing(dat_split))

### 2023-04-23 AileensCode.Rmd
added rf code
top5 and answering Qs

@@
 You can embed an R code chunk like this:
-
-```{r cars}
 
@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
+
+# DRAFT W/ TOP10 NOT TOP5
+## Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.
+
+  Air pollution has consequences for everyone, most especially for those with pre-existing conditions.
+Air pollution is measured in tiny particles or droplets in the air that are two and one-half microns or less in width called PM2.5.
+So being able to predict the average PM2.5 concentrations ($\mu$g/m$^3$) will allow us to keep people most vulnerable safe as we look for and implement changes to improve the air quality in the region.
+We created four models to predict the annual average of ambient air pollution in a location based on the variables in the dataset.
+We chose our predictors using the Random Forest algorithm.
+And for our four models, we chose Linear Regression, K-Nearest Neighbors, Xgboosting, and Random Forest.
+Linear Regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
+K-Nearest Neighbors returns predicted PM2.5 values based on their neighboring data points.
+Xgboosting predicts PM2.5 values by combining the estimates of a set of simpler, weaker models.
+Random forest makes an averaged prediction from a collection of independent decision trees.
+We hypothesize that the RMSE performance of the Xgboosting model will be the best, with a value of around 0.5.
+
+```{r Library}
+library(tidyverse)
+library(tidymodels)
+library(broom)
+library(xgboost)
+library(caret)
+library(plotROC)
+library(randomForest)
+library(factoextra)
+library(MASS)
+library(ranger)
+library(doParallel)
+
+origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
+```
+
+## Wrangling
+
+We split 80% of the origin dataset into training and 20% into testing.
+Then, we scaled the training datasets for PCA and kNN since both of these require little variance among the variables in the dataset.
+We omitted the 'id' and 'value' variables from the 'trained_scaled' dataset for PCA because the 'id' values for the monitors would not provide any useful insight on PM2.5 concentration and 'value' is not a predictor.
+Next, we chose 12 principal components with the highest explained variance since the sum of these components met our threshold of 80% explained variance.
+Then, we tried to see which variables contributed the most to 'value' and reduced the dimension of the 'trained_scale' dataset based on these variables.
+For kNN, we created a scaled training set 'train_knn' since extreme values would bias the distance calculation used in kNN modeling.
+The other models either used 'train' dataset since the variables' values do not affect their prediction performance or used a specially altered version of it.
+Lastly, we did some exploratory analysis to see the linear relationship between longitude and latitude with PM2.5 concentration.
+
+```{r ExploratoryAnalysis}
+set.seed(123)
+# Split origin dataset into 80/20
+dat_split <- initial_split(origin, prop =.8)
+dat_split
+# Use 80% of data for training 
+train <- training(dat_split)
+test <- testing(dat_split)
+
+# Create standardize train data for kNN and PCA
+# Omit value and id variables since these should not be scaled
+# train_scaled for PCA
+train_scaled = train[,3:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) 
+#%>% cbind(state=train$state,county=train$county,city=train$city)
+
+# train_knn for kNN model
+train_knn = train[,2:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)
+
+# Calculate principal components on scaled training data
+pca_result <- train_scaled %>% dplyr::select(where(is.numeric)) %>%
+  prcomp()
+
+# Plot scree plot
+pca_result %>% fviz_eig()
+
+# Plot table to show explained variance % by PCs
+summary(pca_result)
+
+# Threshold of Explained Variance = 80%
+# Calculated the sum of PCs with highest explained variance until threshold was meant
+0.3253 + 0.09749 + 0.07984 + 0.06501 + 0.05196 + 0.04147 + 0.03445 +
+0.02926 + 0.02563 + 0.0220 + 0.02127 + 0.0188
+
+PC1 <- pca_result$rotation[,1]
+PC1_scores <- abs(PC1)
+PC1_scores_ordered <- sort(PC1_scores, decreasing = TRUE)
+names(PC1_scores_ordered)
+
+# Reduce dimension of dataset
+trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
+# Add the center (and re-scale) back to data 
+if(all(pca_result$scale != FALSE)){
+  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
+  } 
+if(all(pca_result$center != FALSE)){ 
+  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
+  } 
+dim(trunc); dim(train_scaled)
+
+# unhelpful plot -- delete
+# plot(pca_result$x[,1], pca_result$x[,2])
+
+# Show which features have the most influence
+as_tibble(pca_result$rotation, 
+          rownames = "variable") %>% 
+    ggplot(aes(variable, PC1)) +
+    geom_point() +
+    coord_flip()
+
+as_tibble(pca_result$rotation, 
+          rownames = "variable") %>% 
+    ggplot(aes(variable, PC2)) +
+    geom_point() +
+    coord_flip()
+
+# Plot clusters between PC1 and PC2 using a biplot
+fviz_pca_var(pca_result)
+
+# Reduce dimension of dataset
+trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
+# Add the center (and re-scale) back to data 
+if(all(pca_result$scale != FALSE)){
+  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
+  } 
+if(all(pca_result$center != FALSE)){ 
+  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
+  } 
+dim(trunc); dim(train_scaled)
+
+# Visualize linear relationship between predictors (lat, lon, state) and value
+origin %>% ggplot(aes(x=lon, y=value)) + 
+  geom_point() + geom_smooth() + 
+  labs(title="PM2.5 Concentration vs Longitude", x="Longitude (Degrees)", y="PM2.5 (mu g/m^3)")
+
+origin %>% ggplot(aes(x=lat, y=value)) + 
+  geom_point() + geom_smooth() + 
+  labs(title="PM2.5 Concentration vs Latitude", x="Latitude (Degrees)", y="PM2.5 (mu g/m^3)")
+```
+
+## Results
+### Predictor/Feature Extraction
+
+We used the random forest algorithm (RF) to determine which variables would be the best predictors for our model since RF is good at using variance to determine which features would be most influential for a model's predictive performance.
+In other words, the more variability there is in a dataset, the better RF performs at predicting which variables contribute to the outcome by averaging the results of all trees at the end and this averaging reduces the model's variance.
+Since our dataset has a wide variety of predictors ranging from education attainment levels to poverty levels in a given monitor region to emission data, RF would be good at reducing the variance in our dataset.
+For a given feature, the lower its impurity levels are, the more important that feature is.
+As a result, we got an ordered list of important variables and took the top 10 as input for the training set for our models.
+The top 10 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', 'aod', 'popdens_county', 'zcta', 'log_nei_2008_pm25_sum_10000', and 'log_nei_2008_pm10_sum_10000'.
+We will use these features to predict 'value' proceeding onwards.
+This website was used: [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
+
+```{r}
+# Use Random Forest for variable selection
+rfmodel = randomForest(value~., data=train[,2:50])
+import=as.data.frame(randomForest::importance(rfmodel)) |> arrange(desc(IncNodePurity))
+import=tibble::rownames_to_column(import, 'variables')
+
+# take top 10 important variables
+import10 = import[1:10,]
+```
+
+### Models 
+### 1. Linear Regression
+For linear regression (LR), the unscaled training set was used since variance does not affect the prediction performance of this model.
+Step Akaike Information Criteria (AIC) was used to simplify feature amount without impacting the model's performance.
+Features are dropped as the AIC score decreases and feature dropping stops once the AIC score increases.
+'CMAQ', 'lat', 'lon', 'aod', 'zcta', and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe.
+Then, model was fitted.
+Using the summary function, we found the LR model had a RMSE of 2.22 performance.
+After 10-fold cross validation, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
+
+```{r LinearRegression}
+set.seed(123)
+# Fit model and get summary
+fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train)
+step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
+# Drops county_area, popdens_county, fips, and log_nei_2008_pm25_sum_10000
+
+# Create the recipe for all models
+rec1 <- train %>% 
+    recipe(value ~ CMAQ+lat+lon+aod+zcta+log_nei_2008_pm25_sum_10000)
+
+# Linear regr. model
+model1 <- linear_reg() %>% 
+    set_engine("lm") %>% 
+    set_mode("regression")
+
+wf1 <- workflow() %>% 
+    add_recipe(rec1) %>% 
+    add_model(model1)
+# wf1
+
+res1 <- wf1 |> parsnip::fit(data = train)
+
+# Check performance of linear regression model on the training data
+res1 %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+# Check linear regression model performance using cross-validation
+folds1 <- vfold_cv(train, v = 10)
+# folds1
+res1 <- fit_resamples(wf1, resamples = folds1)
+res1 %>% 
+    collect_metrics()
+```
+
+### 2. K-Nearest Neighbors
+
+The K-Nearest Neighbors (KNN) model finds the predicted 'value' by taking the average 'value' of its k neighbors.
+We first found the ideal number of k neighbors.
+This was determined by finding the square root of the number of observations, which was rounded to be 26.
+We fit the model on the training set data and checked its performance using two methods: the first was fitting the model to extracting the MAE and MSE and the second was 10-fold cross validation.
+RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
+We found that after 10-fold cross validation, the RMSE was 1.78.
+This indicates that the model does not predict well since there is such a large amount of error.
+
+```{r kNearestNeighbors}
+# kNN uses scaled data called train_knn
+set.seed(123)
+# Find ideal k neighbors
+sqrt(nrow(train))
+
+# Create recipe
+rec2 = train_knn |> recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
+
+# Create kNN model
+model2 <- nearest_neighbor(neighbors = 26) %>% 
+    set_engine("kknn") %>% 
+    set_mode("regression")
+
+# Create workflow
+  wf2 <- workflow() %>% 
+    add_recipe(rec2) %>% 
+    add_model(model2)
+
+# Fit the model on the training dataset using the `fit()` function
+res2 <- parsnip::fit(wf2, data = train_knn)
+
+# Check performance on the complete training data
+res2 %>% 
+    extract_fit_engine() %>% 
+    summary()
+
+# Check performance using cross-validation
+folds2 <- vfold_cv(train, v = 10)
+# folds
+res2 <- fit_resamples(wf2, resamples = folds2) # ERROR Assigned data `orig_rows` must be compatible with existing data.
+res2 %>% 
+    collect_metrics()
+```
+
+### 3. Extreme Gradient Boost Regression
+
+The Extreme Gradient Boosting (XGB) model performs by training weak learners, models that have low prediction accuracy, sequentially to become a single strong learner, a model that has strong prediction accuracy.
+We preprocess the training set to make the predictive modeling process more accurate and smoother by prepping (estimates the quantities for 'train_scaled') and baking (assigns prepped data to an object) the data.
+The aforementioned top 10 predictors were used in this preprocessing recipe.
+Moreover, the categorical variables were factored and features with no variance were removed before this data was baked.
+Then, this processed data is assigned to 'folds3' and resampled on 5 subsets of the training set.
+Using 'fold3', we tune the hyperparameters to make the modeling process more efficient and perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+low prediction error).
+Next, we isolated the best hyperparameter values, so they can be used for the final boosting model.
+Lastly, we fitted the model and evaluated its prediction performance.
+Its RMSE score was 0.55, indicating the XG Boosting is a good model.
+This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
+
+```{r Xgboost}
+set.seed(123)
+# Preprocessing recipe
+preprocessing_recipe <- 
+  recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = training(dat_split)) %>%
+  # Convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # Combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # Remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds3 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
+head(xgboost_grid)
+
+xgboost_wf <- workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
+
+# Hyperparameter tuning
+# Takes a long time to run, 5-8 min
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds3,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
+  control = tune::control_grid(verbose = TRUE))
+
+# Find hyper parameter values which performed best at minimizing RMSE
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
+xgboost_best_params
+
+# Final boost model
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
+
+# Eval. model performance on train data
+train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
+
+train_prediction <- xgboost_model_final %>%
+  # Fit the model on all the training data
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
+  # Predict value for the training data
+  predict(new_data = train_processed) %>%
+  bind_cols(training(dat_split))
+
+xgboost_score_train <- train_prediction %>%
+  yardstick::metrics(value, .pred) %>%
+  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
+xgboost_score_train
+```
+
+### 4. Random Forest Regression
+
+The Random Forest (RF) Regression model performs by training multiple different samples simultaneously and averages the outcome at the end for the final prediction.
+The randomness of these samples contribute to the prediction accuracy of this model.
+Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve make the predictive modeling process and then create model specifications.
+This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set to tune the hyperparameters.
+We then perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+low prediction error).
+Next, we isolated the best hyperparameter values, so they can be used for the final boosting model.
+Lastly, we fitted the model and evaluated its prediction performance.
+Its RMSE score was .62, indicating the RF is a good predictive model.
+
+```{r RandomForest}
+set.seed(123)
+# Preprocessing recipe
+rec4 <- recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train) %>%
+  step_log(all_outcomes()) |> 
+  step_normalize(all_numeric_predictors()) |> 
+  step_dummy(all_nominal_predictors())
+
+#  Create model specification and wf
+rf_spec <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>%
+  set_engine("ranger", num.threads=7, importance="impurity") |> 
+  set_mode("regression")
+
+wf4 <- workflow() %>%
+  add_recipe(rec4) %>%
+  add_model(rf_spec)
+
+folds4 = recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# Space-filling designs grid
+rf_grid <- grid_latin_hypercube(min_n(), mtry(range = c(4, 9)), trees(), size = 60)
+
+# Tuning hyperparameters
+all_cores = parallel::detectCores(logical=FALSE)
+cl = makePSOCKcluster(all_cores)
+doParallel::registerDoParallel(cl)
+
+# Takes long time to load 2 min
+tune_res <- wf4 |> tune_grid(resamples = folds4, grid = rf_grid, metrics=metric_set(rmse,rsq), control = tune::control_grid(verbose = TRUE))
+# tune_res
+
+# Find hyper parameter values which performed best at minimizing RMSE
+tune_res %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+rf_best_params <- tune_res %>% tune::select_best("rmse")
+rf_best_params
+
+# Final Random Forest model
+rf_model_final <- rf_spec %>% finalize_model(rf_best_params)
+
+# Check Random Forest model performance
+train_processed2 <- bake(preprocessing_recipe,  new_data = training(dat_split))
+
+train_prediction2 = rf_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed2) |> 
+  predict(new_data=train_processed2) |> 
+  bind_cols(training(dat_split))
+
+rf_score_train = train_prediction2 |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+rf_score_train
+```
+
+### Best Model
+
+The following code creates a table containing the RMSE and RSQ estimates for each of our four models.
+
+```{r Best&Final}
+# Create table of prediction metrics from training data
+linreg = res1 |> collect_metrics() |> as.data.frame()
+linreg = cbind(linreg[,1], round(linreg[,3],2))
+knn = res2 %>% collect_metrics() |> as.data.frame()
+knn = cbind(knn[,1], round(knn[,3],2))
+xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
+xgboost = cbind(xgboost[,1], xgboost[,3])
+ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
+ranfor = cbind(ranfor[,1], ranfor[,3])
+
+compare = c('LR','LR','KNN','KNN','XGB','XGB','RF','RF') |> cbind(rbind(linreg,knn,xgboost,ranfor))
+colnames(compare) = c('model','estimator','estimate') 
+compare = as.data.frame(compare) |> pivot_wider(names_from=estimator, values_from=estimate)
+compare
+
+# Visual of rmse for our 4 models
+compare |> ggplot(aes(x=model, y=rmse)) + 
+  geom_bar(stat="identity") + 
+  labs(title='RMSE of the Four Models') +
+  theme_minimal()
+
+# Fit RF model to testing data
+test_processed <- bake(preprocessing_recipe, new_data = testing(dat_split))
+
+# Get pred. metrics based on testing data
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
+             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
+
+xgb_score_test = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+xgb_score_test
+```
+
+As seen on the table and visual, LR has the highest RMSE and lowest r-squared estimate.
+KNN has the second highest RMSE with a moderate R-squared estimate.
+And XGB has the lowest RMSE of 0.55 and the highest R-squared estimate of 0.96.
+Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
+Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.23 and 0.73, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.23 $\mu$g/m$^3$, and that the features we used in our model are able to explain 73% of the variance in the data, which means this model does not fit/predict the data well.

### 2023-04-23 Draft.Rmd
top5 and answering Qs

@@
 For a given feature, the lower its impurity levels are, the more important that feature is.
-As a result, we got an ordered list of important variables and took the top 10 as input for the training set for our models.
-The top 10 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', 'aod', 'popdens_county', 'zcta', 'log_nei_2008_pm25_sum_10000', and 'log_nei_2008_pm10_sum_10000'.
-We will use these features to predict 'value' proceeding onwards.
+As a result, we got an ordered list of important variables and took the top 5 as input for the training set for our models.
+The top 5 important predictors were 'CMAQ', 'lat', 'county_area', 'lon', and 'aod'.
+We will use these features to predict 'value' proceeding onward.
 This website was used: [TowardDataScience](https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f).
@@
 # take top 10 important variables
-import10 = import[1:10,]
+import5 = import[1:5,]
 ```
@@
 Features are dropped as the AIC score decreases and feature dropping stops once the AIC score increases.
-'CMAQ', 'lat', 'lon', 'aod', 'zcta', and 'log_nei_2008_pm25_sum_10000' were determined to be the most important features, and these predictors were used in the recipe.
+'CMAQ'and 'aod' were determined to be the most important features, and these predictors were used in the recipe.
 Then, model was fitted.
-Using the summary function, we found the LR model had a RMSE of 2.22 performance.
-After 10-fold cross validation, the RMSE score was 2.21, indicating that this model's prediction performance is not good.
+Using the summary function, we found the LR model had a RMSE of 2.27 performance.
+After 10-fold cross validation, the RMSE score was over 2, indicating that this model's prediction performance is not good.
 
@@
 # Fit model and get summary
-fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train)
+fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod, data=train)
 step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
-# Drops county_area, popdens_county, fips, and log_nei_2008_pm25_sum_10000
+# Keeps cmaq and aod
 
@@
 rec1 <- train %>% 
-    recipe(value ~ CMAQ+lat+lon+aod+zcta+log_nei_2008_pm25_sum_10000)
+    recipe(value ~ CMAQ+aod)
 
@@
 RMSE is the square root of MSE and we were able to confirm its value in the cross-validation by comparing it to the square root of MSE attained from the first method.
-We found that after 10-fold cross validation, the RMSE was 1.78.
-This indicates that the model does not predict well since there is such a large amount of error.
+We found that after 10-fold cross validation, the RMSE was 1.84.
+This indicates that the model does not predict well since the amount of error is greater than 1.
 
@@
 # Create recipe
-rec2 = train_knn |> recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
+rec2 = train_knn |> recipe(value ~ CMAQ+lat+county_area+lon+aod)
 
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was 0.55, indicating the XG Boosting is a good model.
+Its RMSE score was 0.69, indicating the XG Boosting is an adequate model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 preprocessing_recipe <- 
-  recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = training(dat_split)) %>%
+  recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod, data = training(dat_split)) %>%
   # Convert categorical variables to factors
@@
   add_model(xgboost_model) %>% 
-  add_formula(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000)
+  add_formula(value ~ CMAQ+lat+county_area+lon+aod)
 
@@
   # Fit the model on all the training data
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data = train_processed) %>%
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod, data = train_processed) %>%
   # Predict value for the training data
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was .62, indicating the RF is a good predictive model.
+Its RMSE score was 8.81, indicating the RF is not a good predictive model.
 
@@
 # Preprocessing recipe
-rec4 <- recipe(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train) %>%
+rec4 <- recipe(value ~ CMAQ+lat+county_area+lon+aod, data=train) %>%
   step_log(all_outcomes()) |> 
   step_normalize(all_numeric_predictors()) |> 
-  step_dummy(all_nominal_predictors())
+  step_dummy(all_nominal_predictors()) |> prep()
 
@@
 
-folds4 = recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+folds4 = recipes::bake(rec4, new_data = training(dat_split)) %>%  
   rsample::vfold_cv(v = 5)
@@
 # Check Random Forest model performance
-train_processed2 <- bake(preprocessing_recipe,  new_data = training(dat_split))
+train_processed2 <- bake(rec4,  new_data = training(dat_split))
 
 train_prediction2 = rf_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed2) |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod, data=train_processed2) |> 
   predict(new_data=train_processed2) |> 
@@
 
-# Fit XG Boost model to testing data
+# Fit XGB model to testing data
 test_processed <- bake(preprocessing_recipe, new_data = testing(dat_split))
@@
 test_prediction = xgboost_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=train_processed) |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod, data=train_processed) |> 
   predict(new_data=test_processed) |> 
@@
 
-As seen on the table and visual, LR has the highest RMSE and lowest r-squared estimate.
+As seen on the table and visual, LR has the highest RMSE and lowest R-squared estimate.
 KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.55 and the highest R-squared estimate of 0.96.
+And XGB has the lowest RMSE of 0.69 and the highest R-squared estimate of 0.93.
 Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
 Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.23 and 0.73, respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.23 $\mu$g/m$^3$, and that the features we used in our model are able to explain 73% of the variance in the data, which means this model fits/predicts the data well.
-
-Your results should include 
-at least one visualization demonstrating the prediction performance of your models.
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.39 and 0.66, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 66% of the variance in the data, which means this model does not fit/predict the data well.
 
@@
 
+```{r Q1}
+# Arrange obs.s by greatest diff
+loc = test_prediction |> dplyr::select(.pred, value, CMAQ, lat, lon, county_area, aod, state) |> mutate(diff=round(abs(value-.pred),2)) |> arrange(desc(diff))
+
+# Find number of obs.s per the 3 states
+loc |> filter(state=='Oregon' | state=='Iowa' | state=='Virginia') |> group_by(state) |> summarise(mon=n())
+```
+
+Based on the test set performance, it seems that our model gives the closest prediction for both Iowa and Virginia  The model gives the furthest prediction for Oregon.
+We hypothesize that the model gives bad performance for Oregon because despite being clearly larger than both Iowa and Virginia, it has the same number of monitors as the latter states, making the data less representative of the variation in PM2.5 concentration for the state.
+
 **2.
@@
 Are there variables that are not included in this dataset that you think might improve the model performance if they were included in your model?**
+
+```{r Q2}
+# Visual for the most frequently close predictions by state
+loc |> filter(diff<0.5) |> ggplot(aes(y=state)) + geom_bar()
+
+# Visual for the most frequently furthest predictions by state
+loc |> filter(diff>=0.5) |> ggplot(aes(y=state)) + geom_bar()
+```
+
+Indiana, Ohio, Iowa, and Alabama most frequently compared to the other states.
+Our model also gives the furthers predictions for California, Colorado, Kentucky, Pennsylvania, and Texas most frequently.
+We noticed that some of these states where our model's prediction performance was bad were on the larger side.
+We hypothesize that the reason why our prediction performance is bad could be attributed to the possible increase of variance in ambient air pollution that comes with a larger state area or that the model has poor outlier handling.
 
@@
 # Fit RF model to testing data
-
+max(origin$value)
+min(origin$value)
 # Get pred. metrics based on testing data

### 2023-04-23 Draft.Rmd
popop

@@
 Using the summary function, we found the LR model had a RMSE of 2.27 performance.
-After 10-fold cross validation, the RMSE score was over 2, indicating that this model's prediction performance is not good.
+After 10-fold cross validation, the RMSE score was over 1, indicating that this model's prediction performance is not good.
 
@@
 Based on the test set performance, it seems that our model gives the closest prediction for both Iowa and Virginia  The model gives the furthest prediction for Oregon.
-We hypothesize that the model gives bad performance for Oregon because despite being clearly larger than both Iowa and Virginia, it has the same number of monitors as the latter states, making the data less representative of the variation in PM2.5 concentration for the state.
+We hypothesize that the model gives bad performance for Oregon because despite being clearly larger than both Iowa and Virginia, it has the same number of monitors as the latter states, making the data less representative of the variation in PM2.5 concentration for the state for the model to make a good prediction based on the features we chose.
 
@@
 
-Indiana, Ohio, Iowa, and Alabama most frequently compared to the other states.
-Our model also gives the furthers predictions for California, Colorado, Kentucky, Pennsylvania, and Texas most frequently.
-We noticed that some of these states where our model's prediction performance was bad were on the larger side.
-We hypothesize that the reason why our prediction performance is bad could be attributed to the possible increase of variance in ambient air pollution that comes with a larger state area or that the model has poor outlier handling.
+'CMAQ', 'county_area', and 'aod' might predict where our model performs well or not.
+We define a good prediction by having an absolute difference of less than 0.5 between 'value' and '.pred'.
+Indiana, Ohio, Iowa, and Alabama most frequently have good predictions.
+So the model does fairly well at predicting some of the Midwest.
+Our model gives the furthest predictions for California, Colorado, Kentucky, Pennsylvania, and Texas most frequently.
+So our model does poorly at predicting the West and the South.
+We think that including the variables 'popdens_county', 'zcta', and 'log_nei_2008_pm25_sum_10000' might improve the model performance since they were the following variables listed as most important in our feature selection process.
 

### 2023-04-23 Draft.Rmd
boost

@@
 
-# take top 10 important variables
+# take top 5 important variables
 import5 = import[1:5,]
@@
 # Check performance using cross-validation
-folds2 <- vfold_cv(train, v = 10)
+folds2 <- vfold_cv(train_knn, v = 10)
 # folds
@@
 So our model does poorly at predicting the West and the South.
-We think that including the variables 'popdens_county', 'zcta', and 'log_nei_2008_pm25_sum_10000' might improve the model performance since they were the following variables listed as most important in our feature selection process.
+We think that including historical data of ambient air pollution over the years would potentially improve the performance of the model because if we are able to track the air pollution over the years, we could get a better prediction for any given location.
 
@@
 
-- create visualization showing how close features CMAQ and AOD predict values of PM2.5 to actual/observed values
 - no cmaq and no aod models
 
-```{r Q3}
-# Fit RF model to testing data
-max(origin$value)
-min(origin$value)
-# Get pred. metrics based on testing data
+```{r Q3-1}
+set.seed(123)
+# XGB model w/only cmaq and aod
+# Preprocessing recipe
+preprocessing_recipe <- 
+  recipes::recipe(value ~ CMAQ + aod, data = training(dat_split)) %>%
+  # Convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # Combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # Remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds5 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
+head(xgboost_grid)
+
+xgboost_wf <- workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value ~ CMAQ+aod)
+
+# Hyperparameter tuning
+# Takes a long time to run, 5-8 min
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds5,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
+  control = tune::control_grid(verbose = TRUE))
+
+# Find hyper parameter values which performed best at minimizing RMSE
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
+xgboost_best_params
+
+# Final boost model
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
+
+# Eval. model performance on train data
+test_processed <- bake(preprocessing_recipe,  new_data = testing(dat_split))
+train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
+
 test_prediction = xgboost_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
-             log_nei_2008_pm25_sum_10000+fips+log_nei_2008_pm10_sum_10000, data=test_processed) |> 
+  parsnip::fit(formula = value ~ CMAQ+aod, data=train_processed) |> 
   predict(new_data=test_processed) |> 
@@
 
-xgb_score_test = test_prediction |> 
+xgb_q3p1 = test_prediction |> 
   yardstick::metrics(value, .pred) |> 
   mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-xgb_score_test
+xgb_q3p1
+```
 
+```{r Q3-2}
+set.seed(123)
+# XGB model w/o cmaq and aod
+# Preprocessing recipe
+preprocessing_recipe <- 
+  recipes::recipe(value ~ lat+county_area+lon, data = training(dat_split)) %>%
+  # Convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # Combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # Remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds6 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
+head(xgboost_grid)
+
+xgboost_wf <- workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value ~ lat+county_area+lon)
+
+# Hyperparameter tuning
+# Takes a long time to run, 5-8 min
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds6,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
+  control = tune::control_grid(verbose = TRUE))
+
+# Find hyper parameter values which performed best at minimizing RMSE
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
+xgboost_best_params
+
+# Final boost model
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
+
+# Eval. model performance on train data
+test_processed <- bake(preprocessing_recipe,  new_data = testing(dat_split))
+
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ lat+county_area+lon, data=train_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
+
+xgb_q3p2 = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+xgb_q3p2
 ```
@@
 **4. The dataset here did not include data from Alaska or Hawaii. Do you think your model will perform well or not in those two states? Explain your reasoning.**
-
+EDIT THIS
 Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the original dataset included states of varying sizes with different climates and pollution levels.
@@
 ## Discussion
-Putting it all together, what did you learn from your data and your model performance?
+**Putting it all together, what did you learn from your data and your model performance?
+Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.**
 
-• Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
+**Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?**
 
-• Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
+**Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?**
 
-• Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
+**Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).**
 
-• Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).
+## Acknowledgements
+**Aileen Li & Nyah Strickland:**
+- Intro
+
+- Wrangling
+
+- Results
+
+- Discussion
+
+- Formatting

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

@@
 We chose our predictors using the Random Forest algorithm.
-And for our four models, we chose Linear Regression, K-Nearest Neighbors, Xgboosting, and Random Forest.
+And for our four models, we chose Linear Regression, K-Nearest Neighbors, XG Boost, and Random Forest.
 Linear Regression models a linear relationship between the PM2.5 value in the atmosphere and the predictors.
 K-Nearest Neighbors returns predicted PM2.5 values based on their neighboring data points.
-Xgboosting predicts PM2.5 values by combining the estimates of a set of simpler, weaker models.
+XG Boost predicts PM2.5 values by combining the estimates of a set of simpler, weaker models.
 Random forest makes an averaged prediction from a collection of independent decision trees.
-We hypothesize that the RMSE performance of the Xgboosting model will be the best, with a value of around 0.5.
+We hypothesize that the RMSE performance of the XG Boost model will be the best, with a value of around 0.5.
 
@@
 'CMAQ'and 'aod' were determined to be the most important features, and these predictors were used in the recipe.
-Then, model was fitted.
+Then, the model was fitted.
 Using the summary function, we found the LR model had a RMSE of 2.27 performance.
@@
 We preprocess the training set to make the predictive modeling process more accurate and smoother by prepping (estimates the quantities for 'train_scaled') and baking (assigns prepped data to an object) the data.
-The aforementioned top 10 predictors were used in this preprocessing recipe.
+The aforementioned top 5 predictors were used in this preprocessing recipe.
 Moreover, the categorical variables were factored and features with no variance were removed before this data was baked.
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was 0.69, indicating the XG Boosting is an adequate model.
+Its RMSE score was 0.69, indicating that XG Boost is an adequate model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 The randomness of these samples contribute to the prediction accuracy of this model.
-Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve make the predictive modeling process and then create model specifications.
+Similar to the XG Boosting Regression model, we preprocess the training set with the same features to improve the predictive modeling process and then create model specifications.
 This processed data is assigned to 'folds4' and resampled on 5 subsets of the training set to tune the hyperparameters.
-We then perform grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
+We then performed grid specification to determine which hyperparameter values have high prediction accuracy (i.e.
 low prediction error).
@@
 
-As seen on the table and visual, LR has the highest RMSE and lowest R-squared estimate.
-KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.69 and the highest R-squared estimate of 0.93.
-Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
-Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.39 and 0.66, respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 66% of the variance in the data, which means this model does not fit/predict the data well.
+As seen on the table and visual, Random Forest has the highest RMSE and lowest R-squared estimate.
+LR has the second highest RMSE with a moderate R-squared estimate.
+And XG Boost has the lowest RMSE of 0.23 and the highest R-squared estimate of 0.99.
+The kNN model has the both the second lowest RMSE and second highest R-squared estimate.
+Since we are choosing the best model by the best RMSE, which is the lowest one, the XG Boost model is thus the best and final model based on our procedure.
+After fitting the XG Boost model to the testing data, we find that its RMSE and R-squared is 1.38 and 0.68, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.38 $\mu$g/m$^3$, and that the features we used in our model are able to explain 68% of the variance in the data, which means this model does not fit/predict the data well.
 

### 2023-04-23 Draft.Rmd
pioioi

--- 2023-04-23 Draft.Rmd
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was 0.69, indicating the XG Boosting is an adequate model.
+Its RMSE score was 0.23, indicating the XG Boosting is an adequate model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 # Preprocessing recipe
-preprocessing_recipe <- 
+rec3 <- 
   recipes::recipe(value ~ CMAQ+lat+county_area+lon+aod, data = training(dat_split)) %>%
@@
 
-folds3 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+folds3 <- recipes::bake(rec3, new_data = training(dat_split)) %>%  
   rsample::vfold_cv(v = 5)
@@
 
-head(xgboost_grid)
+# head(xgboost_grid)
 
@@
 # Eval. model performance on train data
-train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
+train_processed <- bake(rec3,  new_data = training(dat_split))
 
@@
 
-xgboost_score_train <- train_prediction %>%
+res3 <- train_prediction %>%
   yardstick::metrics(value, .pred) %>%
   mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
-xgboost_score_train
+res3
 ```
@@
 # Space-filling designs grid
-rf_grid <- grid_latin_hypercube(min_n(), mtry(range = c(4, 9)), trees(), size = 60)
+rf_grid <- grid_latin_hypercube(min_n(), mtry(range(4,9)), trees(), size = 60)
 
@@
 
-rf_score_train = train_prediction2 |> 
+res4 = train_prediction2 |> 
   yardstick::metrics(value, .pred) |> 
   mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-rf_score_train
+res4
 ```
@@
 ```{r Best&Final}
+set.seed(123)
 # Create table of prediction metrics from training data
@@
 knn = cbind(knn[,1], round(knn[,3],2))
-xgboost = xgboost_score_train |> filter(.metric!='mae') |> as.data.frame()
+xgboost = res3 |> filter(.metric!='mae') |> as.data.frame()
 xgboost = cbind(xgboost[,1], xgboost[,3])
-ranfor = rf_score_train |> filter(.metric!='mae') |> as.data.frame()
+ranfor = res4 |> filter(.metric!='mae') |> as.data.frame()
 ranfor = cbind(ranfor[,1], ranfor[,3])
@@
 
+# Final model
 # Fit XGB model to testing data
-test_processed <- bake(preprocessing_recipe, new_data = testing(dat_split))
+test_processed <- bake(rec3, new_data = testing(dat_split))
 
@@
 
-xgb_score_test = test_prediction |> 
+res_final = test_prediction |> 
   yardstick::metrics(value, .pred) |> 
   mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-xgb_score_test
+res_final
 ```
@@
 KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.69 and the highest R-squared estimate of 0.93.
+And XGB has the lowest RMSE of 0.23 and the highest R-squared estimate of 0.99.
 Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
 Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.39 and 0.66, respectively.
-Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.39 $\mu$g/m$^3$, and that the features we used in our model are able to explain 66% of the variance in the data, which means this model does not fit/predict the data well.
+After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.38 and 0.68, respectively.
+Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.38 $\mu$g/m$^3$, and that the features we used in our model are able to explain 68% of the variance in the data, which means this model does not fit/predict the data well.
 
@@
 
-- no cmaq and no aod models
-
 ```{r Q3-1}
@@
 # Preprocessing recipe
-preprocessing_recipe <- 
+rec5 <- 
   recipes::recipe(value ~ CMAQ + aod, data = training(dat_split)) %>%
@@
 
-folds5 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+folds5 <- recipes::bake(rec5, new_data = training(dat_split)) %>%  
   rsample::vfold_cv(v = 5)
@@
 # Eval. model performance on train data
-test_processed <- bake(preprocessing_recipe,  new_data = testing(dat_split))
-train_processed <- bake(preprocessing_recipe,  new_data = training(dat_split))
+test_processed <- bake(rec5,  new_data = testing(dat_split))
+train_processed <- bake(rec5,  new_data = training(dat_split))
 
@@
 
-xgb_q3p1 = test_prediction |> 
+res5 = test_prediction |> 
   yardstick::metrics(value, .pred) |> 
   mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-xgb_q3p1
+res5
 ```
@@
 set.seed(123)
+# XGB model w/only cmaq
+# Preprocessing recipe
+rec6 <- 
+  recipes::recipe(value ~ CMAQ, data = training(dat_split)) %>%
+  # Convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # Combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # Remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds6 <- recipes::bake(rec6, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
+head(xgboost_grid)
+
+xgboost_wf <- workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value ~ CMAQ)
+
+# Hyperparameter tuning
+# Takes a long time to run, 5-8 min
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds6,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
+  control = tune::control_grid(verbose = TRUE))
+
+# Find hyper parameter values which performed best at minimizing RMSE
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
+xgboost_best_params
+
+# Final boost model
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
+
+# Eval. model performance on train data
+test_processed <- bake(rec6,  new_data = testing(dat_split))
+train_processed <- bake(rec6,  new_data = training(dat_split))
+
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ CMAQ, data=train_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
+
+res6 = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+res6
+```
+
+```{r Q3-3}
+set.seed(123)
+# XGB model w/only aod
+# Preprocessing recipe
+rec7 <- 
+  recipes::recipe(value ~ aod, data = training(dat_split)) %>%
+  # Convert categorical variables to factors
+  recipes::step_string2factor(all_nominal()) %>%
+  # Combine low frequency factor levels
+  recipes::step_other(all_nominal(), threshold = 0.01) %>%
+  # Remove no variance predictors which provide no predictive information 
+  recipes::step_nzv(all_nominal()) %>%
+  prep()
+
+folds7 <- recipes::bake(rec7, new_data = training(dat_split)) %>%  
+  rsample::vfold_cv(v = 5)
+
+# XGBoost model specification
+xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
+  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
+  set_engine("xgboost", objective = "reg:squarederror")
+
+# Grid specification
+xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
+
+xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
+
+head(xgboost_grid)
+
+xgboost_wf <- workflows::workflow() %>%
+  add_model(xgboost_model) %>% 
+  add_formula(value ~ aod)
+
+# Hyperparameter tuning
+# Takes a long time to run, 5-8 min
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds7,
+  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
+  control = tune::control_grid(verbose = TRUE))
+
+# Find hyper parameter values which performed best at minimizing RMSE
+xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+# Isolate the best performing hyperparameter values.
+xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
+xgboost_best_params
+
+# Final boost model
+xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
+
+# Eval. model performance on train data
+test_processed <- bake(rec7,  new_data = testing(dat_split))
+train_processed <- bake(rec7,  new_data = training(dat_split))
+
+test_prediction = xgboost_model_final |> 
+  parsnip::fit(formula = value ~ aod, data=train_processed) |> 
+  predict(new_data=test_processed) |> 
+  bind_cols(testing(dat_split))
+
+res7 = test_prediction |> 
+  yardstick::metrics(value, .pred) |> 
+  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
+res7
+```
+
+```{r Q3-4}
+set.seed(123)
 # XGB model w/o cmaq and aod
 # Preprocessing recipe
-preprocessing_recipe <- 
+rec8 <- 
   recipes::recipe(value ~ lat+county_area+lon, data = training(dat_split)) %>%
@@
 
-folds6 <- recipes::bake(preprocessing_recipe, new_data = training(dat_split)) %>%  
+folds8 <- recipes::bake(rec8, new_data = training(dat_split)) %>%  
   rsample::vfold_cv(v = 5)
@@
 # Takes a long time to run, 5-8 min
-xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds6,
+xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds8,
   grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
@@
 # Eval. model performance on train data
-test_processed <- bake(preprocessing_recipe,  new_data = testing(dat_split))
+test_processed <- bake(rec8,  new_data = testing(dat_split))
 
@@
 
-xgb_q3p2 = test_prediction |> 
+res8 = test_prediction |> 
   yardstick::metrics(value, .pred) |> 
   mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-xgb_q3p2
+res8
 ```
+
+3.
+There is interest in developing more cost-effect approaches to monitoring air pollution on the ground.
+Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD.
+How well do CMAQ and AOD predict ground-level concentrations of PM2.5?
+How does the prediction performance of your model change when CMAQ or AOD are included (or not included) in the model?
+
+CMAQ and aod do not predict
 

### 2023-04-24 Draft.Rmd
uuu

@@
 We preprocess the training set to make the predictive modeling process more accurate and smoother by prepping (estimates the quantities for 'train_scaled') and baking (assigns prepped data to an object) the data.
-The aforementioned top 10 predictors were used in this preprocessing recipe.
+The aforementioned top 5 predictors were used in this 'rec3'.
 Moreover, the categorical variables were factored and features with no variance were removed before this data was baked.
@@
 Lastly, we fitted the model and evaluated its prediction performance.
-Its RMSE score was 0.23, indicating the XG Boosting is an adequate model.
+Its RMSE score was 0.23, indicating that XG Boost is an adequate model.
 This website was used: [RBloggers](https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/)
@@
 
-As seen on the table and visual, LR has the highest RMSE and lowest R-squared estimate.
-KNN has the second highest RMSE with a moderate R-squared estimate.
-And XGB has the lowest RMSE of 0.23 and the highest R-squared estimate of 0.99.
-Random Forest model has the both the second lowest RMSE and second highest R-squared estimate.
-Since we are choosing the best model by the best RMSE, which is the lowest one, the Xgboost model is thus the best and final model based on our procedure.
-After fitting the Xgboost model to the testing data, we find that its RMSE and R-squared is 1.38 and 0.68, respectively.
+As seen on the table and visual, Random Forest has the highest RMSE and lowest R-squared estimate.
+LR has the second highest RMSE with a moderate R-squared estimate.
+And XG Boost has the lowest RMSE of 0.23 and the highest R-squared estimate of 0.99.
+The kNN model has the both the second lowest RMSE and second highest R-squared estimate.
+Since we are choosing the best model by the best RMSE, which is the lowest one, the XG Boost model is thus the best and final model based on our procedure.
+After fitting the XG Boost model to the testing data, we find that its RMSE and R-squared is 1.38 and 0.68, respectively.
 Since we are trying to predict annual average ambient air pollution of a given monitor, then these statistics mean that the amount of error in our model's predictions is about 1.38 $\mu$g/m$^3$, and that the features we used in our model are able to explain 68% of the variance in the data, which means this model does not fit/predict the data well.
@@
 How does the prediction performance of your model change when CMAQ or AOD are included (or not included) in the model?**
+
+The model with only 'CMAQ' and 'aod' as features has an RMSE of 1.99.
+Since it is greater than 1, this means that 'CMAQ' and 'aod' are not good predictors for annual ambient air pollution in a given location.
+The RMSE of our model on the test data is 1.38.
+The RMSE of our model without 'CMAQ' and 'aod' is 1.73.
+This means that the model without 'CMAQ' and 'aod' has the better prediction performance since its RMSE is lower than our original model.
 
@@
 set.seed(123)
-# XGB model w/only cmaq
-# Preprocessing recipe
-rec6 <- 
-  recipes::recipe(value ~ CMAQ, data = training(dat_split)) %>%
-  # Convert categorical variables to factors
-  recipes::step_string2factor(all_nominal()) %>%
-  # Combine low frequency factor levels
-  recipes::step_other(all_nominal(), threshold = 0.01) %>%
-  # Remove no variance predictors which provide no predictive information 
-  recipes::step_nzv(all_nominal()) %>%
-  prep()
-
-folds6 <- recipes::bake(rec6, new_data = training(dat_split)) %>%  
-  rsample::vfold_cv(v = 5)
-
-# XGBoost model specification
-xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
-  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
-  set_engine("xgboost", objective = "reg:squarederror")
-
-# Grid specification
-xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
-
-xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
-
-head(xgboost_grid)
-
-xgboost_wf <- workflows::workflow() %>%
-  add_model(xgboost_model) %>% 
-  add_formula(value ~ CMAQ)
-
-# Hyperparameter tuning
-# Takes a long time to run, 5-8 min
-xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds6,
-  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
-  control = tune::control_grid(verbose = TRUE))
-
-# Find hyper parameter values which performed best at minimizing RMSE
-xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
-# Isolate the best performing hyperparameter values.
-xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
-xgboost_best_params
-
-# Final boost model
-xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
-
-# Eval. model performance on train data
-test_processed <- bake(rec6,  new_data = testing(dat_split))
-train_processed <- bake(rec6,  new_data = training(dat_split))
-
-test_prediction = xgboost_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ, data=train_processed) |> 
-  predict(new_data=test_processed) |> 
-  bind_cols(testing(dat_split))
-
-res6 = test_prediction |> 
-  yardstick::metrics(value, .pred) |> 
-  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-res6
-```
-
-```{r Q3-3}
-set.seed(123)
-# XGB model w/only aod
-# Preprocessing recipe
-rec7 <- 
-  recipes::recipe(value ~ aod, data = training(dat_split)) %>%
-  # Convert categorical variables to factors
-  recipes::step_string2factor(all_nominal()) %>%
-  # Combine low frequency factor levels
-  recipes::step_other(all_nominal(), threshold = 0.01) %>%
-  # Remove no variance predictors which provide no predictive information 
-  recipes::step_nzv(all_nominal()) %>%
-  prep()
-
-folds7 <- recipes::bake(rec7, new_data = training(dat_split)) %>%  
-  rsample::vfold_cv(v = 5)
-
-# XGBoost model specification
-xgboost_model <- parsnip::boost_tree(mode = "regression", trees = 1000, min_n = tune(),
-  tree_depth = tune(), learn_rate = tune(), loss_reduction = tune()) %>%
-  set_engine("xgboost", objective = "reg:squarederror")
-
-# Grid specification
-xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
-
-xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
-
-head(xgboost_grid)
-
-xgboost_wf <- workflows::workflow() %>%
-  add_model(xgboost_model) %>% 
-  add_formula(value ~ aod)
-
-# Hyperparameter tuning
-# Takes a long time to run, 5-8 min
-xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds7,
-  grid = xgboost_grid, metrics = yardstick::metric_set(rmse, rsq),
-  control = tune::control_grid(verbose = TRUE))
-
-# Find hyper parameter values which performed best at minimizing RMSE
-xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
-# Isolate the best performing hyperparameter values.
-xgboost_best_params <- xgboost_tuned %>% tune::select_best("rmse")
-xgboost_best_params
-
-# Final boost model
-xgboost_model_final <- xgboost_model %>% finalize_model(xgboost_best_params)
-
-# Eval. model performance on train data
-test_processed <- bake(rec7,  new_data = testing(dat_split))
-train_processed <- bake(rec7,  new_data = training(dat_split))
-
-test_prediction = xgboost_model_final |> 
-  parsnip::fit(formula = value ~ aod, data=train_processed) |> 
-  predict(new_data=test_processed) |> 
-  bind_cols(testing(dat_split))
-
-res7 = test_prediction |> 
-  yardstick::metrics(value, .pred) |> 
-  mutate(.estimate=format(round(.estimate, 2), big.mark=","))
-res7
-```
-
-```{r Q3-4}
-set.seed(123)
 # XGB model w/o cmaq and aod
@@
 # Eval. model performance on train data
+train_processed = bake(rec8, new_data=training(dat_split))
 test_processed <- bake(rec8, new_data = testing(dat_split))
@@
 
-3.
-There is interest in developing more cost-effect approaches to monitoring air pollution on the ground.
-Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD.
-How well do CMAQ and AOD predict ground-level concentrations of PM2.5?
-How does the prediction performance of your model change when CMAQ or AOD are included (or not included) in the model?
+**4. The dataset here did not include data from Alaska or Hawaii. Do you think your model will perform well or not in those two states? Explain your reasoning.**
 
-CMAQ and aod do not predict
-
-**4. The dataset here did not include data from Alaska or Hawaii. Do you think your model will perform well or not in those two states? Explain your reasoning.**
-EDIT THIS
-Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the original dataset included states of varying sizes with different climates and pollution levels.
-Moreover, its RMSE score is 0.62 and R-squared is 0.94, indicating that the prediction performance of this model is good in relation to the other models.
-Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also inter-relatedness of the features in this dataset aids the model in predicting ambient air pollution in differing environments.
+Given that the top 5 features were 'CMAQ', 'lat', 'county_area', 'lon', and 'aod'.
+We think that XG Boost model will not perform well since our model did not perform well on the test dataset.
+It seems like we overfit our model, so fitting it to data from Hawaii and Alaska, which we expect to be veyr different from our training dataset, will yield similar results to fitting our model to the test dataset.
 
@@
 
+The most challenging aspect of this project was figuring out the process to determine which predictors were the best to use for our models.
+We ran into many debugging issues and Googled a lot to resolve our uncertainties.
+We learned that finding the best predictors for a model can be a lengthy process and that running a new model (e.g.
+preprocessing steps for XG Boost) often may require lots of research into what is needed for the model to run before it can actually run.
+
 **Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?**
+
+The RMSE of our model was 1.38 on the testing dataset, which means it does not predict well.
+It did not perform as well as we originally expected, especially since we saw that the RMSE of our model was 0.23 on the training dataset.
+We believe the model did not perform well because we overfit the model to the training data.
+This means that the model gives inaccurate predictions and cannot perform well for all types of new data, which is why despite the low RMSE on the training data, the model has poor prediction performance on the testing data.
 

### 2023-04-24 Draft.Rmd
removed pca

@@
 date: "2023-04-18"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 editor_options:
@@
 train_knn = train[,2:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)
-
-# Calculate principal components on scaled training data
-pca_result <- train_scaled %>% dplyr::select(where(is.numeric)) %>%
-  prcomp()
-
-# Plot scree plot
-pca_result %>% fviz_eig()
-
-# Plot table to show explained variance % by PCs
-summary(pca_result)
-
-# Threshold of Explained Variance = 80%
-# Calculated the sum of PCs with highest explained variance until threshold was meant
-0.3253 + 0.09749 + 0.07984 + 0.06501 + 0.05196 + 0.04147 + 0.03445 +
-0.02926 + 0.02563 + 0.0220 + 0.02127 + 0.0188
-
-PC1 <- pca_result$rotation[,1]
-PC1_scores <- abs(PC1)
-PC1_scores_ordered <- sort(PC1_scores, decreasing = TRUE)
-names(PC1_scores_ordered)
-
-# Reduce dimension of dataset
-trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
-# Add the center (and re-scale) back to data 
-if(all(pca_result$scale != FALSE)){
-  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
-  } 
-if(all(pca_result$center != FALSE)){ 
-  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
-  } 
-dim(trunc); dim(train_scaled)
-
-# unhelpful plot -- delete
-# plot(pca_result$x[,1], pca_result$x[,2])
-
-# Show which features have the most influence
-as_tibble(pca_result$rotation, 
-          rownames = "variable") %>% 
-    ggplot(aes(variable, PC1)) +
-    geom_point() +
-    coord_flip()
-
-as_tibble(pca_result$rotation, 
-          rownames = "variable") %>% 
-    ggplot(aes(variable, PC2)) +
-    geom_point() +
-    coord_flip()
-
-# Plot clusters between PC1 and PC2 using a biplot
-fviz_pca_var(pca_result)
-
-# Reduce dimension of dataset
-trunc <- pca_result$x[,1:12] %*% t(pca_result$rotation[,1:12])
-# Add the center (and re-scale) back to data 
-if(all(pca_result$scale != FALSE)){
-  trunc <- scale(trunc, center = FALSE , scale=1/pca_result$scale) 
-  } 
-if(all(pca_result$center != FALSE)){ 
-  trunc <- scale(trunc, center = -1 * pca_result$center, scale=FALSE) 
-  } 
-dim(trunc); dim(train_scaled)
 
@@
 
+We learned that we overfit our Xgboost model to the data, which is why the prediction performance was poor for the testing dataset.
+This can be seen in our model having an RMSE value of 1.38 despite the RMSE of the model fit to the training data being 0.23.
+In general, we learned that understanding the disadvantages and advantages of each model is helpful toward understanding why a model fails or succeeds at the training and testing stages.
+For instance, we learned the Xgboost is helpful for unbalanced data and that Random Forest Regression performs well for datasets with a lot of noise.
+
 **Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?**
@@
 We learned that finding the best predictors for a model can be a lengthy process and that running a new model (e.g.
-preprocessing steps for XG Boost) often may require lots of research into what is needed for the model to run before it can actually run.
+preprocessing and hyperparameter tuning steps for XG Boost and Random Forest Regression) often may require lots of research into what is needed for the model to run before it can actually run.
 
@@
 **Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).**
-
 ## Acknowledgements

### 2023-04-24 Draft.Rmd
dfgh

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 editor_options:
@@
 ```{r setup, include=FALSE} 
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
 ```
@@
 
-```{r Library}
+```{r Library message=FALSE}
 library(tidyverse)
@@
 
-## Results
 ### Predictor/Feature Extraction
@@
 fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod, data=train)
-step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
+step <- stepAIC(fit_lm, direction="backward", trace=FALSE)
 # Keeps cmaq and aod

### 2023-04-24 Draft.tex
dfgh

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.},
  pdfauthor={Aileen Li, Nyah Strickland},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Predicting Ambient Air Pollution (PM2.5) Across the Contiguous
U.S.}
\author{Aileen Li, Nyah Strickland}
\date{2023-04-18}

\begin{document}
\maketitle

\hypertarget{predicting-ambient-air-pollution-pm2.5-across-the-contiguous-u.s.}{%
\subsection{Predicting Ambient Air Pollution (PM2.5) Across the
Contiguous
U.S.}\label{predicting-ambient-air-pollution-pm2.5-across-the-contiguous-u.s.}}

Air pollution has consequences for everyone, most especially for those
with pre-existing conditions. Air pollution is measured in tiny
particles or droplets in the air that are two and one-half microns or
less in width called PM2.5. So being able to predict the average PM2.5
concentrations (\(\mu\)g/m\(^3\)) will allow us to keep people most
vulnerable safe as we look for and implement changes to improve the air
quality in the region. We created four models to predict the annual
average of ambient air pollution in a location based on the variables in
the dataset. We chose our predictors using the Random Forest algorithm.
And for our four models, we chose Linear Regression, K-Nearest
Neighbors, XG Boost, and Random Forest. Linear Regression models a
linear relationship between the PM2.5 value in the atmosphere and the
predictors. K-Nearest Neighbors returns predicted PM2.5 values based on
their neighboring data points. XG Boost predicts PM2.5 values by
combining the estimates of a set of simpler, weaker models. Random
forest makes an averaged prediction from a collection of independent
decision trees. We hypothesize that the RMSE performance of the XG Boost
model will be the best, with a value of around 0.5.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'tidyverse' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'ggplot2' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'tibble' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'tidyr' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'readr' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'dplyr' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'forcats' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'lubridate' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## -- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
## v dplyr     1.1.1     v readr     2.1.4
## v forcats   1.0.0     v stringr   1.5.0
## v ggplot2   3.4.1     v tibble    3.2.1
## v lubridate 1.9.2     v tidyr     1.3.0
## v purrr     1.0.1     
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
## i Use the ]8;;http://conflicted.r-lib.org/conflicted package]8;; to force all conflicts to become errors
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidymodels)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'tidymodels' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## -- Attaching packages -------------------------------------- tidymodels 1.0.0 --
## v broom        1.0.4     v rsample      1.1.1
## v dials        1.2.0     v tune         1.1.1
## v infer        1.0.4     v workflows    1.1.3
## v modeldata    1.1.0     v workflowsets 1.0.1
## v parsnip      1.1.0     v yardstick    1.1.0
## v recipes      1.0.5
\end{verbatim}

\begin{verbatim}
## Warning: package 'broom' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'dials' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'infer' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'modeldata' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'parsnip' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'recipes' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'rsample' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'workflows' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'workflowsets' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Warning: package 'yardstick' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## -- Conflicts ----------------------------------------- tidymodels_conflicts() --
## x scales::discard() masks purrr::discard()
## x dplyr::filter()   masks stats::filter()
## x recipes::fixed()  masks stringr::fixed()
## x dplyr::lag()      masks stats::lag()
## x yardstick::spec() masks readr::spec()
## x recipes::step()   masks stats::step()
## * Dig deeper into tidy modeling with R at https://www.tmwr.org
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(broom)}
\FunctionTok{library}\NormalTok{(xgboost)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'xgboost' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'xgboost'
## 
## The following object is masked from 'package:dplyr':
## 
##     slice
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(caret)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'caret' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Loading required package: lattice
## 
## Attaching package: 'caret'
## 
## The following objects are masked from 'package:yardstick':
## 
##     precision, recall, sensitivity, specificity
## 
## The following object is masked from 'package:purrr':
## 
##     lift
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(plotROC)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'plotROC' was built under R version 4.2.3
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(randomForest)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'randomForest' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## randomForest 4.7-1.1
## Type rfNews() to see new features/changes/bug fixes.
## 
## Attaching package: 'randomForest'
## 
## The following object is masked from 'package:dplyr':
## 
##     combine
## 
## The following object is masked from 'package:ggplot2':
## 
##     margin
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(factoextra)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'factoextra' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Welcome! Want to learn more? See two factoextra-related books at https://goo.gl/ve3WBa
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(MASS)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'MASS' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'MASS'
## 
## The following object is masked from 'package:dplyr':
## 
##     select
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(ranger)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'ranger' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'ranger'
## 
## The following object is masked from 'package:randomForest':
## 
##     importance
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(doParallel)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'doParallel' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## Loading required package: foreach
## 
## Attaching package: 'foreach'
## 
## The following objects are masked from 'package:purrr':
## 
##     accumulate, when
## 
## Loading required package: iterators
## Loading required package: parallel
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{origin }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"https://github.com/rdpeng/stat322E\_public/raw/main/data/pm25\_data.csv.gz"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Rows: 876 Columns: 50
## -- Column specification --------------------------------------------------------
## Delimiter: ","
## chr  (3): state, county, city
## dbl (47): id, value, fips, lat, lon, CMAQ, zcta, zcta_area, zcta_pop, imp_a5...
## 
## i Use `spec()` to retrieve the full column specification for this data.
## i Specify the column types or set `show_col_types = FALSE` to quiet this message.
\end{verbatim}

\hypertarget{wrangling}{%
\subsection{Wrangling}\label{wrangling}}

We split 80\% of the origin dataset into training and 20\% into testing.
Then, we scaled the training datasets for PCA and kNN since both of
these require little variance among the variables in the dataset. We
omitted the `id' and `value' variables from the `trained\_scaled'
dataset for PCA because the `id' values for the monitors would not
provide any useful insight on PM2.5 concentration and `value' is not a
predictor. Next, we chose 12 principal components with the highest
explained variance since the sum of these components met our threshold
of 80\% explained variance. Then, we tried to see which variables
contributed the most to `value' and reduced the dimension of the
`trained\_scale' dataset based on these variables. For kNN, we created a
scaled training set `train\_knn' since extreme values would bias the
distance calculation used in kNN modeling. The other models either used
`train' dataset since the variables' values do not affect their
prediction performance or used a specially altered version of it.
Lastly, we did some exploratory analysis to see the linear relationship
between longitude and latitude with PM2.5 concentration.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Split origin dataset into 80/20}
\NormalTok{dat\_split }\OtherTok{\textless{}{-}} \FunctionTok{initial\_split}\NormalTok{(origin, }\AttributeTok{prop =}\NormalTok{.}\DecValTok{8}\NormalTok{)}
\NormalTok{dat\_split}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## <Training/Testing/Total>
## <700/176/876>
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Use 80\% of data for training }
\NormalTok{train }\OtherTok{\textless{}{-}} \FunctionTok{training}\NormalTok{(dat\_split)}
\NormalTok{test }\OtherTok{\textless{}{-}} \FunctionTok{testing}\NormalTok{(dat\_split)}

\CommentTok{\# Create standardize train data for kNN and PCA}
\CommentTok{\# Omit value and id variables since these should not be scaled}
\CommentTok{\# train\_scaled for PCA}
\NormalTok{train\_scaled }\OtherTok{=}\NormalTok{ train[,}\DecValTok{3}\SpecialCharTok{:}\DecValTok{50}\NormalTok{] }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(}\FunctionTok{where}\NormalTok{(is.numeric)) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(fips}\SpecialCharTok{:}\NormalTok{aod, scale)) }
\CommentTok{\#\%\textgreater{}\% cbind(state=train$state,county=train$county,city=train$city)}

\CommentTok{\# train\_knn for kNN model}
\NormalTok{train\_knn }\OtherTok{=}\NormalTok{ train[,}\DecValTok{2}\SpecialCharTok{:}\DecValTok{50}\NormalTok{] }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(}\FunctionTok{where}\NormalTok{(is.numeric)) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(fips}\SpecialCharTok{:}\NormalTok{aod, scale)) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{cbind}\NormalTok{(}\AttributeTok{state=}\NormalTok{train}\SpecialCharTok{$}\NormalTok{state,}\AttributeTok{county=}\NormalTok{train}\SpecialCharTok{$}\NormalTok{county,}\AttributeTok{city=}\NormalTok{train}\SpecialCharTok{$}\NormalTok{city)}

\CommentTok{\# Visualize linear relationship between predictors (lat, lon, state) and value}
\NormalTok{origin }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{lon, }\AttributeTok{y=}\NormalTok{value)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_smooth}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title=}\StringTok{"PM2.5 Concentration vs Longitude"}\NormalTok{, }\AttributeTok{x=}\StringTok{"Longitude (Degrees)"}\NormalTok{, }\AttributeTok{y=}\StringTok{"PM2.5 (mu g/m\^{}3)"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `geom_smooth()` using method = 'loess' and formula = 'y ~ x'
\end{verbatim}

\includegraphics{Draft_files/figure-latex/ExploratoryAnalysis-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{origin }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{lat, }\AttributeTok{y=}\NormalTok{value)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_smooth}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title=}\StringTok{"PM2.5 Concentration vs Latitude"}\NormalTok{, }\AttributeTok{x=}\StringTok{"Latitude (Degrees)"}\NormalTok{, }\AttributeTok{y=}\StringTok{"PM2.5 (mu g/m\^{}3)"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `geom_smooth()` using method = 'loess' and formula = 'y ~ x'
\end{verbatim}

\includegraphics{Draft_files/figure-latex/ExploratoryAnalysis-2.pdf}

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{predictorfeature-extraction}{%
\subsubsection{Predictor/Feature
Extraction}\label{predictorfeature-extraction}}

We used the random forest algorithm (RF) to determine which variables
would be the best predictors for our model since RF is good at using
variance to determine which features would be most influential for a
model's predictive performance. In other words, the more variability
there is in a dataset, the better RF performs at predicting which
variables contribute to the outcome by averaging the results of all
trees at the end and this averaging reduces the model's variance. Since
our dataset has a wide variety of predictors ranging from education
attainment levels to poverty levels in a given monitor region to
emission data, RF would be good at reducing the variance in our dataset.
For a given feature, the lower its impurity levels are, the more
important that feature is. As a result, we got an ordered list of
important variables and took the top 5 as input for the training set for
our models. The top 5 important predictors were `CMAQ', `lat',
`county\_area', `lon', and `aod'. We will use these features to predict
`value' proceeding onward. This website was used:
\href{https://towardsdatascience.com/feature-selection-using-random-forest-26d7b747597f}{TowardDataScience}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Use Random Forest for variable selection}
\NormalTok{rfmodel }\OtherTok{=} \FunctionTok{randomForest}\NormalTok{(value}\SpecialCharTok{\textasciitilde{}}\NormalTok{., }\AttributeTok{data=}\NormalTok{train[,}\DecValTok{2}\SpecialCharTok{:}\DecValTok{50}\NormalTok{])}
\NormalTok{import}\OtherTok{=}\FunctionTok{as.data.frame}\NormalTok{(randomForest}\SpecialCharTok{::}\FunctionTok{importance}\NormalTok{(rfmodel)) }\SpecialCharTok{|\textgreater{}} \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(IncNodePurity))}
\NormalTok{import}\OtherTok{=}\NormalTok{tibble}\SpecialCharTok{::}\FunctionTok{rownames\_to\_column}\NormalTok{(import, }\StringTok{\textquotesingle{}variables\textquotesingle{}}\NormalTok{)}

\CommentTok{\# take top 5 important variables}
\NormalTok{import5 }\OtherTok{=}\NormalTok{ import[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{,]}
\end{Highlighting}
\end{Shaded}

\hypertarget{models}{%
\subsubsection{Models}\label{models}}

\hypertarget{linear-regression}{%
\subsubsection{1. Linear Regression}\label{linear-regression}}

For linear regression (LR), the unscaled training set was used since
variance does not affect the prediction performance of this model. Step
Akaike Information Criteria (AIC) was used to simplify feature amount
without impacting the model's performance. Features are dropped as the
AIC score decreases and feature dropping stops once the AIC score
increases. `CMAQ'and 'aod' were determined to be the most important
features, and these predictors were used in the recipe. Then, the model
was fitted. Using the summary function, we found the LR model had a RMSE
of 2.27 performance. After 10-fold cross validation, the RMSE score was
over 1, indicating that this model's prediction performance is not good.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Fit model and get summary}
\NormalTok{fit\_lm }\OtherTok{=} \FunctionTok{lm}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data=}\NormalTok{train)}
\NormalTok{step }\OtherTok{\textless{}{-}} \FunctionTok{stepAIC}\NormalTok{(fit\_lm, }\AttributeTok{direction=}\StringTok{"backward"}\NormalTok{, }\AttributeTok{trace=}\ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Start:  AIC=1166.85
## value ~ CMAQ + lat + county_area + lon + aod
## 
##               Df Sum of Sq    RSS    AIC
## - lon          1      0.12 3644.2 1164.9
## - lat          1      2.50 3646.6 1165.3
## - county_area  1      2.81 3646.9 1165.4
## <none>                     3644.1 1166.8
## - aod          1    217.29 3861.4 1205.4
## - CMAQ         1    396.56 4040.7 1237.2
## 
## Step:  AIC=1164.87
## value ~ CMAQ + lat + county_area + aod
## 
##               Df Sum of Sq    RSS    AIC
## - lat          1      2.59 3646.8 1163.4
## - county_area  1      3.03 3647.3 1163.5
## <none>                     3644.2 1164.9
## - aod          1    218.47 3862.7 1203.6
## - CMAQ         1    426.81 4071.0 1240.4
## 
## Step:  AIC=1163.37
## value ~ CMAQ + county_area + aod
## 
##               Df Sum of Sq    RSS    AIC
## - county_area  1      2.35 3649.2 1161.8
## <none>                     3646.8 1163.4
## - aod          1    220.86 3867.7 1202.5
## - CMAQ         1    560.41 4207.2 1261.4
## 
## Step:  AIC=1161.82
## value ~ CMAQ + aod
## 
##        Df Sum of Sq    RSS    AIC
## <none>              3649.2 1161.8
## - aod   1    227.72 3876.9 1202.2
## - CMAQ  1    580.05 4229.2 1263.1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Keeps cmaq and aod}

\CommentTok{\# Create the recipe for all models}
\NormalTok{rec1 }\OtherTok{\textless{}{-}}\NormalTok{ train }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{aod) }

\CommentTok{\# Linear regr. model}
\NormalTok{model1 }\OtherTok{\textless{}{-}} \FunctionTok{linear\_reg}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"lm"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{set\_mode}\NormalTok{(}\StringTok{"regression"}\NormalTok{)}

\NormalTok{wf1 }\OtherTok{\textless{}{-}} \FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{add\_recipe}\NormalTok{(rec1) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{add\_model}\NormalTok{(model1)}
\CommentTok{\# wf1}

\NormalTok{res1 }\OtherTok{\textless{}{-}}\NormalTok{ wf1 }\SpecialCharTok{|\textgreater{}}\NormalTok{ parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{data =}\NormalTok{ train)}

\CommentTok{\# Check performance of linear regression model on the training data}
\NormalTok{res1 }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{extract\_fit\_engine}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summary}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## stats::lm(formula = ..y ~ ., data = data)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -6.4165 -1.1913 -0.0098  1.1486 12.8274 
## 
## Coefficients:
##             Estimate Std. Error t value Pr(>|t|)    
## (Intercept) 6.735167   0.284723  23.655  < 2e-16 ***
## CMAQ        0.327107   0.031077  10.526  < 2e-16 ***
## aod         0.030750   0.004663   6.595 8.41e-11 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.288 on 697 degrees of freedom
## Multiple R-squared:  0.2458, Adjusted R-squared:  0.2437 
## F-statistic: 113.6 on 2 and 697 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Check linear regression model performance using cross{-}validation}
\NormalTok{folds1 }\OtherTok{\textless{}{-}} \FunctionTok{vfold\_cv}\NormalTok{(train, }\AttributeTok{v =} \DecValTok{10}\NormalTok{)}
\CommentTok{\# folds1}
\NormalTok{res1 }\OtherTok{\textless{}{-}} \FunctionTok{fit\_resamples}\NormalTok{(wf1, }\AttributeTok{resamples =}\NormalTok{ folds1)}
\NormalTok{res1 }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{collect\_metrics}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 2 x 6
##   .metric .estimator  mean     n std_err .config             
##   <chr>   <chr>      <dbl> <int>   <dbl> <chr>               
## 1 rmse    standard   2.27     10  0.118  Preprocessor1_Model1
## 2 rsq     standard   0.249    10  0.0216 Preprocessor1_Model1
\end{verbatim}

\hypertarget{k-nearest-neighbors}{%
\subsubsection{2. K-Nearest Neighbors}\label{k-nearest-neighbors}}

The K-Nearest Neighbors (KNN) model finds the predicted `value' by
taking the average `value' of its k neighbors. We first found the ideal
number of k neighbors. This was determined by finding the square root of
the number of observations, which was rounded to be 26. We fit the model
on the training set data and checked its performance using two methods:
the first was fitting the model to extracting the MAE and MSE and the
second was 10-fold cross validation. RMSE is the square root of MSE and
we were able to confirm its value in the cross-validation by comparing
it to the square root of MSE attained from the first method. We found
that after 10-fold cross validation, the RMSE was 1.84. This indicates
that the model does not predict well since the amount of error is
greater than 1.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# kNN uses scaled data called train\_knn}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Find ideal k neighbors}
\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(train))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 26.45751
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create recipe}
\NormalTok{rec2 }\OtherTok{=}\NormalTok{ train\_knn }\SpecialCharTok{|\textgreater{}} \FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod)}

\CommentTok{\# Create kNN model}
\NormalTok{model2 }\OtherTok{\textless{}{-}} \FunctionTok{nearest\_neighbor}\NormalTok{(}\AttributeTok{neighbors =} \DecValTok{26}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"kknn"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{set\_mode}\NormalTok{(}\StringTok{"regression"}\NormalTok{)}

\CommentTok{\# Create workflow}
\NormalTok{  wf2 }\OtherTok{\textless{}{-}} \FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{add\_recipe}\NormalTok{(rec2) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{add\_model}\NormalTok{(model2)}

\CommentTok{\# Fit the model on the training dataset using the \textasciigrave{}fit()\textasciigrave{} function}
\NormalTok{res2 }\OtherTok{\textless{}{-}}\NormalTok{ parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(wf2, }\AttributeTok{data =}\NormalTok{ train\_knn)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: package 'kknn' was built under R version 4.2.3
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'kknn'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:caret':
## 
##     contr.dummy
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Check performance on the complete training data}
\NormalTok{res2 }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{extract\_fit\_engine}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summary}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## kknn::train.kknn(formula = ..y ~ ., data = data, ks = min_rows(26,     data, 5))
## 
## Type of response variable: continuous
## minimal mean absolute error: 1.257437
## Minimal mean squared error: 3.327239
## Best kernel: optimal
## Best k: 26
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Check performance using cross{-}validation}
\NormalTok{folds2 }\OtherTok{\textless{}{-}} \FunctionTok{vfold\_cv}\NormalTok{(train\_knn, }\AttributeTok{v =} \DecValTok{10}\NormalTok{)}
\CommentTok{\# folds}
\NormalTok{res2 }\OtherTok{\textless{}{-}} \FunctionTok{fit\_resamples}\NormalTok{(wf2, }\AttributeTok{resamples =}\NormalTok{ folds2) }\CommentTok{\# ERROR Assigned data \textasciigrave{}orig\_rows\textasciigrave{} must be compatible with existing data.}
\NormalTok{res2 }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{collect\_metrics}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 2 x 6
##   .metric .estimator  mean     n std_err .config             
##   <chr>   <chr>      <dbl> <int>   <dbl> <chr>               
## 1 rmse    standard   1.84     10  0.0842 Preprocessor1_Model1
## 2 rsq     standard   0.514    10  0.0381 Preprocessor1_Model1
\end{verbatim}

\hypertarget{extreme-gradient-boost-regression}{%
\subsubsection{3. Extreme Gradient Boost
Regression}\label{extreme-gradient-boost-regression}}

The Extreme Gradient Boosting (XGB) model performs by training weak
learners, models that have low prediction accuracy, sequentially to
become a single strong learner, a model that has strong prediction
accuracy. We preprocess the training set to make the predictive modeling
process more accurate and smoother by prepping (estimates the quantities
for `train\_scaled') and baking (assigns prepped data to an object) the
data. The aforementioned top 5 predictors were used in this `rec3'.
Moreover, the categorical variables were factored and features with no
variance were removed before this data was baked. Then, this processed
data is assigned to `folds3' and resampled on 5 subsets of the training
set. Using `fold3', we tune the hyperparameters to make the modeling
process more efficient and perform grid specification to determine which
hyperparameter values have high prediction accuracy (i.e.~low prediction
error). Next, we isolated the best hyperparameter values, so they can be
used for the final boosting model. Lastly, we fitted the model and
evaluated its prediction performance. Its RMSE score was 0.23,
indicating that XG Boost is an adequate model. This website was used:
\href{https://www.r-bloggers.com/2020/05/using-xgboost-with-tidymodels/}{RBloggers}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Preprocessing recipe}
\NormalTok{rec3 }\OtherTok{\textless{}{-}} 
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Convert categorical variables to factors}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_string2factor}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Combine low frequency factor levels}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_other}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{(), }\AttributeTok{threshold =} \FloatTok{0.01}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Remove no variance predictors which provide no predictive information }
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_nzv}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{prep}\NormalTok{()}

\NormalTok{folds3 }\OtherTok{\textless{}{-}}\NormalTok{ recipes}\SpecialCharTok{::}\FunctionTok{bake}\NormalTok{(rec3, }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}  
\NormalTok{  rsample}\SpecialCharTok{::}\FunctionTok{vfold\_cv}\NormalTok{(}\AttributeTok{v =} \DecValTok{5}\NormalTok{)}

\CommentTok{\# XGBoost model specification}
\NormalTok{xgboost\_model }\OtherTok{\textless{}{-}}\NormalTok{ parsnip}\SpecialCharTok{::}\FunctionTok{boost\_tree}\NormalTok{(}\AttributeTok{mode =} \StringTok{"regression"}\NormalTok{, }\AttributeTok{trees =} \DecValTok{1000}\NormalTok{, }\AttributeTok{min\_n =} \FunctionTok{tune}\NormalTok{(),}
  \AttributeTok{tree\_depth =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{learn\_rate =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{loss\_reduction =} \FunctionTok{tune}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"xgboost"}\NormalTok{, }\AttributeTok{objective =} \StringTok{"reg:squarederror"}\NormalTok{)}

\CommentTok{\# Grid specification}
\NormalTok{xgboost\_params }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{parameters}\NormalTok{(}\FunctionTok{min\_n}\NormalTok{(), }\FunctionTok{tree\_depth}\NormalTok{(), }\FunctionTok{learn\_rate}\NormalTok{(), }\FunctionTok{loss\_reduction}\NormalTok{())}

\NormalTok{xgboost\_grid }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{grid\_max\_entropy}\NormalTok{(xgboost\_params, }\AttributeTok{size =} \DecValTok{60}\NormalTok{)}

\CommentTok{\# head(xgboost\_grid)}

\NormalTok{xgboost\_wf }\OtherTok{\textless{}{-}}\NormalTok{ workflows}\SpecialCharTok{::}\FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_model}\NormalTok{(xgboost\_model) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{add\_formula}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod)}

\CommentTok{\# Hyperparameter tuning}
\CommentTok{\# Takes a long time to run, 5{-}8 min}
\NormalTok{xgboost\_tuned }\OtherTok{\textless{}{-}}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{tune\_grid}\NormalTok{(}\AttributeTok{object =}\NormalTok{ xgboost\_wf, }\AttributeTok{resamples =}\NormalTok{ folds3,}
  \AttributeTok{grid =}\NormalTok{ xgboost\_grid, }\AttributeTok{metrics =}\NormalTok{ yardstick}\SpecialCharTok{::}\FunctionTok{metric\_set}\NormalTok{(rmse, rsq),}
  \AttributeTok{control =}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{control\_grid}\NormalTok{(}\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## i Fold1: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 1/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 1/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 2/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 2/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 3/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 3/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 4/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 4/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 5/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 5/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 6/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 6/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 7/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 7/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 8/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 8/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 9/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 9/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 10/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 10/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 11/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 11/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 12/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 12/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 13/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 13/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 14/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 14/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 15/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 15/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 16/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 16/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 17/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 17/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 18/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 18/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 19/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 19/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 20/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 20/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 21/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 21/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 22/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 22/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 23/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 23/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 24/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 24/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 25/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 25/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 26/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 26/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 27/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 27/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 28/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 28/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 29/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 29/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 30/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 30/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 31/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 31/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 32/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 32/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 33/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 33/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 34/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 34/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 35/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 35/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 36/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 36/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 37/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 37/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 38/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 38/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 39/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 39/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 40/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 40/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 41/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 41/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 42/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 42/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 43/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 43/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 44/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 44/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 45/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 45/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 46/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 46/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 47/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 47/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 48/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 48/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 49/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 49/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 50/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 50/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 51/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 51/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 52/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 52/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 53/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 53/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 54/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 54/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 55/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 55/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 56/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 56/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 57/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 57/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 58/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 58/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 59/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 59/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## v Fold1: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 60/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold1: preprocessor 1/1, model 60/60 (predictions)
\end{verbatim}

\begin{verbatim}
## ! Fold1: internal:
##   There was 1 warning in `dplyr::summarise()`.
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 31`, `tree_depth = 3`, `learn_rate = 4.228428e-...
##     `loss_reduction = 1.230863e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 13`, `learn_rate = 8.942791e...
##     `loss_reduction = 2.073912`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 5`, `learn_rate = 1.685285e-...
##     `loss_reduction = 9.230063e-10`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 39`, `tree_depth = 14`, `learn_rate = 2.038467e...
##     `loss_reduction = 0.05878203`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 32`, `tree_depth = 6`, `learn_rate = 3.583763e-...
##     `loss_reduction = 0.04223655`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 14`, `tree_depth = 2`, `learn_rate = 1.786541e-...
##     `loss_reduction = 1.142136e-05`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 33`, `tree_depth = 10`, `learn_rate = 5.990585e...
##     `loss_reduction = 3.553207e-07`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 14`, `learn_rate = 9.438684e...
##     `loss_reduction = 25.86689`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 13`, `tree_depth = 8`, `learn_rate = 3.959735e-...
##     `loss_reduction = 5.666308e-06`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 5`, `tree_depth = 2`, `learn_rate = 6.002922e-09`,
##     `loss_reduction = 2.467321`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 1`, `learn_rate = 1.100178e-...
##     `loss_reduction = 0.0001398712`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 23`, `tree_depth = 10`, `learn_rate = 2.271355e...
##     `loss_reduction = 1.305291e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
\end{verbatim}

\begin{verbatim}
## v Fold1: internal
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 1/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 1/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 2/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 2/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 3/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 3/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 4/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 4/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 5/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 5/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 6/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 6/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 7/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 7/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 8/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 8/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 9/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 9/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 10/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 10/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 11/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 11/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 12/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 12/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 13/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 13/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 14/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 14/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 15/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 15/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 16/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 16/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 17/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 17/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 18/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 18/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 19/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 19/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 20/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 20/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 21/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 21/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 22/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 22/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 23/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 23/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 24/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 24/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 25/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 25/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 26/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 26/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 27/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 27/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 28/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 28/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 29/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 29/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 30/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 30/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 31/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 31/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 32/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 32/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 33/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 33/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 34/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 34/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 35/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 35/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 36/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 36/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 37/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 37/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 38/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 38/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 39/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 39/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 40/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 40/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 41/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 41/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 42/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 42/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 43/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 43/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 44/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 44/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 45/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 45/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 46/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 46/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 47/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 47/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 48/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 48/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 49/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 49/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 50/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 50/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 51/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 51/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 52/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 52/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 53/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 53/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 54/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 54/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 55/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 55/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 56/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 56/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 57/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 57/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 58/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 58/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 59/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 59/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## v Fold2: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 60/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold2: preprocessor 1/1, model 60/60 (predictions)
\end{verbatim}

\begin{verbatim}
## ! Fold2: internal:
##   There was 1 warning in `dplyr::summarise()`.
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 31`, `tree_depth = 3`, `learn_rate = 4.228428e-...
##     `loss_reduction = 1.230863e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 13`, `learn_rate = 8.942791e...
##     `loss_reduction = 2.073912`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 5`, `learn_rate = 1.685285e-...
##     `loss_reduction = 9.230063e-10`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 39`, `tree_depth = 14`, `learn_rate = 2.038467e...
##     `loss_reduction = 0.05878203`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 32`, `tree_depth = 6`, `learn_rate = 3.583763e-...
##     `loss_reduction = 0.04223655`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 14`, `tree_depth = 2`, `learn_rate = 1.786541e-...
##     `loss_reduction = 1.142136e-05`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 33`, `tree_depth = 10`, `learn_rate = 5.990585e...
##     `loss_reduction = 3.553207e-07`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 14`, `learn_rate = 9.438684e...
##     `loss_reduction = 25.86689`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 13`, `tree_depth = 8`, `learn_rate = 3.959735e-...
##     `loss_reduction = 5.666308e-06`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 5`, `tree_depth = 2`, `learn_rate = 6.002922e-09`,
##     `loss_reduction = 2.467321`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 1`, `learn_rate = 1.100178e-...
##     `loss_reduction = 0.0001398712`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 23`, `tree_depth = 10`, `learn_rate = 2.271355e...
##     `loss_reduction = 1.305291e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
\end{verbatim}

\begin{verbatim}
## v Fold2: internal
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 1/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 1/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 2/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 2/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 3/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 3/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 4/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 4/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 5/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 5/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 6/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 6/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 7/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 7/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 8/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 8/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 9/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 9/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 10/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 10/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 11/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 11/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 12/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 12/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 13/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 13/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 14/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 14/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 15/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 15/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 16/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 16/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 17/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 17/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 18/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 18/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 19/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 19/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 20/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 20/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 21/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 21/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 22/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 22/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 23/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 23/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 24/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 24/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 25/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 25/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 26/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 26/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 27/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 27/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 28/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 28/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 29/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 29/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 30/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 30/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 31/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 31/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 32/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 32/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 33/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 33/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 34/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 34/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 35/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 35/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 36/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 36/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 37/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 37/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 38/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 38/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 39/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 39/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 40/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 40/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 41/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 41/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 42/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 42/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 43/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 43/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 44/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 44/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 45/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 45/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 46/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 46/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 47/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 47/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 48/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 48/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 49/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 49/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 50/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 50/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 51/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 51/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 52/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 52/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 53/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 53/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 54/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 54/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 55/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 55/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 56/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 56/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 57/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 57/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 58/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 58/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 59/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 59/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## v Fold3: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 60/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold3: preprocessor 1/1, model 60/60 (predictions)
\end{verbatim}

\begin{verbatim}
## ! Fold3: internal:
##   There was 1 warning in `dplyr::summarise()`.
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 31`, `tree_depth = 3`, `learn_rate = 4.228428e-...
##     `loss_reduction = 1.230863e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 13`, `learn_rate = 8.942791e...
##     `loss_reduction = 2.073912`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 5`, `learn_rate = 1.685285e-...
##     `loss_reduction = 9.230063e-10`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 39`, `tree_depth = 14`, `learn_rate = 2.038467e...
##     `loss_reduction = 0.05878203`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 32`, `tree_depth = 6`, `learn_rate = 3.583763e-...
##     `loss_reduction = 0.04223655`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 14`, `tree_depth = 2`, `learn_rate = 1.786541e-...
##     `loss_reduction = 1.142136e-05`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 33`, `tree_depth = 10`, `learn_rate = 5.990585e...
##     `loss_reduction = 3.553207e-07`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 14`, `learn_rate = 9.438684e...
##     `loss_reduction = 25.86689`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 13`, `tree_depth = 8`, `learn_rate = 3.959735e-...
##     `loss_reduction = 5.666308e-06`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 5`, `tree_depth = 2`, `learn_rate = 6.002922e-09`,
##     `loss_reduction = 2.467321`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 1`, `learn_rate = 1.100178e-...
##     `loss_reduction = 0.0001398712`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 23`, `tree_depth = 10`, `learn_rate = 2.271355e...
##     `loss_reduction = 1.305291e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
\end{verbatim}

\begin{verbatim}
## v Fold3: internal
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 1/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 1/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 2/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 2/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 3/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 3/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 4/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 4/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 5/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 5/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 6/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 6/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 7/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 7/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 8/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 8/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 9/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 9/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 10/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 10/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 11/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 11/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 12/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 12/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 13/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 13/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 14/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 14/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 15/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 15/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 16/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 16/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 17/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 17/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 18/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 18/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 19/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 19/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 20/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 20/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 21/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 21/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 22/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 22/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 23/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 23/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 24/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 24/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 25/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 25/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 26/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 26/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 27/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 27/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 28/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 28/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 29/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 29/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 30/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 30/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 31/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 31/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 32/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 32/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 33/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 33/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 34/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 34/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 35/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 35/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 36/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 36/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 37/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 37/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 38/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 38/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 39/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 39/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 40/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 40/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 41/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 41/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 42/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 42/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 43/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 43/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 44/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 44/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 45/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 45/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 46/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 46/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 47/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 47/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 48/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 48/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 49/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 49/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 50/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 50/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 51/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 51/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 52/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 52/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 53/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 53/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 54/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 54/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 55/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 55/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 56/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 56/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 57/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 57/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 58/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 58/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 59/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 59/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## v Fold4: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 60/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold4: preprocessor 1/1, model 60/60 (predictions)
\end{verbatim}

\begin{verbatim}
## ! Fold4: internal:
##   There was 1 warning in `dplyr::summarise()`.
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 31`, `tree_depth = 3`, `learn_rate = 4.228428e-...
##     `loss_reduction = 1.230863e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 13`, `learn_rate = 8.942791e...
##     `loss_reduction = 2.073912`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 5`, `learn_rate = 1.685285e-...
##     `loss_reduction = 9.230063e-10`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 39`, `tree_depth = 14`, `learn_rate = 2.038467e...
##     `loss_reduction = 0.05878203`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 32`, `tree_depth = 6`, `learn_rate = 3.583763e-...
##     `loss_reduction = 0.04223655`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 14`, `tree_depth = 2`, `learn_rate = 1.786541e-...
##     `loss_reduction = 1.142136e-05`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 33`, `tree_depth = 10`, `learn_rate = 5.990585e...
##     `loss_reduction = 3.553207e-07`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 14`, `learn_rate = 9.438684e...
##     `loss_reduction = 25.86689`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 13`, `tree_depth = 8`, `learn_rate = 3.959735e-...
##     `loss_reduction = 5.666308e-06`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 5`, `tree_depth = 2`, `learn_rate = 6.002922e-09`,
##     `loss_reduction = 2.467321`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 1`, `learn_rate = 1.100178e-...
##     `loss_reduction = 0.0001398712`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 23`, `tree_depth = 10`, `learn_rate = 2.271355e...
##     `loss_reduction = 1.305291e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
\end{verbatim}

\begin{verbatim}
## v Fold4: internal
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 1/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 1/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 1/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 2/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 2/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 2/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 3/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 3/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 3/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 4/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 4/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 4/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 5/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 5/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 5/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 6/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 6/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 6/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 7/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 7/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 7/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 8/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 8/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 8/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 9/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 9/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 9/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 10/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 10/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 10/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 11/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 11/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 11/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 12/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 12/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 12/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 13/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 13/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 13/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 14/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 14/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 14/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 15/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 15/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 15/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 16/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 16/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 16/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 17/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 17/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 17/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 18/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 18/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 18/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 19/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 19/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 19/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 20/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 20/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 20/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 21/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 21/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 21/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 22/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 22/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 22/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 23/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 23/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 23/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 24/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 24/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 24/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 25/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 25/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 25/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 26/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 26/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 26/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 27/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 27/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 27/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 28/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 28/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 28/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 29/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 29/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 29/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 30/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 30/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 30/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 31/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 31/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 31/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 32/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 32/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 32/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 33/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 33/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 33/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 34/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 34/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 34/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 35/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 35/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 35/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 36/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 36/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 36/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 37/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 37/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 37/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 38/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 38/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 38/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 39/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 39/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 39/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 40/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 40/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 40/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 41/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 41/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 41/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 42/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 42/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 42/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 43/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 43/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 43/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 44/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 44/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 44/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 45/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 45/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 45/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 46/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 46/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 46/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 47/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 47/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 47/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 48/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 48/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 48/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 49/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 49/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 49/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 50/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 50/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 50/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 51/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 51/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 51/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 52/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 52/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 52/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 53/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 53/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 53/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 54/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 54/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 54/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 55/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 55/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 55/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 56/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 56/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 56/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 57/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 57/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 57/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 58/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 58/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 58/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 59/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 59/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 59/60 (predictions)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## v Fold5: preprocessor 1/1, model 60/60
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 60/60 (extracts)
\end{verbatim}

\begin{verbatim}
## i Fold5: preprocessor 1/1, model 60/60 (predictions)
\end{verbatim}

\begin{verbatim}
## ! Fold5: internal:
##   There was 1 warning in `dplyr::summarise()`.
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 31`, `tree_depth = 3`, `learn_rate = 4.228428e-...
##     `loss_reduction = 1.230863e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 13`, `learn_rate = 8.942791e...
##     `loss_reduction = 2.073912`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 16`, `tree_depth = 5`, `learn_rate = 1.685285e-...
##     `loss_reduction = 9.230063e-10`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 39`, `tree_depth = 14`, `learn_rate = 2.038467e...
##     `loss_reduction = 0.05878203`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 32`, `tree_depth = 6`, `learn_rate = 3.583763e-...
##     `loss_reduction = 0.04223655`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 14`, `tree_depth = 2`, `learn_rate = 1.786541e-...
##     `loss_reduction = 1.142136e-05`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 33`, `tree_depth = 10`, `learn_rate = 5.990585e...
##     `loss_reduction = 3.553207e-07`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 14`, `learn_rate = 9.438684e...
##     `loss_reduction = 25.86689`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 13`, `tree_depth = 8`, `learn_rate = 3.959735e-...
##     `loss_reduction = 5.666308e-06`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 5`, `tree_depth = 2`, `learn_rate = 6.002922e-09`,
##     `loss_reduction = 2.467321`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 30`, `tree_depth = 1`, `learn_rate = 1.100178e-...
##     `loss_reduction = 0.0001398712`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
##   i In argument: `.estimate = metric_fn(truth = value, estimate = .pred,...
##     na_rm)`.
##   i In group 1: `min_n = 23`, `tree_depth = 10`, `learn_rate = 2.271355e...
##     `loss_reduction = 1.305291e-09`.
##   Caused by warning:
##   ! A correlation computation is required, but `estimate` is constant an...
\end{verbatim}

\begin{verbatim}
## v Fold5: internal
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Find hyper parameter values which performed best at minimizing RMSE}
\NormalTok{xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{show\_best}\NormalTok{(}\AttributeTok{metric =} \StringTok{"rmse"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0566}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1415}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0755}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0849}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0283}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0943}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2075}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedleft
min\_n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
tree\_depth
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
learn\_rate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
loss\_reduction
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.estimator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
mean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
std\_err
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.config
\end{minipage} \\
\midrule()
\endhead
7 & 9 & 0.0301111 & 0.0000000 & rmse & standard & 1.662004 & 5 &
0.0872732 & Preprocessor1\_Model44 \\
22 & 8 & 0.0200526 & 0.1687102 & rmse & standard & 1.667683 & 5 &
0.0939255 & Preprocessor1\_Model57 \\
16 & 15 & 0.0228946 & 1.4483751 & rmse & standard & 1.676670 & 5 &
0.0965591 & Preprocessor1\_Model42 \\
2 & 11 & 0.0832471 & 0.5027694 & rmse & standard & 1.679748 & 5 &
0.0911398 & Preprocessor1\_Model51 \\
23 & 9 & 0.0059687 & 0.0000000 & rmse & standard & 1.705072 & 5 &
0.0861119 & Preprocessor1\_Model36 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Isolate the best performing hyperparameter values.}
\NormalTok{xgboost\_best\_params }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{select\_best}\NormalTok{(}\StringTok{"rmse"}\NormalTok{)}
\NormalTok{xgboost\_best\_params}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 1 x 5
##   min_n tree_depth learn_rate loss_reduction .config              
##   <int>      <int>      <dbl>          <dbl> <chr>                
## 1     7          9     0.0301       8.93e-10 Preprocessor1_Model44
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Final boost model}
\NormalTok{xgboost\_model\_final }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_model }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{finalize\_model}\NormalTok{(xgboost\_best\_params)}

\CommentTok{\# Eval. model performance on train data}
\NormalTok{train\_processed }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec3,  }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split))}

\NormalTok{train\_prediction }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_model\_final }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Fit the model on all the training data}
\NormalTok{  parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data =}\NormalTok{ train\_processed) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Predict value for the training data}
  \FunctionTok{predict}\NormalTok{(}\AttributeTok{new\_data =}\NormalTok{ train\_processed) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{training}\NormalTok{(dat\_split))}

\NormalTok{res3 }\OtherTok{\textless{}{-}}\NormalTok{ train\_prediction }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{  yardstick}\SpecialCharTok{::}\FunctionTok{metrics}\NormalTok{(value, .pred) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{.estimate =} \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(.estimate, }\DecValTok{2}\NormalTok{), }\AttributeTok{big.mark =} \StringTok{","}\NormalTok{))}
\NormalTok{res3}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 3
##   .metric .estimator .estimate
##   <chr>   <chr>      <chr>    
## 1 rmse    standard   0.23     
## 2 rsq     standard   0.99     
## 3 mae     standard   0.15
\end{verbatim}

\hypertarget{random-forest-regression}{%
\subsubsection{4. Random Forest
Regression}\label{random-forest-regression}}

The Random Forest (RF) Regression model performs by training multiple
different samples simultaneously and averages the outcome at the end for
the final prediction. The randomness of these samples contribute to the
prediction accuracy of this model. Similar to the XG Boosting Regression
model, we preprocess the training set with the same features to improve
the predictive modeling process and then create model specifications.
This processed data is assigned to `folds4' and resampled on 5 subsets
of the training set to tune the hyperparameters. We then performed grid
specification to determine which hyperparameter values have high
prediction accuracy (i.e.~low prediction error). Next, we isolated the
best hyperparameter values, so they can be used for the final boosting
model. Lastly, we fitted the model and evaluated its prediction
performance. Its RMSE score was 8.81, indicating the RF is not a good
predictive model.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Preprocessing recipe}
\NormalTok{rec4 }\OtherTok{\textless{}{-}} \FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data=}\NormalTok{train) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{step\_log}\NormalTok{(}\FunctionTok{all\_outcomes}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{step\_normalize}\NormalTok{(}\FunctionTok{all\_numeric\_predictors}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{step\_dummy}\NormalTok{(}\FunctionTok{all\_nominal\_predictors}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} \FunctionTok{prep}\NormalTok{()}

\CommentTok{\#  Create model specification and wf}
\NormalTok{rf\_spec }\OtherTok{\textless{}{-}} \FunctionTok{rand\_forest}\NormalTok{(}\AttributeTok{mtry =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{trees =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{min\_n =} \FunctionTok{tune}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"ranger"}\NormalTok{, }\AttributeTok{num.threads=}\DecValTok{7}\NormalTok{, }\AttributeTok{importance=}\StringTok{"impurity"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{set\_mode}\NormalTok{(}\StringTok{"regression"}\NormalTok{)}

\NormalTok{wf4 }\OtherTok{\textless{}{-}} \FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_recipe}\NormalTok{(rec4) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_model}\NormalTok{(rf\_spec)}

\NormalTok{folds4 }\OtherTok{=}\NormalTok{ recipes}\SpecialCharTok{::}\FunctionTok{bake}\NormalTok{(rec4, }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}  
\NormalTok{  rsample}\SpecialCharTok{::}\FunctionTok{vfold\_cv}\NormalTok{(}\AttributeTok{v =} \DecValTok{5}\NormalTok{)}

\CommentTok{\# Space{-}filling designs grid}
\NormalTok{rf\_grid }\OtherTok{\textless{}{-}} \FunctionTok{grid\_latin\_hypercube}\NormalTok{(}\FunctionTok{min\_n}\NormalTok{(), }\FunctionTok{mtry}\NormalTok{(}\FunctionTok{range}\NormalTok{(}\DecValTok{4}\NormalTok{,}\DecValTok{9}\NormalTok{)), }\FunctionTok{trees}\NormalTok{(), }\AttributeTok{size =} \DecValTok{60}\NormalTok{)}

\CommentTok{\# Tuning hyperparameters}
\NormalTok{all\_cores }\OtherTok{=}\NormalTok{ parallel}\SpecialCharTok{::}\FunctionTok{detectCores}\NormalTok{(}\AttributeTok{logical=}\ConstantTok{FALSE}\NormalTok{)}
\NormalTok{cl }\OtherTok{=} \FunctionTok{makePSOCKcluster}\NormalTok{(all\_cores)}
\NormalTok{doParallel}\SpecialCharTok{::}\FunctionTok{registerDoParallel}\NormalTok{(cl)}

\CommentTok{\# Takes long time to load 2 min}
\NormalTok{tune\_res }\OtherTok{\textless{}{-}}\NormalTok{ wf4 }\SpecialCharTok{|\textgreater{}} \FunctionTok{tune\_grid}\NormalTok{(}\AttributeTok{resamples =}\NormalTok{ folds4, }\AttributeTok{grid =}\NormalTok{ rf\_grid, }\AttributeTok{metrics=}\FunctionTok{metric\_set}\NormalTok{(rmse,rsq), }\AttributeTok{control =}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{control\_grid}\NormalTok{(}\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{))}
\CommentTok{\# tune\_res}

\CommentTok{\# Find hyper parameter values which performed best at minimizing RMSE}
\NormalTok{tune\_res }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{show\_best}\NormalTok{(}\AttributeTok{metric =} \StringTok{"rmse"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0617}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0988}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1358}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0370}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.2716}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedleft
mtry
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
trees
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
min\_n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.estimator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
mean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
std\_err
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.config
\end{minipage} \\
\midrule()
\endhead
4 & 793 & 3 & rmse & standard & 0.0807276 & 5 & 0.0043356 &
Preprocessor1\_Model28 \\
4 & 690 & 15 & rmse & standard & 0.0817487 & 5 & 0.0041090 &
Preprocessor1\_Model11 \\
5 & 1542 & 3 & rmse & standard & 0.0817565 & 5 & 0.0038243 &
Preprocessor1\_Model53 \\
8 & 1342 & 3 & rmse & standard & 0.0818413 & 5 & 0.0039331 &
Preprocessor1\_Model19 \\
7 & 422 & 5 & rmse & standard & 0.0819239 & 5 & 0.0038807 &
Preprocessor1\_Model05 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Isolate the best performing hyperparameter values.}
\NormalTok{rf\_best\_params }\OtherTok{\textless{}{-}}\NormalTok{ tune\_res }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{select\_best}\NormalTok{(}\StringTok{"rmse"}\NormalTok{)}
\NormalTok{rf\_best\_params}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 1 x 4
##    mtry trees min_n .config              
##   <int> <int> <int> <chr>                
## 1     4   793     3 Preprocessor1_Model28
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Final Random Forest model}
\NormalTok{rf\_model\_final }\OtherTok{\textless{}{-}}\NormalTok{ rf\_spec }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{finalize\_model}\NormalTok{(rf\_best\_params)}

\CommentTok{\# Check Random Forest model performance}
\NormalTok{train\_processed2 }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec4,  }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split))}

\NormalTok{train\_prediction2 }\OtherTok{=}\NormalTok{ rf\_model\_final }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data=}\NormalTok{train\_processed2) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{predict}\NormalTok{(}\AttributeTok{new\_data=}\NormalTok{train\_processed2) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{training}\NormalTok{(dat\_split))}

\NormalTok{res4 }\OtherTok{=}\NormalTok{ train\_prediction2 }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  yardstick}\SpecialCharTok{::}\FunctionTok{metrics}\NormalTok{(value, .pred) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{.estimate=}\FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(.estimate, }\DecValTok{2}\NormalTok{), }\AttributeTok{big.mark=}\StringTok{","}\NormalTok{))}
\NormalTok{res4}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 3
##   .metric .estimator .estimate
##   <chr>   <chr>      <chr>    
## 1 rmse    standard   8.81     
## 2 rsq     standard   0.91     
## 3 mae     standard   8.47
\end{verbatim}

\hypertarget{best-model}{%
\subsubsection{Best Model}\label{best-model}}

The following code creates a table containing the RMSE and RSQ estimates
for each of our four models.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# Create table of prediction metrics from training data}
\NormalTok{linreg }\OtherTok{=}\NormalTok{ res1 }\SpecialCharTok{|\textgreater{}} \FunctionTok{collect\_metrics}\NormalTok{() }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
\NormalTok{linreg }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(linreg[,}\DecValTok{1}\NormalTok{], }\FunctionTok{round}\NormalTok{(linreg[,}\DecValTok{3}\NormalTok{],}\DecValTok{2}\NormalTok{))}
\NormalTok{knn }\OtherTok{=}\NormalTok{ res2 }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{collect\_metrics}\NormalTok{() }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
\NormalTok{knn }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(knn[,}\DecValTok{1}\NormalTok{], }\FunctionTok{round}\NormalTok{(knn[,}\DecValTok{3}\NormalTok{],}\DecValTok{2}\NormalTok{))}
\NormalTok{xgboost }\OtherTok{=}\NormalTok{ res3 }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(.metric}\SpecialCharTok{!=}\StringTok{\textquotesingle{}mae\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
\NormalTok{xgboost }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(xgboost[,}\DecValTok{1}\NormalTok{], xgboost[,}\DecValTok{3}\NormalTok{])}
\NormalTok{ranfor }\OtherTok{=}\NormalTok{ res4 }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(.metric}\SpecialCharTok{!=}\StringTok{\textquotesingle{}mae\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
\NormalTok{ranfor }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(ranfor[,}\DecValTok{1}\NormalTok{], ranfor[,}\DecValTok{3}\NormalTok{])}

\NormalTok{compare }\OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}LR\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}LR\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}KNN\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}KNN\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}XGB\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}XGB\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}RF\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}RF\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{rbind}\NormalTok{(linreg,knn,xgboost,ranfor))}
\FunctionTok{colnames}\NormalTok{(compare) }\OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}model\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}estimator\textquotesingle{}}\NormalTok{,}\StringTok{\textquotesingle{}estimate\textquotesingle{}}\NormalTok{) }
\NormalTok{compare }\OtherTok{=} \FunctionTok{as.data.frame}\NormalTok{(compare) }\SpecialCharTok{|\textgreater{}} \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from=}\NormalTok{estimator, }\AttributeTok{values\_from=}\NormalTok{estimate)}
\NormalTok{compare}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 4 x 3
##   model rmse  rsq  
##   <chr> <chr> <chr>
## 1 LR    2.27  0.25 
## 2 KNN   1.84  0.51 
## 3 XGB   0.23  0.99 
## 4 RF    8.81  0.91
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Visual of rmse for our 4 models}
\NormalTok{compare }\SpecialCharTok{|\textgreater{}} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{model, }\AttributeTok{y=}\NormalTok{rmse)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat=}\StringTok{"identity"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title=}\StringTok{\textquotesingle{}RMSE of the Four Models\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Draft_files/figure-latex/Best\&Final-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Final model}
\CommentTok{\# Fit XGB model to testing data}
\NormalTok{test\_processed }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec3, }\AttributeTok{new\_data =} \FunctionTok{testing}\NormalTok{(dat\_split))}

\CommentTok{\# Get pred. metrics based on testing data}
\NormalTok{test\_prediction }\OtherTok{=}\NormalTok{ xgboost\_model\_final }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data=}\NormalTok{train\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{predict}\NormalTok{(}\AttributeTok{new\_data=}\NormalTok{test\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{testing}\NormalTok{(dat\_split))}

\NormalTok{res\_final }\OtherTok{=}\NormalTok{ test\_prediction }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  yardstick}\SpecialCharTok{::}\FunctionTok{metrics}\NormalTok{(value, .pred) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{.estimate=}\FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(.estimate, }\DecValTok{2}\NormalTok{), }\AttributeTok{big.mark=}\StringTok{","}\NormalTok{))}
\NormalTok{res\_final}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 3
##   .metric .estimator .estimate
##   <chr>   <chr>      <chr>    
## 1 rmse    standard   1.38     
## 2 rsq     standard   0.68     
## 3 mae     standard   1.05
\end{verbatim}

As seen on the table and visual, Random Forest has the highest RMSE and
lowest R-squared estimate. LR has the second highest RMSE with a
moderate R-squared estimate. And XG Boost has the lowest RMSE of 0.23
and the highest R-squared estimate of 0.99. The kNN model has the both
the second lowest RMSE and second highest R-squared estimate. Since we
are choosing the best model by the best RMSE, which is the lowest one,
the XG Boost model is thus the best and final model based on our
procedure. After fitting the XG Boost model to the testing data, we find
that its RMSE and R-squared is 1.38 and 0.68, respectively. Since we are
trying to predict annual average ambient air pollution of a given
monitor, then these statistics mean that the amount of error in our
model's predictions is about 1.38 \(\mu\)g/m\(^3\), and that the
features we used in our model are able to explain 68\% of the variance
in the data, which means this model does not fit/predict the data well.

\textbf{1. Based on test set performance, at what locations does your
model give predictions that are closest and furthest from the observed
values? What do you hypothesize are the reasons for the good or bad
performance at these locations?}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Arrange obs.s by greatest diff}
\NormalTok{loc }\OtherTok{=}\NormalTok{ test\_prediction }\SpecialCharTok{|\textgreater{}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(.pred, value, CMAQ, lat, lon, county\_area, aod, state) }\SpecialCharTok{|\textgreater{}} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{diff=}\FunctionTok{round}\NormalTok{(}\FunctionTok{abs}\NormalTok{(value}\SpecialCharTok{{-}}\NormalTok{.pred),}\DecValTok{2}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(diff))}

\CommentTok{\# Find number of obs.s per the 3 states}
\NormalTok{loc }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(state}\SpecialCharTok{==}\StringTok{\textquotesingle{}Oregon\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ state}\SpecialCharTok{==}\StringTok{\textquotesingle{}Iowa\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ state}\SpecialCharTok{==}\StringTok{\textquotesingle{}Virginia\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(state) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarise}\NormalTok{(}\AttributeTok{mon=}\FunctionTok{n}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 2
##   state      mon
##   <chr>    <int>
## 1 Iowa         6
## 2 Oregon       5
## 3 Virginia     5
\end{verbatim}

Based on the test set performance, it seems that our model gives the
closest prediction for both Iowa and Virginia The model gives the
furthest prediction for Oregon. We hypothesize that the model gives bad
performance for Oregon because despite being clearly larger than both
Iowa and Virginia, it has the same number of monitors as the latter
states, making the data less representative of the variation in PM2.5
concentration for the state for the model to make a good prediction
based on the features we chose.

\textbf{2. What variables might predict where your model performs well
or not? For example, are their regions of the country where the model
does better or worse? Are there variables that are not included in this
dataset that you think might improve the model performance if they were
included in your model?}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Visual for the most frequently close predictions by state}
\NormalTok{loc }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(diff}\SpecialCharTok{\textless{}}\FloatTok{0.5}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{y=}\NormalTok{state)) }\SpecialCharTok{+} \FunctionTok{geom\_bar}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Draft_files/figure-latex/Q2-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Visual for the most frequently furthest predictions by state}
\NormalTok{loc }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(diff}\SpecialCharTok{\textgreater{}=}\FloatTok{0.5}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{y=}\NormalTok{state)) }\SpecialCharTok{+} \FunctionTok{geom\_bar}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Draft_files/figure-latex/Q2-2.pdf}

`CMAQ', `county\_area', and `aod' might predict where our model performs
well or not. We define a good prediction by having an absolute
difference of less than 0.5 between `value' and `.pred'. Indiana, Ohio,
Iowa, and Alabama most frequently have good predictions. So the model
does fairly well at predicting some of the Midwest. Our model gives the
furthest predictions for California, Colorado, Kentucky, Pennsylvania,
and Texas most frequently. So our model does poorly at predicting the
West and the South. We think that including historical data of ambient
air pollution over the years would potentially improve the performance
of the model because if we are able to track the air pollution over the
years, we could get a better prediction for any given location.

\textbf{3. There is interest in developing more cost-effect approaches
to monitoring air pollution on the ground. Two candidates for replacing
the use of ground-based monitors are numerical models like CMAQ and
satellite-based observations such as AOD. How well do CMAQ and AOD
predict ground-level concentrations of PM2.5? How does the prediction
performance of your model change when CMAQ or AOD are included (or not
included) in the model?}

The model with only `CMAQ' and `aod' as features has an RMSE of 1.99.
Since it is greater than 1, this means that `CMAQ' and `aod' are not
good predictors for annual ambient air pollution in a given location.
The RMSE of our model on the test data is 1.38. The RMSE of our model
without `CMAQ' and `aod' is 1.73. This means that the model without
`CMAQ' and `aod' has the better prediction performance since its RMSE is
lower than our original model.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# XGB model w/only cmaq and aod}
\CommentTok{\# Preprocessing recipe}
\NormalTok{rec5 }\OtherTok{\textless{}{-}} 
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ }\SpecialCharTok{+}\NormalTok{ aod, }\AttributeTok{data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Convert categorical variables to factors}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_string2factor}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Combine low frequency factor levels}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_other}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{(), }\AttributeTok{threshold =} \FloatTok{0.01}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Remove no variance predictors which provide no predictive information }
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_nzv}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{prep}\NormalTok{()}

\NormalTok{folds5 }\OtherTok{\textless{}{-}}\NormalTok{ recipes}\SpecialCharTok{::}\FunctionTok{bake}\NormalTok{(rec5, }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}  
\NormalTok{  rsample}\SpecialCharTok{::}\FunctionTok{vfold\_cv}\NormalTok{(}\AttributeTok{v =} \DecValTok{5}\NormalTok{)}

\CommentTok{\# XGBoost model specification}
\NormalTok{xgboost\_model }\OtherTok{\textless{}{-}}\NormalTok{ parsnip}\SpecialCharTok{::}\FunctionTok{boost\_tree}\NormalTok{(}\AttributeTok{mode =} \StringTok{"regression"}\NormalTok{, }\AttributeTok{trees =} \DecValTok{1000}\NormalTok{, }\AttributeTok{min\_n =} \FunctionTok{tune}\NormalTok{(),}
  \AttributeTok{tree\_depth =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{learn\_rate =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{loss\_reduction =} \FunctionTok{tune}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"xgboost"}\NormalTok{, }\AttributeTok{objective =} \StringTok{"reg:squarederror"}\NormalTok{)}

\CommentTok{\# Grid specification}
\NormalTok{xgboost\_params }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{parameters}\NormalTok{(}\FunctionTok{min\_n}\NormalTok{(), }\FunctionTok{tree\_depth}\NormalTok{(), }\FunctionTok{learn\_rate}\NormalTok{(), }\FunctionTok{loss\_reduction}\NormalTok{())}

\NormalTok{xgboost\_grid }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{grid\_max\_entropy}\NormalTok{(xgboost\_params, }\AttributeTok{size =} \DecValTok{60}\NormalTok{)}

\FunctionTok{head}\NormalTok{(xgboost\_grid)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 6 x 4
##   min_n tree_depth learn_rate loss_reduction
##   <int>      <int>      <dbl>          <dbl>
## 1    35          3   5.13e- 8        6.09e-5
## 2    37          2   1.25e- 5        1.78e+1
## 3    36          8   1.82e- 6        1.52e-7
## 4    24          5   1.54e- 6        4.86e-2
## 5     2          3   8.76e- 9        1.26e-7
## 6    31          3   4.23e-10        1.23e-9
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{xgboost\_wf }\OtherTok{\textless{}{-}}\NormalTok{ workflows}\SpecialCharTok{::}\FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_model}\NormalTok{(xgboost\_model) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{add\_formula}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{aod)}

\CommentTok{\# Hyperparameter tuning}
\CommentTok{\# Takes a long time to run, 5{-}8 min}
\NormalTok{xgboost\_tuned }\OtherTok{\textless{}{-}}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{tune\_grid}\NormalTok{(}\AttributeTok{object =}\NormalTok{ xgboost\_wf, }\AttributeTok{resamples =}\NormalTok{ folds5,}
  \AttributeTok{grid =}\NormalTok{ xgboost\_grid, }\AttributeTok{metrics =}\NormalTok{ yardstick}\SpecialCharTok{::}\FunctionTok{metric\_set}\NormalTok{(rmse, rsq),}
  \AttributeTok{control =}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{control\_grid}\NormalTok{(}\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{))}

\CommentTok{\# Find hyper parameter values which performed best at minimizing RMSE}
\NormalTok{xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{show\_best}\NormalTok{(}\AttributeTok{metric =} \StringTok{"rmse"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0566}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1415}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0755}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0849}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0283}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0943}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2075}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedleft
min\_n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
tree\_depth
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
learn\_rate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
loss\_reduction
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.estimator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
mean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
std\_err
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.config
\end{minipage} \\
\midrule()
\endhead
16 & 15 & 0.0228946 & 1.4483751 & rmse & standard & 2.013219 & 5 &
0.0448618 & Preprocessor1\_Model42 \\
22 & 8 & 0.0200526 & 0.1687102 & rmse & standard & 2.067097 & 5 &
0.0494466 & Preprocessor1\_Model57 \\
2 & 11 & 0.0832471 & 0.5027694 & rmse & standard & 2.074551 & 5 &
0.0606428 & Preprocessor1\_Model51 \\
7 & 9 & 0.0301111 & 0.0000000 & rmse & standard & 2.088754 & 5 &
0.0733218 & Preprocessor1\_Model44 \\
23 & 9 & 0.0059687 & 0.0000000 & rmse & standard & 2.099911 & 5 &
0.0676423 & Preprocessor1\_Model36 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Isolate the best performing hyperparameter values.}
\NormalTok{xgboost\_best\_params }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{select\_best}\NormalTok{(}\StringTok{"rmse"}\NormalTok{)}
\NormalTok{xgboost\_best\_params}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 1 x 5
##   min_n tree_depth learn_rate loss_reduction .config              
##   <int>      <int>      <dbl>          <dbl> <chr>                
## 1    16         15     0.0229           1.45 Preprocessor1_Model42
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Final boost model}
\NormalTok{xgboost\_model\_final }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_model }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{finalize\_model}\NormalTok{(xgboost\_best\_params)}

\CommentTok{\# Eval. model performance on train data}
\NormalTok{test\_processed }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec5,  }\AttributeTok{new\_data =} \FunctionTok{testing}\NormalTok{(dat\_split))}
\NormalTok{train\_processed }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec5,  }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split))}

\NormalTok{test\_prediction }\OtherTok{=}\NormalTok{ xgboost\_model\_final }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ CMAQ}\SpecialCharTok{+}\NormalTok{aod, }\AttributeTok{data=}\NormalTok{train\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{predict}\NormalTok{(}\AttributeTok{new\_data=}\NormalTok{test\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{testing}\NormalTok{(dat\_split))}

\NormalTok{res5 }\OtherTok{=}\NormalTok{ test\_prediction }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  yardstick}\SpecialCharTok{::}\FunctionTok{metrics}\NormalTok{(value, .pred) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{.estimate=}\FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(.estimate, }\DecValTok{2}\NormalTok{), }\AttributeTok{big.mark=}\StringTok{","}\NormalTok{))}
\NormalTok{res5}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 3
##   .metric .estimator .estimate
##   <chr>   <chr>      <chr>    
## 1 rmse    standard   1.99     
## 2 rsq     standard   0.36     
## 3 mae     standard   1.43
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\CommentTok{\# XGB model w/o cmaq and aod}
\CommentTok{\# Preprocessing recipe}
\NormalTok{rec8 }\OtherTok{\textless{}{-}} 
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{recipe}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon, }\AttributeTok{data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Convert categorical variables to factors}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_string2factor}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Combine low frequency factor levels}
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_other}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{(), }\AttributeTok{threshold =} \FloatTok{0.01}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Remove no variance predictors which provide no predictive information }
\NormalTok{  recipes}\SpecialCharTok{::}\FunctionTok{step\_nzv}\NormalTok{(}\FunctionTok{all\_nominal}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{prep}\NormalTok{()}

\NormalTok{folds8 }\OtherTok{\textless{}{-}}\NormalTok{ recipes}\SpecialCharTok{::}\FunctionTok{bake}\NormalTok{(rec8, }\AttributeTok{new\_data =} \FunctionTok{training}\NormalTok{(dat\_split)) }\SpecialCharTok{\%\textgreater{}\%}  
\NormalTok{  rsample}\SpecialCharTok{::}\FunctionTok{vfold\_cv}\NormalTok{(}\AttributeTok{v =} \DecValTok{5}\NormalTok{)}

\CommentTok{\# XGBoost model specification}
\NormalTok{xgboost\_model }\OtherTok{\textless{}{-}}\NormalTok{ parsnip}\SpecialCharTok{::}\FunctionTok{boost\_tree}\NormalTok{(}\AttributeTok{mode =} \StringTok{"regression"}\NormalTok{, }\AttributeTok{trees =} \DecValTok{1000}\NormalTok{, }\AttributeTok{min\_n =} \FunctionTok{tune}\NormalTok{(),}
  \AttributeTok{tree\_depth =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{learn\_rate =} \FunctionTok{tune}\NormalTok{(), }\AttributeTok{loss\_reduction =} \FunctionTok{tune}\NormalTok{()) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{set\_engine}\NormalTok{(}\StringTok{"xgboost"}\NormalTok{, }\AttributeTok{objective =} \StringTok{"reg:squarederror"}\NormalTok{)}

\CommentTok{\# Grid specification}
\NormalTok{xgboost\_params }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{parameters}\NormalTok{(}\FunctionTok{min\_n}\NormalTok{(), }\FunctionTok{tree\_depth}\NormalTok{(), }\FunctionTok{learn\_rate}\NormalTok{(), }\FunctionTok{loss\_reduction}\NormalTok{())}

\NormalTok{xgboost\_grid }\OtherTok{\textless{}{-}}\NormalTok{ dials}\SpecialCharTok{::}\FunctionTok{grid\_max\_entropy}\NormalTok{(xgboost\_params, }\AttributeTok{size =} \DecValTok{60}\NormalTok{)}

\FunctionTok{head}\NormalTok{(xgboost\_grid)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 6 x 4
##   min_n tree_depth learn_rate loss_reduction
##   <int>      <int>      <dbl>          <dbl>
## 1    35          3   5.13e- 8        6.09e-5
## 2    37          2   1.25e- 5        1.78e+1
## 3    36          8   1.82e- 6        1.52e-7
## 4    24          5   1.54e- 6        4.86e-2
## 5     2          3   8.76e- 9        1.26e-7
## 6    31          3   4.23e-10        1.23e-9
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{xgboost\_wf }\OtherTok{\textless{}{-}}\NormalTok{ workflows}\SpecialCharTok{::}\FunctionTok{workflow}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{add\_model}\NormalTok{(xgboost\_model) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{add\_formula}\NormalTok{(value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon)}

\CommentTok{\# Hyperparameter tuning}
\CommentTok{\# Takes a long time to run, 5{-}8 min}
\NormalTok{xgboost\_tuned }\OtherTok{\textless{}{-}}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{tune\_grid}\NormalTok{(}\AttributeTok{object =}\NormalTok{ xgboost\_wf, }\AttributeTok{resamples =}\NormalTok{ folds8,}
  \AttributeTok{grid =}\NormalTok{ xgboost\_grid, }\AttributeTok{metrics =}\NormalTok{ yardstick}\SpecialCharTok{::}\FunctionTok{metric\_set}\NormalTok{(rmse, rsq),}
  \AttributeTok{control =}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{control\_grid}\NormalTok{(}\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{))}

\CommentTok{\# Find hyper parameter values which performed best at minimizing RMSE}
\NormalTok{xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{show\_best}\NormalTok{(}\AttributeTok{metric =} \StringTok{"rmse"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0566}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1415}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0755}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1038}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0849}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0283}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0943}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2075}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedleft
min\_n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
tree\_depth
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
learn\_rate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
loss\_reduction
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.estimator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
mean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
std\_err
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
.config
\end{minipage} \\
\midrule()
\endhead
7 & 9 & 0.0301111 & 0.0000000 & rmse & standard & 1.675871 & 5 &
0.0512906 & Preprocessor1\_Model44 \\
2 & 11 & 0.0832471 & 0.5027694 & rmse & standard & 1.689391 & 5 &
0.0500638 & Preprocessor1\_Model51 \\
16 & 15 & 0.0228946 & 1.4483751 & rmse & standard & 1.699305 & 5 &
0.0304960 & Preprocessor1\_Model42 \\
22 & 8 & 0.0200526 & 0.1687102 & rmse & standard & 1.740950 & 5 &
0.0541269 & Preprocessor1\_Model57 \\
23 & 9 & 0.0059687 & 0.0000000 & rmse & standard & 1.786317 & 5 &
0.0473593 & Preprocessor1\_Model36 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Isolate the best performing hyperparameter values.}
\NormalTok{xgboost\_best\_params }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_tuned }\SpecialCharTok{\%\textgreater{}\%}\NormalTok{ tune}\SpecialCharTok{::}\FunctionTok{select\_best}\NormalTok{(}\StringTok{"rmse"}\NormalTok{)}
\NormalTok{xgboost\_best\_params}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 1 x 5
##   min_n tree_depth learn_rate loss_reduction .config              
##   <int>      <int>      <dbl>          <dbl> <chr>                
## 1     7          9     0.0301       8.93e-10 Preprocessor1_Model44
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Final boost model}
\NormalTok{xgboost\_model\_final }\OtherTok{\textless{}{-}}\NormalTok{ xgboost\_model }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{finalize\_model}\NormalTok{(xgboost\_best\_params)}

\CommentTok{\# Eval. model performance on train data}
\NormalTok{train\_processed }\OtherTok{=} \FunctionTok{bake}\NormalTok{(rec8, }\AttributeTok{new\_data=}\FunctionTok{training}\NormalTok{(dat\_split))}
\NormalTok{test\_processed }\OtherTok{\textless{}{-}} \FunctionTok{bake}\NormalTok{(rec8, }\AttributeTok{new\_data =} \FunctionTok{testing}\NormalTok{(dat\_split))}

\NormalTok{test\_prediction }\OtherTok{=}\NormalTok{ xgboost\_model\_final }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  parsnip}\SpecialCharTok{::}\FunctionTok{fit}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ value }\SpecialCharTok{\textasciitilde{}}\NormalTok{ lat}\SpecialCharTok{+}\NormalTok{county\_area}\SpecialCharTok{+}\NormalTok{lon, }\AttributeTok{data=}\NormalTok{train\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{predict}\NormalTok{(}\AttributeTok{new\_data=}\NormalTok{test\_processed) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{bind\_cols}\NormalTok{(}\FunctionTok{testing}\NormalTok{(dat\_split))}

\NormalTok{res8 }\OtherTok{=}\NormalTok{ test\_prediction }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  yardstick}\SpecialCharTok{::}\FunctionTok{metrics}\NormalTok{(value, .pred) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{.estimate=}\FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(.estimate, }\DecValTok{2}\NormalTok{), }\AttributeTok{big.mark=}\StringTok{","}\NormalTok{))}
\NormalTok{res8}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 3 x 3
##   .metric .estimator .estimate
##   <chr>   <chr>      <chr>    
## 1 rmse    standard   1.73     
## 2 rsq     standard   0.52     
## 3 mae     standard   1.13
\end{verbatim}

\textbf{4. The dataset here did not include data from Alaska or Hawaii.
Do you think your model will perform well or not in those two states?
Explain your reasoning.}

Given that the top 5 features were `CMAQ', `lat', `county\_area', `lon',
and `aod'. We think that XG Boost model will not perform well since our
model did not perform well on the test dataset. It seems like we overfit
our model, so fitting it to data from Hawaii and Alaska, which we expect
to be veyr different from our training dataset, will yield similar
results to fitting our model to the test dataset.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\textbf{Putting it all together, what did you learn from your data and
your model performance? Answer your Question posed above, citing any
supporting statistics, visualizations, or results from the data or your
models.}

We learned that we overfit our Xgboost model to the data, which is why
the prediction performance was poor for the testing dataset. This can be
seen in our model having an RMSE value of 1.38 despite the RMSE of the
model fit to the training data being 0.23. In general, we learned that
understanding the disadvantages and advantages of each model is helpful
toward understanding why a model fails or succeeds at the training and
testing stages. For instance, we learned the Xgboost is helpful for
unbalanced data and that Random Forest Regression performs well for
datasets with a lot of noise.

\textbf{Reflect on the process of conducting this project. What was
challenging, what have you learned from the process itself?}

The most challenging aspect of this project was figuring out the process
to determine which predictors were the best to use for our models. We
ran into many debugging issues and Googled a lot to resolve our
uncertainties. We learned that finding the best predictors for a model
can be a lengthy process and that running a new model
(e.g.~preprocessing and hyperparameter tuning steps for XG Boost and
Random Forest Regression) often may require lots of research into what
is needed for the model to run before it can actually run.

\textbf{Reflect on the performance of your final prediction model. Did
it perform as well as you originally expected? If not, why do you think
it didn't perform as well?}

The RMSE of our model was 1.38 on the testing dataset, which means it
does not predict well. It did not perform as well as we originally
expected, especially since we saw that the RMSE of our model was 0.23 on
the training dataset. We believe the model did not perform well because
we overfit the model to the training data. This means that the model
gives inaccurate predictions and cannot perform well for all types of
new data, which is why despite the low RMSE on the training data, the
model has poor prediction performance on the testing data.

\textbf{Include acknowledgments for any help received. If a group
project, report the contribution of each member (i.e.~who did what?).}
\#\# Acknowledgements \textbf{Aileen Li \& Nyah Strickland:} - Intro

\begin{itemize}
\item
  Wrangling
\item
  Results
\item
  Discussion
\item
  Formatting
\end{itemize}

\end{document}

### 2023-04-24 Draft.Rmd
final

@@
 ```
-## Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.
-
 Air pollution has consequences for everyone, most especially for those with pre-existing conditions.
@@
 
-```{r Library message=FALSE}
-library(tidyverse)
-library(tidymodels)
-library(broom)
-library(xgboost)
-library(caret)
-library(plotROC)
-library(randomForest)
-library(factoextra)
-library(MASS)
-library(ranger)
-library(doParallel)
-
+```{r Library}
+library(tidyverse);library(tidymodels);library(broom);library(xgboost);library(caret);library(plotROC)
+library(randomForest);library(factoextra);library(MASS);library(ranger);library(doParallel)
 origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
@@
 # train_knn for kNN model
-train_knn = train[,2:50] %>% dplyr::select(where(is.numeric)) %>% mutate(across(fips:aod, scale)) %>% cbind(state=train$state,county=train$county,city=train$city)
+train_knn = train[,2:50] %>% 
+  dplyr::select(where(is.numeric)) %>% 
+  mutate(across(fips:aod, scale)) %>%
+  cbind(state=train$state,county=train$county,city=train$city)
 
 # Visualize linear relationship between predictors (lat, lon, state) and value
-origin %>% ggplot(aes(x=lon, y=value)) + 
-  geom_point() + geom_smooth() + 
+origin %>% ggplot(aes(x=lon, y=value)) + geom_point() + geom_smooth() + 
   labs(title="PM2.5 Concentration vs Longitude", x="Longitude (Degrees)", y="PM2.5 (mu g/m^3)")
 
-origin %>% ggplot(aes(x=lat, y=value)) + 
-  geom_point() + geom_smooth() + 
+origin %>% ggplot(aes(x=lat, y=value)) + geom_point() + geom_smooth() + 
   labs(title="PM2.5 Concentration vs Latitude", x="Latitude (Degrees)", y="PM2.5 (mu g/m^3)")
@@
 import=tibble::rownames_to_column(import, 'variables')
-
 # take top 5 important variables
@@
     add_model(model1)
-# wf1
 
@@
 # Check performance of linear regression model on the training data
-res1 %>% 
-    extract_fit_engine() %>% 
-    summary()
+res1 %>% extract_fit_engine() %>% summary()
 
@@
 res1 <- fit_resamples(wf1, resamples = folds1)
-res1 %>% 
-    collect_metrics()
+res1 %>% collect_metrics()
 ```
@@
 # Check performance on the complete training data
-res2 %>% 
-    extract_fit_engine() %>% 
-    summary()
+res2 %>% extract_fit_engine() %>% summary()
 
@@
 # folds
-res2 <- fit_resamples(wf2, resamples = folds2) # ERROR Assigned data `orig_rows` must be compatible with existing data.
-res2 %>% 
-    collect_metrics()
+res2 <- fit_resamples(wf2, resamples = folds2)
+res2 %>% collect_metrics()
 ```
@@
 
-# head(xgboost_grid)
-
 xgboost_wf <- workflows::workflow() %>%
@@
 
-# Hyperparameter tuning
-# Takes a long time to run, 5-8 min
+# Hyperparameter tuning, Takes a long time to run, 5-8 min
 xgboost_tuned <- tune::tune_grid(object = xgboost_wf, resamples = folds3,
@@
 # Find hyper parameter values which performed best at minimizing RMSE
-xgboost_tuned %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+xgboost_tuned %>% tune::show_best(metric = "rmse")
 # Isolate the best performing hyperparameter values.
@@
 all_cores = parallel::detectCores(logical=FALSE)
-cl = makePSOCKcluster(all_cores)
-doParallel::registerDoParallel(cl)
+cl = makePSOCKcluster(all_cores);doParallel::registerDoParallel(cl)
 
 # Takes long time to load 2 min
-tune_res <- wf4 |> tune_grid(resamples = folds4, grid = rf_grid, metrics=metric_set(rmse,rsq), control = tune::control_grid(verbose = TRUE))
-# tune_res
+tune_res <- wf4 |> tune_grid(resamples = folds4, 
+                             grid = rf_grid, 
+                             metrics=metric_set(rmse,rsq), 
+                             control = tune::control_grid(verbose = TRUE))
 
 # Find hyper parameter values which performed best at minimizing RMSE
-tune_res %>% tune::show_best(metric = "rmse") %>%knitr::kable()
+tune_res %>% tune::show_best(metric = "rmse")
 # Isolate the best performing hyperparameter values.
@@
 train_prediction2 = rf_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod, data=train_processed2) |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod,
+               data=train_processed2) |> 
   predict(new_data=train_processed2) |> 
@@
 # Visual of rmse for our 4 models
-compare |> ggplot(aes(x=model, y=rmse)) + 
-  geom_bar(stat="identity") + 
-  labs(title='RMSE of the Four Models') +
-  theme_minimal()
+compare |> ggplot(aes(x=model, y=rmse)) + geom_bar(stat="identity") + 
+  labs(title='RMSE of the Four Models') + theme_minimal()
 
@@
 test_prediction = xgboost_model_final |> 
-  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod, data=train_processed) |> 
+  parsnip::fit(formula = value ~ CMAQ+lat+county_area+lon+aod,
+               data=train_processed) |> 
   predict(new_data=test_processed) |> 
@@
 # Arrange obs.s by greatest diff
-loc = test_prediction |> dplyr::select(.pred, value, CMAQ, lat, lon, county_area, aod, state) |> mutate(diff=round(abs(value-.pred),2)) |> arrange(desc(diff))
+loc = test_prediction |> 
+  dplyr::select(.pred, value, CMAQ, lat, lon, county_area, aod, state) |>
+  mutate(diff=round(abs(value-.pred),2)) |> arrange(desc(diff))
 
 # Find number of obs.s per the 3 states
-loc |> filter(state=='Oregon' | state=='Iowa' | state=='Virginia') |> group_by(state) |> summarise(mon=n())
+loc |> 
+  filter(state=='Oregon' | state=='Iowa' | state=='Virginia') |>
+  group_by(state) |> summarise(mon=n())
 ```
@@
 # Visual for the most frequently close predictions by state
-loc |> filter(diff<0.5) |> ggplot(aes(y=state)) + geom_bar()
+loc |>filter(diff<0.5) |> ggplot(aes(y=state)) + 
+  geom_bar() + 
+  labs(title='Most Frequent Close Predictions by State')
 
 # Visual for the most frequently furthest predictions by state
-loc |> filter(diff>=0.5) |> ggplot(aes(y=state)) + geom_bar()
+loc |> filter(diff>=0.5) |> ggplot(aes(y=state)) + 
+  geom_bar() + labs(title='Most Frequent Far Predictions by State')
 ```
@@
   # Remove no variance predictors which provide no predictive information 
-  recipes::step_nzv(all_nominal()) %>%
-  prep()
+  recipes::step_nzv(all_nominal()) %>% prep()
 
@@
 xgboost_params <- dials::parameters(min_n(), tree_depth(), learn_rate(), loss_reduction())
-
 xgboost_grid <- dials::grid_max_entropy(xgboost_params, size = 60)
-
-head(xgboost_grid)
 
@@
 **Aileen Li & Nyah Strickland:**
+
 - Intro
